---
title: "VE of Nirsevimab (jags model w/ commensurate priors)"
output: 
  html_document:
    toc: true
    toc_float: true
---

### Date: `r Sys.Date()`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

library(dplyr)
library(tidyr)
library(tidyverse)
library(readxl)
library(writexl)
library(reactable)
library(ggplot2)
library(stringr)
library(flextable)
library(lubridate)
library(rjags)


library(gtsummary) # for table 1
library(multcomp)
library(survival) # for matched case-control

fig.counter <- 1
tab.counter <- 1

source("utils_mAb_VE.R")
source("jags_commensurate_prior.R")


rerun <- FALSE
savenewplot <- FALSE
```

### Take a look at data extracted from previous trials and longitudinal studies 
  * Hammitt et al.2022: MELODY (Phase III)
  * Simões et al. 2023: phase IIb + phase III
  * Ares-Gómez et al. 2024: longitudinal study in Spain
```{r}
# read in data from MELODY trial (Hammitt et al. 2022)
df.orig.trial <- read_excel("../data/jags/ve_trials.xlsx", sheet = "trial") %>% dplyr::select(-title)

df.orig.trial %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T, groupBy = "Trial") 

# make columns for jags output
df.orig.trial$ve_uninfo_median <- NA
df.orig.trial$ve_uninfo_lb <- NA
df.orig.trial$ve_uninfo_ub <- NA
df.orig.trial$ve_info_median <- NA
df.orig.trial$ve_info_lb <- NA
df.orig.trial$ve_info_ub <- NA
```



```{r}
# read in dataset for the current case-control study for Nirsevimab
df <- read.csv("../data/clean_data/df.mab.csv")

# add some variables 
df <- process_df(df)
```

```{r}
# For VE against infection
# only adjusting for those that has significant difference comparing RSV+ and RSV- records
confounders_infection <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat", 
  "birth_weight",
  "risk_factor_gestagelessthan37wks"
)

# convert confounders from character to numeric 
df <- df %>% 
  # recode confounders
  mutate(cf_birth_weight = birth_weight) %>% # about 25% missing 
  mutate(cf_age = case_when(age_at_test_in_months_cat_2 == "under 3m" ~ 1,
                            age_at_test_in_months_cat_2 == "3-6m" ~ 2,
                            age_at_test_in_months_cat_2 == "6-9m" ~ 3,
                            age_at_test_in_months_cat_2 == "9-12m" ~ 4,
                            age_at_test_in_months_cat_2 == "above 1 yo" ~ 5)) %>%
  mutate(cf_month_tested = case_when(month_when_tested_cat == "Oct-Nov" ~ 1,
                                     month_when_tested_cat == "Dec-Jan" ~ 2,
                                     month_when_tested_cat == "Feb-Mar" ~ 3,
                                     month_when_tested_cat == "April and after" ~ 4
                                     )) %>%
  # convert categorical confounders to dummy variables 
  mutate(cf_age_1 = ifelse(cf_age == 1, 1, 0),
         cf_age_2 = ifelse(cf_age == 2, 1, 0),
         cf_age_3 = ifelse(cf_age == 3, 1, 0),
         cf_age_4 = ifelse(cf_age == 4, 1, 0), 
         cf_age_5 = ifelse(cf_age == 5, 1, 0)) %>%
  mutate(cf_month_tested_1 = ifelse(cf_month_tested == 1, 1, 0),
         cf_month_tested_2 = ifelse(cf_month_tested == 2, 1, 0),
         cf_month_tested_3 = ifelse(cf_month_tested == 3, 1, 0),
         cf_month_tested_4 = ifelse(cf_month_tested == 4, 1, 0)) %>%
  mutate(cf_gestage = risk_factor_gestagelessthan37wks)
```

<br>

### Use data from previous trials as priors to do VE estimation {.tabset}

Comparing:   
  * Original trial estimates;
  * Adjusted VE estimated from current case-control study (uninformative priors);
  * Adjusted VE estimated from current case-control study (trial data as informative priors)

#### Medically attended RSV LRTI (Hammitt et al)
  * extracted from case-control: RSV+ LRTI as cases vs. RSV- LRTI as controls
```{r}
####################################################
# Medically attended RSV LRTI as endpoint (Hammitt et al) 
####################################################
df.jags <- df %>% 
  filter(symp_LRT_distress == 1) %>%
  mutate(case_control = positive_rsv) %>%
  filter(!is.na(cf_birth_weight) & !is.na(cf_gestage))


dataset_uninformative_priors <- 
            list(
                # from current case-control
                N_people = nrow(df.jags),
                case_status = df.jags$case_control,
                vax = df.jags$rsv_mab,
                # confounders
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4,
                cf_birth_weight = df.jags$cf_birth_weight,
                cf_gestage = df.jags$cf_gestage
                )

dataset_informative_priors <- 
            list(
                # from previous study
                N_cases_orig = c(25, 12), # (case_placebo, case_vax)
                pop_orig = c(496, 994), # (N_placebo, N_vax)
                # from current case-control
                N_people = nrow(df.jags),
                case_status = df.jags$case_control,
                vax = df.jags$rsv_mab,
                # confounders
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4,
                cf_birth_weight = df.jags$cf_birth_weight,
                cf_gestage = df.jags$cf_gestage,
                # others
                prior_mean_log_irr = 999, 
                set_tau_shp=999, 
                set_tau_rate=999, 
                prior_prec_log_irr = 999, 
                sd.upper=999
                )


source("jags_commensurate_prior.R")

if(rerun){
  # model w/ uninformative priors 
  jags.post.uninfo <- jags.model(textConnection(model_string_uninformative_priors), 
                          data = dataset_uninformative_priors,
                          n.chains = 3)

  samples.uninfo <- coda.samples(jags.post.uninfo, 
                          variable.names=c("int", "beta1"),
                          n.iter = 5000)
  saveRDS(samples.uninfo, "../data/jags/post/RSV_LRTI_uninfo.rds")
  
   # model w/ informative priors 
  jags.post.info <- jags.model(textConnection(model_string_informative_priors), 
                          data = dataset_informative_priors,
                          n.chains = 3)

  samples.info <- coda.samples(jags.post.info, 
                          variable.names=c("delta", "int", "beta1", "shared"),
                          n.iter = 5000)
  saveRDS(samples.info, "../data/jags/post/RSV_LRTI_info.rds")
  
}else{
  samples.uninfo <- readRDS("../data/jags/post/RSV_LRTI_uninfo.rds")
  samples.info <- readRDS("../data/jags/post/RSV_LRTI_info.rds")
}


## process jags output 

# uninformative priors 
post1 <- as.data.frame(as.matrix(samples.uninfo[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples.uninfo[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples.uninfo[[3]][-c(1:4500),])) 
post.uninfo <- bind_rows(post1, post2, post3)

ve.median.uninfo <- round((1 - exp(median(post.uninfo$beta1)))*100,1)
ve.lb.uninfo <- round((1 - exp(quantile(post.uninfo$beta1, 0.975))) *100,1)
ve.ub.uninfo <- round((1 - exp(quantile(post.uninfo$beta1, 0.025)))*100, 1)

# informative priors 
post1 <- as.data.frame(as.matrix(samples.info[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples.info[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples.info[[3]][-c(1:4500),])) 
post.info <- bind_rows(post1, post2, post3)

ve.median.info <- round((1 - exp(median(post.info$beta1)))*100,1)
ve.lb.info <- round((1 - exp(quantile(post.info$beta1, 0.975))) *100,1)
ve.ub.info <- round((1 - exp(quantile(post.info$beta1, 0.025)))*100, 1)

# quantify information-sharing between historical trial and current study
shared.median.RSVLRTI <- median(post.info$shared)

# fill in results
row_index <- 1
df.orig.trial$ve_uninfo_median[row_index] <- ve.median.uninfo
df.orig.trial$ve_uninfo_lb[row_index] <- ve.lb.uninfo
df.orig.trial$ve_uninfo_ub[row_index] <- ve.ub.uninfo
df.orig.trial$ve_info_median[row_index] <- ve.median.info
df.orig.trial$ve_info_lb[row_index] <- ve.lb.info
df.orig.trial$ve_info_ub[row_index] <- ve.ub.info

# show results 
df.orig.trial[row_index,] %>%  
  mutate(ve_trial = paste0(ve_trial_median, " (", ve_trial_lb, "-", ve_trial_ub, ")")) %>%
  mutate(ve_cc_uninformative_priors = paste0(ve_uninfo_median, " (", ve_uninfo_lb, "-", ve_uninfo_ub, ")")) %>%
  mutate(ve_cc_informative_priors = paste0(ve_info_median, " (", ve_info_lb, "-", ve_info_ub, ")")) %>%
  mutate(shared = round(shared.median.RSVLRTI, 3)) %>%
  dplyr::select(outcome, ve_trial, ve_cc_uninformative_priors, ve_cc_informative_priors, shared) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T) 
  

# look at traceplot of coefficient of vax variable
plot(samples.uninfo[, "beta1"])
title("beta1 (uninformative priors)")

plot(samples.info[, "beta1"])
title("beta1 (informative priors)")
```


#### RSV-related LRTI hospitalizations (Hammitt et al)
  * extracted from case-control: RSV-related LRTI hospitalizations as cases vs. RSV- as controls
```{r}
####################################################
# RSV-related LRTI hospitalization as endpoint (Hammitt et al)
####################################################
df.jags <- df %>% 
  filter(symp_LRT_distress == 1 & encounter_type == "inpatient") %>%
  mutate(case_control = positive_rsv) %>% 
  filter(!is.na(cf_birth_weight) & !is.na(cf_gestage))
  


dataset_uninformative_priors <- 
            list(
                # from current case-control
                N_people = nrow(df.jags),
                case_status = df.jags$case_control,
                vax = df.jags$rsv_mab,
                # confounders
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4,
                cf_birth_weight = df.jags$cf_birth_weight,
                cf_gestage = df.jags$cf_gestage
                )

dataset_informative_priors <- 
            list(
                # from previous study
                N_cases_orig = c(8, 6), # (case_placebo, case_vax)
                pop_orig = c(496, 994), # (N_placebo, N_vax)
                # from current case-control
                N_people = nrow(df.jags),
                case_status = df.jags$case_control,
                vax = df.jags$rsv_mab,
                # confounders
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4,
                cf_birth_weight = df.jags$cf_birth_weight,
                cf_gestage = df.jags$cf_gestage,
                # others
                prior_mean_log_irr = 999, 
                set_tau_shp=999, 
                set_tau_rate=999, 
                prior_prec_log_irr = 999, 
                sd.upper=999
                )


source("jags_commensurate_prior.R")

if(rerun){
  # model w/ uninformative priors 
  jags.post.uninfo <- jags.model(textConnection(model_string_uninformative_priors), 
                          data = dataset_uninformative_priors,
                          n.chains = 3)

  samples.uninfo <- coda.samples(jags.post.uninfo, 
                          variable.names=c("int", "beta1"),
                          n.iter = 5000)
  saveRDS(samples.uninfo, "../data/jags/post/RSV_LRTI_hosp_uninfo.rds")
  
   # model w/ informative priors 
  jags.post.info <- jags.model(textConnection(model_string_informative_priors), 
                          data = dataset_informative_priors,
                          n.chains = 3)

  samples.info <- coda.samples(jags.post.info, 
                          variable.names=c("delta", "int", "beta1", "shared"),
                          n.iter = 5000)
  saveRDS(samples.info, "../data/jags/post/RSV_LRTI_hosp_info.rds")
  
}else{
  samples.uninfo <- readRDS("../data/jags/post/RSV_LRTI_hosp_uninfo.rds")
  samples.info <- readRDS("../data/jags/post/RSV_LRTI_hosp_info.rds")
}


## process jags output 

# uninformative priors 
post1 <- as.data.frame(as.matrix(samples.uninfo[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples.uninfo[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples.uninfo[[3]][-c(1:4500),])) 
post.uninfo <- bind_rows(post1, post2, post3)

ve.median.uninfo <- round((1 - exp(median(post.uninfo$beta1)))*100,1)
ve.lb.uninfo <- round((1 - exp(quantile(post.uninfo$beta1, 0.975))) *100,1)
ve.ub.uninfo <- round((1 - exp(quantile(post.uninfo$beta1, 0.025)))*100, 1)

# informative priors 
post1 <- as.data.frame(as.matrix(samples.info[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples.info[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples.info[[3]][-c(1:4500),])) 
post.info <- bind_rows(post1, post2, post3)

ve.median.info <- round((1 - exp(median(post.info$beta1)))*100,1)
ve.lb.info <- round((1 - exp(quantile(post.info$beta1, 0.975))) *100,1)
ve.ub.info <- round((1 - exp(quantile(post.info$beta1, 0.025)))*100, 1)

shared.median.RSVLRTIhosp <- median(post.info$shared)

# fill in results
row_index <- 2
df.orig.trial$ve_uninfo_median[row_index] <- ve.median.uninfo
df.orig.trial$ve_uninfo_lb[row_index] <- ve.lb.uninfo
df.orig.trial$ve_uninfo_ub[row_index] <- ve.ub.uninfo
df.orig.trial$ve_info_median[row_index] <- ve.median.info
df.orig.trial$ve_info_lb[row_index] <- ve.lb.info
df.orig.trial$ve_info_ub[row_index] <- ve.ub.info

# show results 
df.orig.trial[row_index,] %>%  
  mutate(ve_trial = paste0(ve_trial_median, " (", ve_trial_lb, "-", ve_trial_ub, ")")) %>%
  mutate(ve_cc_uninformative_priors = paste0(ve_uninfo_median, " (", ve_uninfo_lb, "-", ve_uninfo_ub, ")")) %>%
  mutate(ve_cc_informative_priors = paste0(ve_info_median, " (", ve_info_lb, "-", ve_info_ub, ")")) %>%
  mutate(shared = round(shared.median.RSVLRTIhosp,3)) %>%
  dplyr::select(outcome, ve_trial, ve_cc_uninformative_priors, ve_cc_informative_priors, shared) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T) 
  

# look at traceplot of coefficient of vax variable
plot(samples.uninfo[, "beta1"])
title("beta1 (uninformative priors)")

plot(samples.info[, "beta1"])
title("beta1 (informative priors)")
```

#### Medically attended all-cause LRTI (Hammitt et al)
  * extracted from case-control: records with LRTI symptoms as cases vs. those without LRTI symptoms as controls
```{r}
####################################################
# Medically attended all-cause LRTI as endpoint (Hammitt et al)
####################################################
df.jags <- df %>% 
  mutate(case_control = case_when(symp_LRT_distress == 1 ~ 1,
                                  is.na(symp_LRT_distress) ~ 0)) %>%
  filter(!is.na(cf_birth_weight) & !is.na(cf_gestage))


dataset_uninformative_priors <- 
            list(
                # from current case-control
                N_people = nrow(df.jags),
                case_status = df.jags$case_control,
                vax = df.jags$rsv_mab,
                # confounders
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4,
                cf_birth_weight = df.jags$cf_birth_weight,
                cf_gestage = df.jags$cf_gestage
                )

dataset_informative_priors <- 
            list(
                # from previous study
                N_cases_orig = c(62, 60), # (case_placebo, case_vax)
                pop_orig = c(342, 686), # (N_placebo, N_vax)
                # from current case-control
                N_people = nrow(df.jags),
                case_status = df.jags$case_control,
                vax = df.jags$rsv_mab,
                # confounders
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4,
                cf_birth_weight = df.jags$cf_birth_weight,
                cf_gestage = df.jags$cf_gestage,
                # others
                prior_mean_log_irr = 999, 
                set_tau_shp=999, 
                set_tau_rate=999, 
                prior_prec_log_irr = 999, 
                sd.upper=999
                )


source("jags_commensurate_prior.R")

if(rerun){
  # model w/ uninformative priors 
  jags.post.uninfo <- jags.model(textConnection(model_string_uninformative_priors), 
                          data = dataset_uninformative_priors,
                          n.chains = 3)

  samples.uninfo <- coda.samples(jags.post.uninfo, 
                          variable.names=c("int", "beta1"),
                          n.iter = 5000)
  saveRDS(samples.uninfo, "../data/jags/post/all_cause_LRTI_uninfo.rds")
  
   # model w/ informative priors 
  jags.post.info <- jags.model(textConnection(model_string_informative_priors), 
                          data = dataset_informative_priors,
                          n.chains = 3)

  samples.info <- coda.samples(jags.post.info, 
                          variable.names=c("delta", "int", "beta1", "shared"),
                          n.iter = 5000)
  saveRDS(samples.info, "../data/jags/post/all_cause_LRTI_info.rds")
  
}else{
  samples.uninfo <- readRDS("../data/jags/post/all_cause_LRTI_uninfo.rds")
  samples.info <- readRDS("../data/jags/post/all_cause_LRTI_info.rds")
}


## process jags output 

# uninformative priors 
post1 <- as.data.frame(as.matrix(samples.uninfo[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples.uninfo[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples.uninfo[[3]][-c(1:4500),])) 
post.uninfo <- bind_rows(post1, post2, post3)

ve.median.uninfo <- round((1 - exp(median(post.uninfo$beta1)))*100,1)
ve.lb.uninfo <- round((1 - exp(quantile(post.uninfo$beta1, 0.975))) *100,1)
ve.ub.uninfo <- round((1 - exp(quantile(post.uninfo$beta1, 0.025)))*100, 1)

# informative priors 
post1 <- as.data.frame(as.matrix(samples.info[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples.info[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples.info[[3]][-c(1:4500),])) 
post.info <- bind_rows(post1, post2, post3)

ve.median.info <- round((1 - exp(median(post.info$beta1)))*100,1)
ve.lb.info <- round((1 - exp(quantile(post.info$beta1, 0.975))) *100,1)
ve.ub.info <- round((1 - exp(quantile(post.info$beta1, 0.025)))*100, 1)

shared.median.allcauseLRTI <- median(post.info$shared)

# fill in results
row_index <- 3
df.orig.trial$ve_uninfo_median[row_index] <- ve.median.uninfo
df.orig.trial$ve_uninfo_lb[row_index] <- ve.lb.uninfo
df.orig.trial$ve_uninfo_ub[row_index] <- ve.ub.uninfo
df.orig.trial$ve_info_median[row_index] <- ve.median.info
df.orig.trial$ve_info_lb[row_index] <- ve.lb.info
df.orig.trial$ve_info_ub[row_index] <- ve.ub.info

# show results 
df.orig.trial[row_index,] %>%  
  mutate(ve_trial = paste0(ve_trial_median, " (", ve_trial_lb, "-", ve_trial_ub, ")")) %>%
  mutate(ve_cc_uninformative_priors = paste0(ve_uninfo_median, " (", ve_uninfo_lb, "-", ve_uninfo_ub, ")")) %>%
  mutate(ve_cc_informative_priors = paste0(ve_info_median, " (", ve_info_lb, "-", ve_info_ub, ")")) %>%
  mutate(shared = round(shared.median.allcauseLRTI, 3)) %>%
  dplyr::select(outcome, ve_trial, ve_cc_uninformative_priors, ve_cc_informative_priors, shared) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T) 
  

# look at traceplot of coefficient of vax variable
plot(samples.uninfo[, "beta1"])
title("beta1 (uninformative priors)")

plot(samples.info[, "beta1"])
title("beta1 (informative priors)")
```


#### RSV-related respiratory hospitalizations (Hammitt et al)
  * extracted from case-control: RSV-positive hospitalizations as cases vs. RSV- as controls
```{r}
####################################################
# RSV-related respiratory hospitalization as endpoint (Hammitt et al)
####################################################
df.jags <- df %>% 
  filter(encounter_type == "inpatient") %>%
  mutate(case_control = positive_rsv) %>% 
  filter(!is.na(case_control)) %>%
  filter(!is.na(cf_birth_weight) & !is.na(cf_gestage))


dataset_uninformative_priors <- 
            list(
                # from current case-control
                N_people = nrow(df.jags),
                case_status = df.jags$case_control,
                vax = df.jags$rsv_mab,
                # confounders
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4,
                cf_birth_weight = df.jags$cf_birth_weight,
                cf_gestage = df.jags$cf_gestage
                )

dataset_informative_priors <- 
            list(
                # from previous study
                N_cases_orig = c(11, 9), # (case_placebo, case_vax)
                pop_orig = c(342, 686), # (N_placebo, N_vax)
                # from current case-control
                N_people = nrow(df.jags),
                case_status = df.jags$case_control,
                vax = df.jags$rsv_mab,
               # confounders
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4,
               cf_birth_weight = df.jags$cf_birth_weight,
                cf_gestage = df.jags$cf_gestage,
                # others
                prior_mean_log_irr = 999, 
                set_tau_shp=999, 
                set_tau_rate=999, 
                prior_prec_log_irr = 999, 
                sd.upper=999
                )


source("jags_commensurate_prior.R")

if(rerun){
  # model w/ uninformative priors 
  jags.post.uninfo <- jags.model(textConnection(model_string_uninformative_priors), 
                          data = dataset_uninformative_priors,
                          n.chains = 3)

  samples.uninfo <- coda.samples(jags.post.uninfo, 
                          variable.names=c("int", "beta1"),
                          n.iter = 5000)
  saveRDS(samples.uninfo, "../data/jags/post/RSV_hosp_uninfo.rds")
  
   # model w/ informative priors 
  jags.post.info <- jags.model(textConnection(model_string_informative_priors), 
                          data = dataset_informative_priors,
                          n.chains = 3)

  samples.info <- coda.samples(jags.post.info, 
                          variable.names=c("delta", "int", "beta1", "shared"),
                          n.iter = 5000)
  saveRDS(samples.info, "../data/jags/post/RSV_hosp_info.rds")
  
}else{
  samples.uninfo <- readRDS("../data/jags/post/RSV_hosp_uninfo.rds")
  samples.info <- readRDS("../data/jags/post/RSV_hosp_info.rds")
}


## process jags output 

# uninformative priors 
post1 <- as.data.frame(as.matrix(samples.uninfo[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples.uninfo[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples.uninfo[[3]][-c(1:4500),])) 
post.uninfo <- bind_rows(post1, post2, post3)

ve.median.uninfo <- round((1 - exp(median(post.uninfo$beta1)))*100,1)
ve.lb.uninfo <- round((1 - exp(quantile(post.uninfo$beta1, 0.975))) *100,1)
ve.ub.uninfo <- round((1 - exp(quantile(post.uninfo$beta1, 0.025)))*100, 1)

# informative priors 
post1 <- as.data.frame(as.matrix(samples.info[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples.info[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples.info[[3]][-c(1:4500),])) 
post.info <- bind_rows(post1, post2, post3)

ve.median.info <- round((1 - exp(median(post.info$beta1)))*100,1)
ve.lb.info <- round((1 - exp(quantile(post.info$beta1, 0.975))) *100,1)
ve.ub.info <- round((1 - exp(quantile(post.info$beta1, 0.025)))*100, 1)

shared.median.RSVhosp <- median(post.info$shared)

# fill in results
row_index <- 4
df.orig.trial$ve_uninfo_median[row_index] <- ve.median.uninfo
df.orig.trial$ve_uninfo_lb[row_index] <- ve.lb.uninfo
df.orig.trial$ve_uninfo_ub[row_index] <- ve.ub.uninfo
df.orig.trial$ve_info_median[row_index] <- ve.median.info
df.orig.trial$ve_info_lb[row_index] <- ve.lb.info
df.orig.trial$ve_info_ub[row_index] <- ve.ub.info

# show results 
df.orig.trial[row_index,] %>%  
  mutate(ve_trial = paste0(ve_trial_median, " (", ve_trial_lb, "-", ve_trial_ub, ")")) %>%
  mutate(ve_cc_uninformative_priors = paste0(ve_uninfo_median, " (", ve_uninfo_lb, "-", ve_uninfo_ub, ")")) %>%
  mutate(ve_cc_informative_priors = paste0(ve_info_median, " (", ve_info_lb, "-", ve_info_ub, ")")) %>%
  mutate(shared = round(shared.median.RSVhosp, 3)) %>%
  dplyr::select(outcome, ve_trial, ve_cc_uninformative_priors, ve_cc_informative_priors, shared) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T) 
  

# look at traceplot of coefficient of vax variable
plot(samples.uninfo[, "beta1"])
title("beta1 (uninformative priors)")

plot(samples.info[, "beta1"])
title("beta1 (informative priors)")
```


<br>

### Compare the results 
```{r, fig.height=5, fig.width=7}
df.compare <- df.orig.trial[1:4,] %>%
  dplyr::select(outcome, 
                ve_trial_median, ve_trial_lb, ve_trial_ub, 
                ve_uninfo_median, ve_uninfo_lb, ve_uninfo_ub,
                ve_info_median, ve_info_lb, ve_info_ub, )

# display the table 
df.compare %>% 
  mutate(ve_trial = paste0(ve_trial_median, " (", ve_trial_lb, "-", ve_trial_ub, ")")) %>%
  mutate(ve_cc_uninformative_priors = paste0(ve_uninfo_median, " (", ve_uninfo_lb, "-", ve_uninfo_ub, ")")) %>%
  mutate(ve_cc_informative_priors = paste0(ve_info_median, " (", ve_info_lb, "-", ve_info_ub, ")")) %>%
  mutate(shared = c(shared.median.RSVLRTI, shared.median.RSVLRTIhosp, 
                    shared.median.allcauseLRTI, shared.median.RSVhosp)) %>%
  dplyr::select(outcome, ve_trial, ve_cc_uninformative_priors, ve_cc_informative_priors, shared) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T) 


# display the figure
colnames(df.compare) <- str_replace(colnames(df.compare), "ve_", "")

plt.compare <- df.compare %>% 
  pivot_longer(cols = 2:10, 
               names_sep = '\\_', 
               names_to = c("source", "metric")) %>%
  pivot_wider(names_from = "metric", values_from = "value") %>% 
  mutate(source = case_when(source == "trial" ~ "Phase III trial",
                            source == "uninfo" ~ "Current case-control with uninformative priors",
                            source == "info" ~ "Current case-control with Phase III trial data as informative priors")) %>%
  mutate(source = factor(source, levels = c(
    "Phase III trial",
    "Current case-control with uninformative priors",
    "Current case-control with Phase III trial data as informative priors"
  ))) %>%
  mutate(outcome = case_when(outcome == "Medically attended RSV LRTI" ~ "Medically attended \nRSV LRTI",
                             outcome == "RSV-related LRTI hospitalization" ~ "RSV-related LRTI \n hospitalization",
                             outcome == "Medically attended all-cause LRTI" ~ "Medically attended\n all-cause LRTI",
                             outcome == "RSV-related respiratory hospitalization" ~ "RSV-related \nhospitalization")) %>%
  ggplot() +
  geom_point(aes(x = outcome, y = median, color = source), position = position_dodge(0.5)) +
  geom_errorbar(aes(x = outcome, ymin = lb, ymax = ub, color = source), position = position_dodge(0.5),
                width = 0.2) +
  theme(legend.position = "top", 
        legend.direction = "vertical",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")
        ) +
  scale_color_brewer(palette = "Dark2") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("Clinical endpoint") + ylab("Efficacy / Effectiveness of \nNirsevimab (%)") +
  labs(color = "Source of estimation") +
  # add notations
  # all-cause LRTI 
  geom_segment(aes(x = 0.83, xend = 1, y = 100 , yend = 100), size = 0.2) +
  geom_segment(aes(x = 0.83, xend = 0.83, y = 100, yend = 97), size = 0.2) +
  geom_segment(aes(x = 1, xend = 1, y = 100, yend = 97), size = 0.2) +
  geom_text(aes(x = (0.83+1)/2, y = 105, label = as.character(round(shared.median.allcauseLRTI,2)) ),
            check_overlap = TRUE, size = 3.5) +
  # RSV LRTI
  geom_segment(aes(x = 1.83, xend = 2, y = 100 , yend = 100), size = 0.2) +
  geom_segment(aes(x = 1.83, xend = 1.83, y = 100, yend = 97), size = 0.2) +
  geom_segment(aes(x = 2, xend = 2, y = 100, yend = 97), size = 0.2) +
  geom_text(aes(x = (1.83+2)/2, y = 105, label = as.character(round(shared.median.RSVLRTI,2)) ),
            check_overlap = TRUE, size = 3.5) +
  # RSV hosp
  geom_segment(aes(x = 2.83, xend = 3, y = 100 , yend = 100), size = 0.2) +
  geom_segment(aes(x = 2.83, xend = 2.83, y = 100, yend = 97), size = 0.2) +
  geom_segment(aes(x = 3, xend = 3, y = 100, yend = 97), size = 0.2) +
  geom_text(aes(x = (2.83+3)/2, y = 105, label = as.character(round(shared.median.RSVhosp,2)) ),
            check_overlap = TRUE, size = 3.5) +
  # RSV LRTI hosp
  geom_segment(aes(x = 3.83, xend = 4, y = 100 , yend = 100), size = 0.2) +
  geom_segment(aes(x = 3.83, xend = 3.83, y = 100, yend = 97), size = 0.2) +
  geom_segment(aes(x = 4, xend = 4, y = 100, yend = 97), size = 0.2) +
  geom_text(aes(x = (3.83+4)/2, y = 105, label = as.character(round(shared.median.RSVLRTIhosp,2)) ),
            check_overlap = TRUE, size = 3.5)
  
  

plt.compare

if(savenewplot){
  ggsave(plot = plt.compare, filename = "../figs_tabs/figures/ve.sequential.addshared.pdf", height = 5, width = 7)
}
```





















