---
title: "VE of Nirsevimab"
output: 
  html_document:
    toc: true
    toc_float: true
---

#### Date: `r Sys.Date()`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

library(dplyr)
library(tidyr)
library(tidyverse)
library(readxl)
library(writexl)
library(reactable)
library(ggplot2)
library(stringr)
library(flextable)
library(lubridate)
library(MASS)
library(smd)


library(gtsummary) # for table 1
library(multcomp)
library(survival) # for matched case-control

fig.counter <- 1
tab.counter <- 1

source("utils_mAb_VE.R")

savenewplot <- FALSE
```


```{r}
# read in dataset
df <- read.csv("../data/clean_data/df.mab.csv") %>% 
  mutate(collection_date = as.Date(collection_date))
colnames <- as.data.frame(colnames(df))

# add some variables 
df <- process_df(df)
```


### There are totally `r nrow(df)` testing records in the analysis dataset. 

### Figure `r fig.counter`. Look at distribution of testing by time 
```{r, fig.width = 8, fig.height = 4}
fig.counter <- fig.counter + 1

plt.collection.date <- 
  df %>% 
  filter(collection_date >= as.Date("2023-10-1")) %>%
  mutate(positive_rsv = ifelse(positive_rsv == 1, "Case", "Control")) %>%
  mutate(positive_rsv = factor(positive_rsv, levels = c("Control", "Case"))) %>%
  ggplot() +
  geom_histogram(aes(x = collection_date, fill = factor(positive_rsv)), color = "black",
                 binwidth = 7) +
  scale_x_date(date_breaks = "1 month", date_labels = "%Y-%m",
               limits = as.Date(c("2023-9-30", "2024-05-14"))) +
  theme_classic() +
  xlab("Time of sample collection for RSV test") +
  ylab("Number of RSV test records")  +
  labs(fill = "Case status") +
  scale_fill_brewer(palette = "Set2") +
  geom_vline(xintercept = as.Date("2023-10-1"), linetype = "dashed")  +
  geom_text(aes(x = as.Date("2023-10-5"), y = 140, vjust = 0.8,
                label = "Nirsevimab \nadministration\n started"), 
            angle = 90, size = 3.5, fontface = "plain", 
            check_overlap = TRUE, lineheight = 0.75) +
  theme(legend.position = "top")


plt.collection.date
  
if(savenewplot){
  ggsave(plot = plt.collection.date, filename = "../figs_tabs/figures/plt.collection.date.pdf", height = 4, width = 8)
}
```

<br>

### Figure `r fig.counter`. Let's look at the distribution of immunization date, and see why coverage is so low?
```{r}
fig.counter <- fig.counter + 1

plt.vax.time <- 
  df %>% 
  filter(rsv_mab == 1) %>% 
  mutate(mab_date = as.Date(mab_date)) %>%
  ggplot() +
  geom_histogram(aes(x = mab_date, fill = rsv_mab_dose), color = "black", binwidth = 7) +
  scale_x_date(date_breaks = "1 month", date_labels = "%Y-%m") + 
  theme_classic() +
  xlab("Time of nirsevimab immunization") +
  ylab("Count")  +
  geom_vline(xintercept = as.Date("2023-10-1"), linetype = "dashed")  +
  geom_text(aes(x = as.Date("2023-10-5"), y = 32, vjust = 0.8, lineheight = 0.75,
                label = "Nirsevimab \nadministration \nstarted"), 
            angle = 90, size = 3.5, fontface = "plain", check_overlap = TRUE) +
  scale_x_date(date_breaks = "1 month", date_labels = "%Y-%m",
               limits = as.Date(c("2023-9-30", "2024-05-14"))) +
  theme(legend.position = "top") +
  scale_fill_brewer(palette = "Set1" ) +
  labs(fill = "Nirsevimab dosage")


plt.vax.time

if(savenewplot){
  ggsave(plot = plt.vax.time, filename = "../figs_tabs/figures/plt.vax.time.pdf", height = 4, width = 8)
}
```

### combine the above two plots in one figure
```{r, fig.width = 8, fig.height = 8}
plt.collection.vaxtime <- plot_grid(plt.collection.date, plt.vax.time,
          labels = c("A.", "B."), 
          ncol = 1, align = "v", rel_heights = c(5:4))

plt.collection.vaxtime

if(savenewplot){
  ggsave(plot = plt.collection.vaxtime, filename = "../figs_tabs/figures/plt.collection.vaxtime.pdf", height = 8, width = 8)
}

```

<br>

### (revision) look at breakdown by eligibility 

```{r}
# those born into the new season (born after 10.1.2023)
df.1 <- df %>% filter(DOB >= as.Date("2023-10-1"))
nrow(df.1) # 685


# those aged 8-12 months with risk factors when entering the season
df.2 <- df %>% filter(as.Date("2023-10-1") - as.Date(DOB) > 8 * 30.44  & 
                        as.Date("2023-10-1") - as.Date(DOB) <= 12 * 30.44) %>%
  filter(risk_factor_atleastone == "yes")
nrow(df.2) # 219


# those under 8 when entering the season
nrow(df) - nrow(df.1) - nrow(df.2) # 2186
```

<br>

### (revision) Maternal vax vaccinated individuals 

```{r}
df_maternal <- 
  df %>% filter(mom_rsv_vaxed == 1) %>%
  dplyr::select(mom_rsv_vaxed_date, DOB, rsv_mab, collection_date, positive_rsv) %>%
  mutate(transfer_time = as.Date(DOB) - as.Date(mom_rsv_vaxed_date)) %>% 
  arrange(rsv_mab, positive_rsv) %>%
  mutate(mom_rsv_vaxed_date = as.Date(mom_rsv_vaxed_date)) 
 #mutate(across(c(mom_rsv_vaxed_date, DOB, collection_date), ~ as.Date(., format = "%m/%d/%Y"))) 

median(df_maternal$transfer_time)

tab_maternal <- df_maternal %>% flextable()

# save_as_docx(tab_maternal, path = "../figs_tabs/tables/maternal_vaxed.docx")


```

<br>

### (revision) Look at records by hospital 
  * There are five hospital delivery networks and associated outpatient clinics. 
```{r}
# classify the individual records to hospital system

# BH: Bridgeport Hospital, this also includes MC (milford campus)
# GH: Greenwich Hospital
# YNH: Yale New Haven Hospital (this also includes FHC)
# LMH: Lawrence + Memorial Hospital (NY)
# WH: Westerly Hospital (RI)


df <- df %>%
  mutate(hospital =
           case_when(
             Admission.Location %in% c("BH 112 QUARRY RD",
                                       "BH 267 GRANT ST",
                                       "BH 309 STILLSON RD",
                                       "MC 300 SEASIDE AVE",
                                       "MC 831 BOSTON POST RD",
                                       "NE 112 QUARRY ROAD",
                                       "YNH 226 MILL HILL AVE",
                                       "YNH 267 GRANT ST") ~ "Bridgeport Hospital",
             Admission.Location %in% c("FHC 150 SARGENT DR",
                                       "FHC 374 GRAND AVE",
                                       "NE 2200 WHITNEY AVE",
                                       "NE 633 MIDDLESEX TPKE",
                                       "SRC 1450 CHAPEL ST",
                                       "YNH 111 GOOSE LANE",
                                       "YNH 20 YORK ST")  ~ "Yale New Haven Hospital",
             Admission.Location %in% c("GH 5 PERRYRIDGE RD",
                                       "NE 90 SOUTH RIDGE ST") ~ "Greenwich Hospital",
             Admission.Location %in% c("LMH 365 MONTAUK AVE",
                                       "LMH 52 HAZELNUT HILL RD") ~ "Lawrence + Memorial Hospital",
             Admission.Location %in% c("NE 45 WELLS ST",
                                       "WH 25 WELLS ST") ~ "Westerly Hospital"
           ))

# for those unassigned, use "Collection department" variable to assign hospital 
df  <- df %>% 
  mutate(hospital = 
           case_when(Collection.Department %in% c("BH EMERGENCY DEPARTMENT") & is.na(hospital) ~ "Bridgeport Hospital",
                     Collection.Department %in% c("GH LABORATORY SPECIMENS") & is.na(hospital) ~ "Greenwich Hospital",
                     Collection.Department %in% c("LMH MAIN LABORATORY") & is.na(hospital) ~ "Lawrence + Memorial Hospital",
                     Collection.Department %in% c("WH DRAW STATION",
                                                  "WH DRAW STATION MORGAN BLDG",
                                                  "WH MAIN LABORATORY") & is.na(hospital) ~ "Westerly Hospital",
                     Collection.Department %in% c("YNH HOME DRAW", "YNH MAIN LAB") & is.na(hospital) ~ "Yale New Haven Hospital",
                     TRUE ~ hospital
                     ))

df %>% count(hospital)

```


<br>


### Look at the risk factors {.tabset}

#### Table `r tab.counter`  Each risk factor
```{r}
tab.counter <- tab.counter + 1

data.frame(
  anemia = nrow(df %>% filter(risk_factor_anemia == "yes")),
  blood = nrow(df %>% filter(risk_factor_blood == "yes")),
  immunodeficiency = nrow(df %>% filter(risk_factor_immunodeficiency == "yes")),
  cardiac = nrow(df %>% filter(risk_factor_cardiac == "yes")),
  pulmonary_disease = nrow(df %>% filter(risk_factor_pulmonary == "yes")),
  down_syndrome = nrow(df %>% filter(risk_factor_down == "yes")),
  small_for_gestage = nrow(df %>% filter(risk_factor_small_for_gestage == 1)),
  gestage_lessthan37wks = nrow(df %>% filter(risk_factor_gestagelessthan37wks == 1))
) %>%
  pivot_longer(cols = 1:8, names_to = "risk_factor", values_to = "n_records") %>%
  arrange(desc(n_records)) %>%
  mutate(perc = round(n_records / nrow(df)*100,1)) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

```

<br>


#### Table `r tab.counter` At least one risk factor 
```{r}
tab.counter <- tab.counter + 1

df %>% count(risk_factor_atleastone) %>%
 mutate(perc = round(n / nrow(df)*100,1)) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))


# filter out those with at least one risk factor 
# a <- df %>% filter(risk_factor_atleastone == "yes") %>% 
#   dplyr::select(StudyID, collection_date, positive_rsv, rsv_mab,
#                 starts_with("risk_factor"))

# write csv for checking
# write.csv(a, "../data/data_to_check/atleastoneriskfactor.csv", row.names = F)
```



<br>

### Table `r tab.counter`. Characteristic of study population (testing level) {.tabset}
  * this is assuming that: if mAb was taken before collection date, we count it as immunized. For SSA, need to change it to: if the person took mAb more than X days before sample collection, we count it as immunized.
  * we look at different pairs of case and control here (mainly to see which ones should be confounders).

#### RSV+ vs. RSV-
```{r}
tab.counter <- tab.counter + 1

df_table1 <- df %>%
  # add dose of mab 
  mutate(rsv_mab = case_when(rsv_mab_detailed == "100mg before collection" ~ "Yes, 100mg dose",
                             rsv_mab_detailed == "50mg before collection" ~ "Yes, 50mg dose",
                             TRUE ~ "No")) %>%
  mutate(risk_factor_gestagelessthan37wks = case_when(
    risk_factor_gestagelessthan37wks == 1 ~ "Less than 37 weeks",
    risk_factor_gestagelessthan37wks == 0 ~ "37 weeks or more"
  )) %>% 
  dplyr::select(positive_rsv,Sex, age_at_test_in_months, age_at_test_in_months_cat_2, race_ethnicity, birth_weight, insurance_type, rsv_mab, month_when_tested_cat, encounter_type, 
                # added hospital 
                hospital,
                # risk factors (main ones that are >= 5% prevalence)
                risk_factor_pulmonary, risk_factor_cardiac, risk_factor_asthma, risk_factor_anemia,
                risk_factor_gestagelessthan37wks,
                risk_factor_atleastone,
                symp_LRT_distress) %>% 
  mutate(positive_rsv = case_when(positive_rsv == 1 ~ "Cases",
                                  positive_rsv == 0 ~ "Controls")) %>%
  # to display the missing, making the NA value explicit level of factor 
  mutate(across(c(positive_rsv,
                  Sex, race_ethnicity, insurance_type, rsv_mab, 
                risk_factor_atleastone, risk_factor_gestagelessthan37wks), ~ factor(.) %>% forcats::fct_explicit_na())) %>% 
  mutate(hospitalization = ifelse(encounter_type != "outpatient", "Hospitalized", "Not hospitalized")) %>%
  # re-rank variables 
  dplyr::select(positive_rsv, 
                Sex, age_at_test_in_months, age_at_test_in_months_cat_2, 
                month_when_tested_cat,
                #hospital,
                hospitalization,
                race_ethnicity, 
                birth_weight,
                risk_factor_gestagelessthan37wks,
                risk_factor_pulmonary, risk_factor_cardiac, risk_factor_anemia,
                risk_factor_atleastone,  insurance_type, rsv_mab, 
                encounter_type, 
                symp_LRT_distress)

df_table1_infection <- df_table1 %>% dplyr::select(-encounter_type, -symp_LRT_distress)

# footnotes 
footnote_otherraces <- "Inclusing Asian, Pacific Islander, Middle Eastern or Northern American, American Indian or Native American by self-reporting."
footnote_atleastoneriskfactor <- "Have at least one of the following conditions recorded in the infant's medical history or diagnosis records: 1) Anemia; 2) Immunodeficiency (e.g. transplantation history, leukemia, etc.); 3) Cardiac diseases (including congenital heart diseases diagnosed at birth or any reporting of heart conditions); 4) Pulmonary diseases; 5) Down syndrome; 6) Small for gestational age (birth weight < 2,500 grams); 7) Prematurity (gestational age less than 37 weeks)."


table1_infection <- df_table1_infection %>% 
  tbl_summary(by = positive_rsv,
              
              type = list(all_continuous() ~ "continuous2"),       # indicate that you want to print multiple statistics 
         statistic = list(all_continuous() ~ c("{mean} ({sd})", 
                                               "{median} ({p25}, {p75})",
                                               "{N_miss} ({p_miss}%)"),                 
                          all_categorical() ~ "{n} ({p}%)"),
         
              digits = list(all_categorical() ~ c(0, 1),
                            all_continuous() ~ 1),
         
              label  = list(  
                Sex ~ "Sex", 
                age_at_test_in_months ~ "Age at testing (months)",
                age_at_test_in_months_cat_2 ~ "Age at testing",
                month_when_tested_cat ~ "Time tested", 
                race_ethnicity ~ "Race and ethnicity",
                #hospital ~ "Hospital", 
                hospitalization ~ "Hospitalized",
                risk_factor_pulmonary ~ "Pulmonary diseases", 
                risk_factor_cardiac ~ "Cardiac diseases", 
                risk_factor_anemia ~ "Anemia",
                risk_factor_gestagelessthan37wks ~ "Gestational age",
                risk_factor_atleastone ~ "Having at least one risk factor",
                insurance_type ~ "Insurance type",
                rsv_mab ~ "mAb status",
                birth_weight ~ "Birth weight"
                ),
         
        missing_text = "Missing"
        #,
         #     percent = "row"
        #      missing= "no"
                      ) %>% 
  add_difference(everything() ~ "smd") %>%
  add_p(pvalue_fun = ~ style_pvalue(., digits = 3)) %>% 
  add_overall(last = F) %>%
  bold_labels() %>%
  modify_table_styling(
    columns = label,
    rows = label == "Other non-Hispanic",
    footnote = footnote_otherraces
                 ) %>%
  modify_table_styling(
    columns = label,
    rows = label == "Having at least one risk factor",
    footnote = footnote_atleastoneriskfactor
  )
  


table1_infection %>% as_flex_table() %>% 
  flextable::set_table_properties( width = 1, layout = "autofit") 
  
if(savenewplot){
  table1_infection %>%
    as_gt() %>%
    gt::gtsave(filename = "../figs_tabs/tables/table1_characteristics.docx")
}
```



<br>

### Clinical outcomes {.tabset}

####  Table `r tab.counter`.
Here we filtered out only the cases (RSV+) and compare between vaccinated and unvaccinated.
```{r}
tab.counter <- tab.counter + 1

df_table1_outcome <- df %>%
  # mutate(rsv_mab = case_when(rsv_mab_detailed == "100mg before collection" ~ "100mg dose",
  #                            rsv_mab_detailed == "50mg before collection" ~ "50mg dose",
  #                            TRUE ~ "Not vaccinated")) %>%
  mutate(rsv_mab = ifelse(rsv_mab == 1, "Vaccinated", "Unvaccinated")) %>%
  mutate(encounter_type = case_when(encounter_type %in% c("inpatient_unrelated", "outpatient") ~ "no",
                                    encounter_type == "inpatient" ~ "yes")) %>%
  mutate(icu_admitted = case_when(icu_admitted %in% c("yes_unrelated", "no") ~ "no",
                                  TRUE ~ "yes")) %>%
  mutate(hosp_los = ifelse(encounter_type == "no", NA, hosp_los)) %>%
  mutate(icu_los_days = ifelse(icu_admitted == "no", NA, icu_los_days)) %>%
  mutate(highflow_oxygen = case_when(highflow_oxygen == 1 ~ "yes",
                                     TRUE ~ "no")) %>% 
  mutate(across(starts_with("symp_"), ~ ifelse(is.na(.), "no", "yes"))) %>%
  mutate(positive_rsv = case_when(positive_rsv == 1 ~ "RSV+",
                                  positive_rsv == 0 ~ "RSV-")) %>%
  # to display the missing, making the NA value explicit level of factor 
  mutate(across(c(positive_rsv,
                   rsv_mab), ~ factor(.) %>% forcats::fct_explicit_na())) %>% 
  # re-rank variables 
  dplyr::select(rsv_mab, positive_rsv, hospital,
                encounter_type, hosp_los, icu_admitted, icu_los_days, highflow_oxygen,
                starts_with("symp_")) %>%
  filter(positive_rsv == "RSV+") %>% 
  dplyr::select(-positive_rsv)



table1_outcome <- df_table1_outcome %>% 
  tbl_summary(by = rsv_mab,
              
              type = list(all_continuous() ~ "continuous2"),       # indicate that you want to print multiple statistics 
         statistic = list(all_continuous() ~ c("{median} ({p25}, {p75})",
                                               "{N_miss} ({p_miss}%)"),                 
                          all_categorical() ~ "{n} ({p}%)"),
         
              digits = list(all_categorical() ~ c(0, 1),
                            all_continuous() ~ 1),
         
              label  = list(  
                hospital ~ "Hospital",
                encounter_type = "Hospital admission",
                hosp_los = "Duration of hospitalization (days)",
                icu_admitted = "ICU admission",
                icu_los_days = "Duration of ICU admission (days)",
                highflow_oxygen = "Required highflow oxygen support",
                symp_URT_distress = "Distress in URT",
                symp_LRT_distress = "Distress in LRT",
                symp_fever = "Fever (> 38°C/100.4°F)",
                symp_cough = "Cough",
                symp_wheezing = "Wheezing",
                symp_breathing = "Breathing difficulties",
                symp_bronchiolitis = "Bronchiolitis",
                symp_sepsis = "Sepsis"
                ),
         
        missing_text = "Missing"
        #,
         #     percent = "row"
        #      missing= "no"
                      ) %>% 
  #add_difference(everything() ~ "smd") %>%
  add_p(pvalue_fun = ~ style_pvalue(., digits = 3)) %>% 
  add_overall(last = F) %>%
  bold_labels() %>%
  modify_table_styling(
    columns = label,
    rows = label == "Other non-Hispanic",
    footnote = footnote_otherraces
  ) %>%
   modify_table_styling(
    columns = label,
    rows = label == "Having at least one risk factor",
    footnote = footnote_atleastoneriskfactor
  )


table1_outcome %>% as_flex_table() %>% 
  flextable::set_table_properties( width = 1, layout = "autofit") 

if(savenewplot){
  table1_outcome %>%
    as_gt() %>%
    gt::gtsave(filename = "../figs_tabs/tables/table2_clinical_outcomes.docx")
}
```

<br>


### compare between immunized vs. unimmunized
#### all infants (all ages)
```{r}
tab.counter <- tab.counter + 1

df_table1_immunize <- df_table1 %>% dplyr::select(-encounter_type, -symp_LRT_distress) %>% 
  mutate(rsv_mab_simple = ifelse(rsv_mab == "No", "Unimmunized", "Immunized"))


table1_immunize <- df_table1_immunize %>% 
  tbl_summary(by = rsv_mab_simple,
              
              type = list(all_continuous() ~ "continuous2"),       # indicate that you want to print multiple statistics 
         statistic = list(all_continuous() ~ c("{mean} ({sd})", 
                                               "{median} ({p25}, {p75})",
                                               "{N_miss} ({p_miss}%)"),                 
                          all_categorical() ~ "{n} ({p}%)"),
         
              digits = list(all_categorical() ~ c(0, 1),
                            all_continuous() ~ 1),
         
              label  = list(  
                Sex ~ "Sex", 
                age_at_test_in_months ~ "Age at testing (months)",
                age_at_test_in_months_cat_2 ~ "Age at testing",
                month_when_tested_cat ~ "Time tested", 
                race_ethnicity ~ "Race and ethnicity",
                risk_factor_pulmonary ~ "Pulmonary diseases", 
                risk_factor_cardiac ~ "Cardiac diseases", 
                risk_factor_anemia ~ "Anemia",
                risk_factor_gestagelessthan37wks ~ "Gestational age",
                risk_factor_atleastone ~ "Having at least one risk factor",
                insurance_type ~ "Insurance type",
                hospital ~ "Hospital",
                birth_weight ~ "Birth weight"
                ),
         
        missing_text = "Missing"
        #,
         #     percent = "row"
        #      missing= "no"
                      ) %>% 
  add_difference(everything() ~ "smd") %>%
  add_p(pvalue_fun = ~ style_pvalue(., digits = 3)) %>% 
  add_overall(last = F) %>%
  bold_labels() %>%
  modify_table_styling(
    columns = label,
    rows = label == "Other non-Hispanic",
    footnote = footnote_otherraces
                 ) %>%
  modify_table_styling(
    columns = label,
    rows = label == "Having at least one risk factor",
    footnote = footnote_atleastoneriskfactor
  )
  


table1_immunize %>% as_flex_table() %>% 
  flextable::set_table_properties( width = 1, layout = "autofit") 
  
if(savenewplot){
  table1_immunize %>%
    as_gt() %>%
    gt::gtsave(filename = "../figs_tabs/tables/table1_immunize.docx")
}
```

#### Born after 2023-10-1 (revised)
```{r}
tab.counter <- tab.counter + 1


temp <- df %>%
  #filter(abs(as.Date(mab_date) - as.Date(DOB)) <= 14)
  filter(DOB >= as.Date("2023-10-1")) %>%
  # add dose of mab 
  mutate(rsv_mab = case_when(rsv_mab_detailed == "100mg before collection" ~ "Yes, 100mg dose",
                             rsv_mab_detailed == "50mg before collection" ~ "Yes, 50mg dose",
                             TRUE ~ "No")) %>%
  mutate(risk_factor_gestagelessthan37wks = case_when(
    risk_factor_gestagelessthan37wks == 1 ~ "Less than 37 weeks",
    risk_factor_gestagelessthan37wks == 0 ~ "37 weeks or more"
  )) %>% 
  dplyr::select(positive_rsv,Sex, age_at_test_in_months, age_at_test_in_months_cat_2, race_ethnicity, birth_weight, insurance_type, rsv_mab, month_when_tested_cat, encounter_type, 
                # risk factors (main ones that are >= 5% prevalence)
                risk_factor_pulmonary, risk_factor_cardiac, risk_factor_asthma, risk_factor_anemia,
                risk_factor_gestagelessthan37wks,
                risk_factor_atleastone,
                symp_LRT_distress) %>% 
  mutate(positive_rsv = case_when(positive_rsv == 1 ~ "Cases",
                                  positive_rsv == 0 ~ "Controls")) %>%
  # to display the missing, making the NA value explicit level of factor 
  mutate(across(c(positive_rsv,
                  Sex, race_ethnicity, insurance_type, rsv_mab, 
                risk_factor_atleastone, risk_factor_gestagelessthan37wks), ~ factor(.) %>% forcats::fct_explicit_na())) %>% 
  # re-rank variables 
  dplyr::select(positive_rsv, 
                Sex, age_at_test_in_months, age_at_test_in_months_cat_2, 
                month_when_tested_cat,
                race_ethnicity, 
                birth_weight,
                risk_factor_gestagelessthan37wks,
                risk_factor_pulmonary, risk_factor_cardiac, risk_factor_anemia,
                risk_factor_atleastone,  insurance_type, rsv_mab, 
                encounter_type, 
                symp_LRT_distress)




df_table1_immunize_newborn <- temp %>% 
  dplyr::select(-encounter_type, -symp_LRT_distress) %>% 
  mutate(rsv_mab_simple = ifelse(rsv_mab == "No", "Unimmunized", "Immunized"))


table1_immunize_newborn <- df_table1_immunize_newborn %>% 
  tbl_summary(by = rsv_mab_simple,
              
              type = list(all_continuous() ~ "continuous2"),       # indicate that you want to print multiple statistics 
         statistic = list(all_continuous() ~ c("{mean} ({sd})", 
                                               "{median} ({p25}, {p75})",
                                               "{N_miss} ({p_miss}%)"),                 
                          all_categorical() ~ "{n} ({p}%)"),
         
              digits = list(all_categorical() ~ c(0, 1),
                            all_continuous() ~ 1),
         
              label  = list(  
                Sex ~ "Sex", 
                age_at_test_in_months ~ "Age at testing (months)",
                age_at_test_in_months_cat_2 ~ "Age at testing",
                month_when_tested_cat ~ "Time tested", 
                race_ethnicity ~ "Race and ethnicity",
                risk_factor_pulmonary ~ "Pulmonary diseases", 
                risk_factor_cardiac ~ "Cardiac diseases", 
                risk_factor_anemia ~ "Anemia",
                risk_factor_gestagelessthan37wks ~ "Gestational age",
                risk_factor_atleastone ~ "Having at least one risk factor",
                insurance_type ~ "Insurance type",
                birth_weight ~ "Birth weight"
                ),
         
        missing_text = "Missing"
        #,
         #     percent = "row"
        #      missing= "no"
                      ) %>% 
  add_difference(everything() ~ "smd") %>%
  add_p(pvalue_fun = ~ style_pvalue(., digits = 3)) %>% 
  add_overall(last = F) %>%
  bold_labels() %>%
  modify_table_styling(
    columns = label,
    rows = label == "Other non-Hispanic",
    footnote = footnote_otherraces
                 ) %>%
  modify_table_styling(
    columns = label,
    rows = label == "Having at least one risk factor",
    footnote = footnote_atleastoneriskfactor
  )
  


table1_immunize_newborn %>% as_flex_table() %>% 
  flextable::set_table_properties( width = 1, layout = "autofit") 
  
if(savenewplot){
  table1_immunize_under8m %>%
    as_gt() %>%
    gt::gtsave(filename = "../figs_tabs/tables/table1_immunize_under8m.docx")
}
```

<be>

### How hospitalization and ICU admission (and other factors) differ by hospital visited ?
```{r}
df_compare_hospital <- df %>%
  # mutate(rsv_mab = case_when(rsv_mab_detailed == "100mg before collection" ~ "100mg dose",
  #                            rsv_mab_detailed == "50mg before collection" ~ "50mg dose",
  #                            TRUE ~ "Not vaccinated")) %>%
  mutate(rsv_mab = ifelse(rsv_mab == 1, "Immunized", "Unimmunized")) %>%
  mutate(encounter_type = case_when(encounter_type %in% c("inpatient_unrelated", "outpatient") ~ "no",
                                    encounter_type == "inpatient" ~ "yes")) %>%
  mutate(icu_admitted = case_when(icu_admitted %in% c("yes_unrelated", "no") ~ "no",
                                  TRUE ~ "yes")) %>%
  mutate(hosp_los = ifelse(encounter_type == "no", NA, hosp_los)) %>%
  mutate(icu_los_days = ifelse(icu_admitted == "no", NA, icu_los_days)) %>%
  mutate(highflow_oxygen = case_when(highflow_oxygen == 1 ~ "yes",
                                     TRUE ~ "no")) %>% 
  mutate(across(starts_with("symp_"), ~ ifelse(is.na(.), "no", "yes"))) %>%
  mutate(positive_rsv = case_when(positive_rsv == 1 ~ "RSV+",
                                  positive_rsv == 0 ~ "RSV-")) %>%
  # to display the missing, making the NA value explicit level of factor 
  mutate(across(c(positive_rsv,
                   rsv_mab), ~ factor(.) %>% forcats::fct_explicit_na())) %>% 
  # re-rank variables 
  dplyr::select(rsv_mab, positive_rsv, hospital,
                encounter_type, 
                #hosp_los, 
                icu_admitted, 
                #icu_los_days, 
                highflow_oxygen,
                starts_with("symp_")
                ) %>% 
  # filter(positive_rsv == "RSV+") %>% 
  #dplyr::select(-positive_rsv)
  dplyr::select(-symp_sepsis)



table_compare_hospital <- df_compare_hospital %>% 
  tbl_summary(by = hospital,
              
              type = list(all_continuous() ~ "continuous2"),       # indicate that you want to print multiple statistics 
         statistic = list(all_continuous() ~ c("{median} ({p25}, {p75})",
                                               "{N_miss} ({p_miss}%)"),                 
                          all_categorical() ~ "{n} ({p}%)"),
         
              digits = list(all_categorical() ~ c(0, 1),
                            all_continuous() ~ 1),
         
              label  = list(  
                rsv_mab ~ "Nirsevimab immunization",
                positive_rsv ~ "RSV positive",
                #hospital ~ "Hospital",
                encounter_type = "Hospital admission",
                hosp_los = "Duration of hospitalization (days)",
                icu_admitted = "ICU admission",
                icu_los_days = "Duration of ICU admission (days)",
                highflow_oxygen = "Required highflow oxygen support",
                symp_URT_distress = "Distress in URT",
                symp_LRT_distress = "Distress in LRT",
                symp_fever = "Fever (> 38°C/100.4°F)",
                symp_cough = "Cough",
                symp_wheezing = "Wheezing",
                symp_breathing = "Breathing difficulties",
                symp_bronchiolitis = "Bronchiolitis"
                #symp_sepsis = "Sepsis"
                ),
         
        missing_text = "Missing"
        #,
         #     percent = "row"
        #      missing= "no"
                      ) %>% 
  #add_difference(everything() ~ "smd") %>%
  add_p(pvalue_fun = ~ style_pvalue(., digits = 3)) %>% 
  add_overall(last = F) %>%
  bold_labels() %>%
  modify_table_styling(
    columns = label,
    rows = label == "Other non-Hispanic",
    footnote = footnote_otherraces
  ) %>%
   modify_table_styling(
    columns = label,
    rows = label == "Having at least one risk factor",
    footnote = footnote_atleastoneriskfactor
  )


table_compare_hospital %>% as_flex_table() %>% 
  flextable::set_table_properties( width = 1, layout = "autofit") 

if(savenewplot){
  table_compare_hospital %>%
    as_gt() %>%
    gt::gtsave(filename = "../figs_tabs/tables/table_compare_hospital.docx")
}


```

<br>

### (revision) Address comments on missingness of prematurity and birth weight
```{r}
# among all the infants who missing for gestational age and birth weight, we checked the medical history / problem list ... vars for more information on the risk factors, check how many of these are missing for the medical hist ... vars

a <- df %>% filter(is.na(birth_weight) & is.na(risk_factor_gestage) & is.na(risk_factor_small_for_gestage))
nrow(a)

a %>% filter(is.na(Medical.History) &
               is.na(Problem.List) &
               is.na(Hospital.Problem.List)) %>% nrow()
```



From table1, there are four variables that are significantly different between the case and control (p < 0.05): age tested, month tested, premature (gestage < 37wk), birth weight. But because this is collinearity between prematurity and birth weight, only included one into the model. Because there is less missing in prematurity variable, thus included this instead of birth weight.
```{r}
library(corrplot)
library(car)


df.cor <- df %>% dplyr::select(
  positive_rsv,
  rsv_mab,
  age_at_test_in_months_cat_2, # 3-month interval
  month_when_tested_cat,
  race_ethnicity,
  birth_weight,
  risk_factor_gestagelessthan37wks,
  risk_factor_atleastone,
  insurance_type
) 
  
df.M <- df.cor %>% 
  dplyr::select(-positive_rsv, -rsv_mab) %>%
  mutate(age_at_test_in_months_cat_2 = case_when(age_at_test_in_months_cat_2 == "under 3m" ~ 1,
                                                 age_at_test_in_months_cat_2 == "3-6m" ~ 2,
                                                 age_at_test_in_months_cat_2 == "6-9m" ~ 3,
                                                 age_at_test_in_months_cat_2 == "9-12m" ~ 4,
                                                 age_at_test_in_months_cat_2 == "above 1 yo" ~ 5)) %>%
  mutate(month_when_tested_cat = case_when(month_when_tested_cat == "Oct-Nov" ~ 1,
                                           month_when_tested_cat == "Dec-Jan" ~ 2,
                                           month_when_tested_cat == "Feb-Mar" ~ 3,
                                           month_when_tested_cat == "April and after" ~ 4)) %>%
  mutate(insurance_type = case_when(insurance_type == "private" ~ 1, 
                                    insurance_type == "public" ~ 2,
                                    insurance_type == "uninsured" ~ 3)) %>%
  mutate(race_ethnicity = case_when(race_ethnicity == "Hispanic" ~ 1,
                                    race_ethnicity == "White non-Hispanic" ~ 2,
                                    race_ethnicity == "Black non-Hispanic" ~ 3,
                                    race_ethnicity == "Other non-Hispanic" ~ 4,
                                    race_ethnicity == "unknown" ~5 )) %>%
  mutate(risk_factor_atleastone = ifelse(risk_factor_atleastone == "yes", 1, 0)) %>%
  rename(`Age tested` = age_at_test_in_months_cat_2,
         `Month tested` = month_when_tested_cat,
         `Birth weight` = birth_weight, 
         `Prematurity` = risk_factor_gestagelessthan37wks,
         `Race` = race_ethnicity,
         `>=1 risk factor` = risk_factor_atleastone,
         `Insurance type` = insurance_type)

M <- cor(df.M, use = "complete.obs")
pdf(file = "../figs_tabs/figures/corr.pdf", width = 5, height = 5)
corrplot(M, method = 'number') # thus prematurity and small for gest age are correlated
dev.off()

M.removebw <- cor(df.M %>% dplyr::select(-`Birth weight`, -Prematurity), use = "complete.obs")
pdf(file = "../figs_tabs/figures/corr_removebw.pdf", width = 5, height = 5)
corrplot(M.removebw, method = 'number', tl.col = "black") # thus prematurity and small for gest age are correlated
dev.off()


pdf(file = "../figs_tabs/figures/corr_comb.pdf", width = 10, height = 5)
par(mfrow=c(1,2))
corrplot(M, method = 'number', tl.col = "black")
mtext("A.", at = 0, line = 0, cex=2)
corrplot(M.removebw, method = 'number', tl.col = "black")
mtext("B.", at = 0, line = 0, cex=2)
dev.off()

```


<br>

```{r}
# recode symp_LRT_distress to have 1 and 0 (previously 1 and NA, will create some issue when counting records in analysis)
df <- df %>%
  mutate(symp_LRT_distress = ifelse(is.na(symp_LRT_distress), 0, 1))

# for the missing value in gest age cat, change the NA --> 999
df <- df %>% 
  mutate(risk_factor_gestagelessthan37wks = ifelse(is.na(risk_factor_gestagelessthan37wks), 999, risk_factor_gestagelessthan37wks))
```


### Selection of confounders included in the adjusted model {.tabset}
Using stepwise (both directions) to select the model using AIC

#### RSV infection
```{r echo=T}
temp <- df 

all_confounders <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat",
  "race_ethnicity",
  "risk_factor_atleastone",
  "insurance_type"
)



formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
)
step.model$anova

aic.infection <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)



# for revision 
# does AIC select "hospital" as potential confounder?
# all_confounders_addhosp <- c(all_confounders, "hospital")
# 
# formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_addhosp), collapse = " + "))
# full.model <- glm(formula, data = temp, family = "binomial")
# step.model <- stepAIC(full.model,
#                       scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat,
#                                    upper = formula),
#                       direction = "backward", trace = FALSE)
# 
# step.model$anova
# 
# aic.infection <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>%
#   mutate(endpoint = "Medically attended RSV infection") %>%
#   mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>%
#   rename(Confounders = Step)

```

#### ED visit as outcome
```{r echo=T}
temp <- df %>% filter(encounter_type == "outpatient")
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_ed <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
)
step.model$anova

aic.ed <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "RSV-associated outpatient visit") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)
```

#### inpatient as outcome 
```{r echo=T}
temp <- df %>% filter(encounter_type == "inpatient")
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_inpatient <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat",
  "risk_factor_atleastone"
)
step.model$anova

aic.inpatient <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "RSV-associated hospitalization") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)



# revision: should hospital be included as confounder?
temp <- df %>% filter(encounter_type == "inpatient")
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_addhosp), collapse = " + "))
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model,
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_inpatient <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat",
  "risk_factor_atleastone"
)
step.model$anova

aic.inpatient <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "RSV-associated hospitalization") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

```

#### severe presentations as outcome
```{r echo=T}
temp <- df %>% filter(icu_admitted == "yes" | highflow_oxygen == 1)
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_severe <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat",
  "risk_factor_atleastone"
)
step.model$anova

aic.severe <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "RSV-associated severe outcomes") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

# revision: should hospital be included as confounder?
temp <- df %>% filter(icu_admitted == "yes" | highflow_oxygen == 1)
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_addhosp), collapse = " + "))
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model,
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_severe <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat",
  "risk_factor_atleastone"
)
aic.severe <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "RSV-associated severe outcomes") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

```

#### LRTI
```{r echo=T}
temp <- df %>% filter(symp_LRT_distress == 1)
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_LRTI <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat",
  "risk_factor_atleastone"
)
step.model$anova

aic.LRTI <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "RSV-associated LRTI") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)
```

#### LRTI hospitalizations
```{r echo=T}
temp <- df %>% filter(symp_LRT_distress == 1 & encounter_type == "inpatient")
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_LRTIhosp <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat",
  "risk_factor_atleastone"
)
step.model$anova

aic.LRTIhosp <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "RSV-associated LRTI hospitalization") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)


# revision: should hospital be included as confounder?
temp <- df %>% filter(symp_LRT_distress == 1 & encounter_type == "inpatient")
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_addhosp), collapse = " + "))
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model,
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_LRTIhosp <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat",
  "risk_factor_atleastone"
)
aic.LRTIhosp <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "RSV-associated LRTI hospitalization") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)
```

#### save the AIC comparison in the backward selection process for each outcome 
```{r}
tab.aic <- 
  rbind(aic.infection,
      aic.ed,
      aic.inpatient,
      aic.severe, 
      aic.LRTI, 
      aic.LRTIhosp) %>%
  mutate(AIC = round(AIC,1)) %>%
  dplyr::select(endpoint, Confounders, AIC) %>%
  # rename some confounders
  mutate(Confounders = str_replace(Confounders, "age_at_test_in_months_cat_2", "age_tested")) %>%
  mutate(Confounders = str_replace(Confounders, "month_when_tested_cat", "month_tested")) %>%
  mutate(Confounders = str_replace(Confounders, "risk_factor_gestagelessthan37wks", "prematurity")) %>%
  mutate(Confounders = str_replace(Confounders, "risk_factor_atleastone", "atleastone_risk_factor")) %>%
  flextable() %>%
  width(j = 1, width = 2) %>%
  width(j = 2, width = 6) %>%
  merge_at(j = 1, i = 1:4) %>%
  merge_at(j = 1, i = 5:8) %>%
  merge_at(j = 1, i = 9:11) %>%
  merge_at(j = 1, i = 12:14) %>%
  merge_at(j = 1, i = 15:17) %>%
  merge_at(j = 1, i = 18:20) %>%
  vline() %>%
  hline()
  
tab.aic

if(savenewplot){
  save_as_docx(tab.aic, path = "../figs_tabs/tables/AIC.docx")
}

```

<br>

### Table `r tab.counter`. Effectiveness of Nirsevimab {.tabset}
##### Here, I pooled all the cases and controls together, to estimate the VE for different pairs of case and control definitions.
  * Columns n_overall, n_cases, n_controls are numbers of individuals were sample size used in the analysis. 
    + The sample size outside the parenthesis is the sample size that contributes to estimates of **unadjusted** effectiveness in the logistic regression models.
    + The sample size inside the parenthesis is the sample size that effectively contributes to estimates of **adjusted** effectiveness in the logistic regression models.
    + look at nirsevimab's effectiveness against: 
      + RSV infection 
      + RSV-associated ED visit (outpatient)
      + RSV-associated hospitalizations
      + RSV-associated LRTI
      + RSV-associated LRTI hospitalizations
      + RSV-associated ICU admissions
      + RSV-associated severe disease
     
#### Table `r tab.counter`. 
```{r warning=F}
tab.counter <- tab.counter + 1
##########################
# Against RSV infection (inpatient + outpatient)
##########################
df.ve <- df %>% mutate(case_control = positive_rsv)

ve.1 <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended RSV infection")


##########################
# Against RSV hospitalizations
##########################
df.ve <- df %>% 
  filter(encounter_type == "inpatient") %>% mutate(case_control = positive_rsv)

ve.2 <- regress_unmatch(df.ve = df.ve, confounders = confounders_inpatient) %>% 
 mutate(against = "RSV-associated hospitalization")


##########################
# Against RSV ED visit
##########################
# remove those "Specimen"? 
df.ve <- df %>% 
  filter(encounter_type == "outpatient") %>% mutate(case_control = positive_rsv)

ve.3 <- regress_unmatch(df.ve = df.ve, confounders = confounders_ed) %>% 
 mutate(against = "RSV-associated outpatient visit")

##########################
# Against RSV-associated LRTI
##########################
df.ve <- df %>% 
  filter(symp_LRT_distress == 1) %>% mutate(case_control = positive_rsv)
ve.4 <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "RSV-associated LRTI (Oct-May)")
ve.4.alltime <- ve.4

df.ve <- df.ve %>% filter(collection_date <= as.Date("2024-1-31"))
ve.4.OctJan <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "RSV-associated LRTI (Oct-Jan)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2023-12-31"))
ve.4.OctDec <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "RSV-associated LRTI (Oct-Dec)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2023-12-31") & collection_date >= as.Date("2023-11-1"))
ve.4.NovDec <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "RSV-associated LRTI (Nov-Dec)")



##########################
# Against RSV-associated LRTI hospitalization
##########################
df.ve <- df %>% 
  filter(symp_LRT_distress == 1 & encounter_type == "inpatient") %>% 
  mutate(case_control = positive_rsv)
ve.5 <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "RSV-associated LRTI hospitalization (Oct-May)")
ve.5.alltime <- ve.5

df.ve <- df.ve %>% filter(collection_date <= as.Date("2024-1-31"))
ve.5.OctJan <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "RSV-associated LRTI hospitalization (Oct-Jan)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2023-12-31"))
ve.5.OctDec <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "RSV-associated LRTI hospitalization (Oct-Dec)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2023-12-31") & collection_date >= as.Date("2023-11-1"))
ve.5.NovDec <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "RSV-associated LRTI hospitalization (Nov-Dec)")




##########################
# Against RSV-associated severe disease outcomes
##########################
# severe disease outcome includes: ICU admissions or high flow rate oxygen support
df.ve <- df %>% 
  filter(icu_admitted == "yes" | highflow_oxygen == 1) %>% 
  mutate(case_control = positive_rsv)

ve.6 <- regress_unmatch(df.ve = df.ve, confounders = confounders_severe) %>% 
 mutate(against = "RSV-associated severe outcomes")


##########################
# Against all-cause LRTI 
##########################

# all time 
df.ve <- df %>% mutate(case_control = symp_LRT_distress)
ve.7.alltime <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "All-cause LRTI (Oct-May)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2024-1-31"))
ve.7.OctJan <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "All-cause LRTI (Oct-Jan)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2023-12-31"))
ve.7.OctDec <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "All-cause LRTI (Oct-Dec)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2023-12-31") & collection_date >= as.Date("2023-11-1"))
ve.7.NovDec <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "All-cause LRTI (Nov-Dec)")

df.ve <- df %>% mutate(case_control = symp_LRT_distress) %>% 
  filter(collection_date >= as.Date("2024-2-1"))
ve.7.FebMay <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "All-cause LRTI (Feb-May)")



##########################
# Against all-cause LRTI hospitalization
##########################

# case: hospitalized LRTI; control: hospitalized non-LRTI (?)
df.ve <- df %>% mutate(case_control = symp_LRT_distress) %>% 
  filter(encounter_type == "inpatient")
ve.8.alltime <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "All-cause LRTI hospitalization (Oct-May)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2024-1-31"))
ve.8.OctJan <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "All-cause LRTI hospitalization (Oct-Jan)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2023-12-31"))
ve.8.OctDec <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "All-cause LRTI hospitalization (Oct-Dec)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2023-12-31") & collection_date >= as.Date("2023-11-1"))
ve.8.NovDec <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "All-cause LRTI hospitalization (Nov-Dec)")

df.ve <- df %>% mutate(case_control = symp_LRT_distress) %>% 
  filter(encounter_type == "inpatient") %>%
  filter(collection_date >= as.Date("2024-2-1"))
ve.8.FebMay <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "All-cause LRTI hospitalization (Feb-May)")



##########################
# Against ICU admission (revision)
##########################
df.ve.icu <- df %>% 
  filter(icu_admitted == "yes") %>% 
  mutate(case_control = positive_rsv)

ve.icu <- regress_unmatch(df.ve = df.ve.icu, confounders = confounders_infection) %>% 
 mutate(against = "RSV-associated ICU admission")
# sample size too small: only one vaccinated case, ve.adj = 80 (-26.5-99)


## combine the results for the main outcome
ve <- 
  rbind(
  ve.1, ve.2, ve.3, ve.4, ve.5, ve.6
) %>% 
  dplyr::select(against, n_cases_mab, n_cases_nomab, n_controls_mab, n_controls_nomab, ve_unadj, ve_adj) 

ve %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T, defaultPageSize = 20)

## combine all results
ve.all <- 
  rbind(
  ve.1, ve.2, ve.3, 
  ve.4,
  ve.5,
  ve.6,
  ve.7.alltime, ve.7.OctJan, ve.7.OctDec, ve.7.NovDec, ve.7.FebMay,
  ve.8.alltime, ve.8.OctJan, ve.8.OctDec, ve.8.NovDec, ve.8.FebMay
) %>% 
  dplyr::select(against, n_cases_mab, n_cases_nomab, n_controls_mab, n_controls_nomab, ve_unadj, ve_adj) 


# save this for ve_realtime_202425 
# write.csv(ve.all, "../data/clean_data/ve_realtime/ve_2324.csv", row.names = F)
```


#### Figure `r fig.counter`. (2 rows for each outcome)
```{r, fig.width = 12, fig.height= 3.5}
fig.counter <- fig.counter + 1

source("utils_mAb_VE.R")

# select the main outcomes
ve.main <- rbind(ve[1,], ve[3,], ve[2,], ve[6,]) %>%
  mutate(across(starts_with("n_"), ~str_replace(., " \\s*\\([^\\)]+\\)", "")))


plt.ve.main <- ve_forest_2rows(df.plot = ve.main)

plt.ve.main

if(savenewplot){
  ggsave(plot = plt.ve.main, filename = "../figs_tabs/figures/ve.main.pdf", height = 3.5, width = 12)
}
```

<br>


<br>

### Read in the literature data and compare with our current estimates {.tabset}

#### all outcomes (unstratifieds)
```{r}
df.lit <- read_excel("../data/SR/SR.xlsx", sheet = "studies")

# classify the outcomes into several categories
df.lit <- df.lit %>% 
  mutate(outcome_group = case_when(outcome %in% c("RSV bronchiolitis ICU admission",
                                                  "RSV severe diseases",
                                                  "Severe RSV LRTI with oxygen support",
                                                  "RSV ICU admission") ~ "RSV-associated severe outcomes",
                                   outcome %in% c("RSV hospitalization") ~ "RSV-associated hospitalization",
                                   outcome %in% c("RSV LRTI") ~ "RSV-associated LRTI",
                                   outcome %in% c("RSV LRTI hospitalization",
                                                  "RSV bronchiolitis hospitalization") ~ "RSV-associated LRTI hospitalization",
                                   outcome %in% c("RSV ED visit") ~ "RSV-associated outpatient visit",
                                   outcome %in% c("all-cause LRTI hospitalization") ~ "All-cause LRTI hospitalization",
                                   outcome %in% c("all-cause bronchiolitis", 
                                                  "all-cause LRTI") ~ "All-cause LRTI",
                                   TRUE ~ outcome))


# combine the literature estimates and current estimates

# first break down the CI of current studies 
a <- matrix(unlist(strsplit(ve.all$ve_adj, "\\(")), ncol = 2, byrow = T) %>% 
    as.data.frame() %>%
    mutate(V2 = str_replace(V2, "\\)", "")) %>% 
    mutate(n_dash = str_count(V2, "-"))
  
a$ve_adj_lb <- NA
a$ve_adj_ub <- NA
  
a[which(a$n_dash == 1),]$ve_adj_lb <- as.numeric(matrix(unlist(strsplit((a[which(a$n_dash == 1),])$V2, "-")), ncol = 2, byrow = T)[,1])
a[which(a$n_dash == 1),]$ve_adj_ub <- as.numeric(matrix(unlist(strsplit((a[which(a$n_dash == 1),])$V2, "-")), ncol = 2, byrow = T)[,2])
  
if(2 %in% c(a$n_dash)){
    # when there is lb < 0 
    a[which(a$n_dash == 2),]$ve_adj_lb <- - as.numeric(matrix(unlist(strsplit(sub(".", "", (a[which(a$n_dash == 2),])$V2), "-")), ncol = 2, byrow = T)[,1])
    a[which(a$n_dash == 2),]$ve_adj_ub <- + as.numeric(matrix(unlist(strsplit(sub(".", "", (a[which(a$n_dash == 2),])$V2), "-")), ncol = 2, byrow = T)[,2])
}
  
a <- a %>% dplyr::rename(ve_adj_median = V1) %>% dplyr::select(-V2, -n_dash)
  
ve.current <- cbind(ve.all %>% dplyr::select(against, ve_adj), a) %>% 
  mutate(studyID = "Current study", study_type = "observational", country = "US") %>% 
  rename(outcome = against) %>% mutate(outcome_group = outcome) %>%
  rename(VE_mean = ve_adj_median, 
         VE_lb = ve_adj_lb, 
         VE_ub = ve_adj_ub) %>% 
  mutate(outcome_group = str_replace(outcome_group, " \\s*\\([^\\)]+\\)", "")) %>%
  mutate(time_range = "Oct-May") %>%
  mutate(time_range = ifelse(str_detect(outcome, "(Oct-May)"), "Oct-May", time_range),
         time_range = ifelse(str_detect(outcome, "(Oct-Jan)"), "Oct-Jan", time_range),
         time_range = ifelse(str_detect(outcome, "(Oct-Dec)"), "Oct-Dec", time_range),
         time_range = ifelse(str_detect(outcome, "(Nov-Dec)"), "Nov-Dec", time_range),
         time_range = ifelse(str_detect(outcome, "(Feb-May)"), "Feb-May", time_range)
         )
  

# combine with previous literature
df.comb <- df.lit %>% dplyr::select(studyID, study_type, country, time_range,outcome, outcome_group, 
                                    VE_mean, VE_lb, VE_ub) %>%
  mutate(ve_adj = paste0(VE_mean, " (", VE_lb, "-", VE_ub, ")")) %>% 
  rbind(ve.current) %>%
  filter(!is.na(outcome)) 

# only keep the Levy 2024 for 3-12 months age group
df.comb <- df.comb %>% 
  filter(studyID != "Levy 2024" | 
           studyID == "Levy 2024" & VE_mean == 26.5)

```


```{r fig.height = 16, fig.width = 9}
### plot all VE in literature for each outcome
df.infection <- df.comb %>% filter(outcome_group == "Medically attended RSV infection")
df.outpatient <- df.comb %>% filter(outcome_group == "RSV-associated outpatient visit")
df.hosp <- df.comb %>% filter(outcome_group == "RSV-associated hospitalization")
df.severe <- df.comb %>% filter(outcome_group == "RSV-associated severe outcomes")
df.LRTI <- df.comb %>% filter(outcome_group == "RSV-associated LRTI")
df.LRTIhosp <- df.comb %>% filter(outcome_group == "RSV-associated LRTI hospitalization")
df.allcauseLRTI <- df.comb %>% filter(outcome_group == "All-cause LRTI")
df.allcauseLRTIhosp <- df.comb %>% filter(outcome_group == "All-cause LRTI hospitalization")



plt.ve.lit.infection <- plot_ve(df.outcome = df.infection)
plt.ve.lit.outpatient <- plot_ve(df.outcome = df.outpatient)
plt.ve.lit.hosp <- plot_ve(df.outcome = df.hosp)
plt.ve.lit.severe <- plot_ve(df.outcome = df.severe)
plt.ve.lit.LRTI <- plot_ve(df.outcome = df.LRTI)
plt.ve.lit.LRTIhosp <- plot_ve(df.outcome = df.LRTIhosp)
plt.ve.lit.allcauseLRTI <- plot_ve(df.outcome = df.allcauseLRTI)
plt.ve.lit.allcauseLRTIhosp <- plot_ve(df.outcome = df.allcauseLRTIhosp)


# combine all 
plt.ve.lit.all <- 
  plot_grid(plt.ve.lit.infection, 
          plt.ve.lit.outpatient,
          plt.ve.lit.hosp,
          plt.ve.lit.severe,
          plt.ve.lit.LRTI,
          plt.ve.lit.LRTIhosp,
          plt.ve.lit.allcauseLRTI,
          plt.ve.lit.allcauseLRTIhosp,
          ncol = 1, 
          rel_heights = c(3.8,4.2,6,5,3.8,4.5,5.6,5),
          labels = c("A)", "B)", "C)", "D)", "E)", "F)", "G)", "H)")
          )


plt.ve.lit.all

if(savenewplot){
  ggsave(plot = plt.ve.lit.all, filename = "../figs_tabs/figures/ve.lit.all.pdf", height = 16, width = 9)
}


```

#### main outcomes
```{r, fig.height = 9, fig.width=9}
# save the main comparison plot for the paper.
plt.ve.lit <- 
  plot_grid(plt.ve.lit.infection, 
          plt.ve.lit.outpatient,
          plt.ve.lit.hosp,
          plt.ve.lit.severe,
          ncol = 1, 
          rel_heights = c(3.8,4,6,5), 
          labels = c("A)", "B)", "C)", "D)"))


plt.ve.lit

if(savenewplot){
  ggsave(plot = plt.ve.lit, filename = "../figs_tabs/figures/ve.lit.pdf", height = 9, width = 9)
}

```

#### all-cause LRTI (stratified)
```{r fig.width = 10, fig.height=6}
# stratify the outcomes against all-cause lRTI & all-cause LRTI hosp
df.allcauseLRTI <- df.allcauseLRTI %>%
  mutate(time_range_cat = case_when(time_range %in% c("Sep-Jan", "Oct-Jan", "Oct-Dec", "Nov-Dec") ~ "Peak months",
                                    time_range %in% c("19/20 season", "Oct-May", "16/17 season", "2019-2021") ~ "Full season",
                                    time_range %in% c("Feb-May") ~ "Off-peak months"))

df.allcauseLRTIhosp <- df.allcauseLRTIhosp %>%
   mutate(time_range_cat = case_when(time_range %in% c("Sep-Dec", "Oct-Jan", "Oct-Dec", "Nov-Dec") ~ "Peak months",
                                     time_range %in% c("19/20 season", "Oct-May",  "16/17 season", "2019-2021") ~ "Full season",
                                     time_range %in% c("Feb-May") ~ "Off-peak months"))

plt.ve.lit.allcauseLRTI.stratified <- plot_ve_stratified(df.outcome = df.allcauseLRTI)
plt.ve.lit.allcauseLRTIhosp.stratified <- plot_ve_stratified(df.outcome = df.allcauseLRTIhosp)

plt.ve.lit.allcauseLRTI.stratified.extend <- plot_ve_stratified_extend(df.outcome = df.allcauseLRTI)
plt.ve.lit.allcauseLRTIhosp.stratified.extend <- plot_ve_stratified_extend(df.outcome = df.allcauseLRTIhosp)


plt.ve.lit.allcause.stratified <- 
  plot_grid(plt.ve.lit.allcauseLRTI.stratified,
            plt.ve.lit.allcauseLRTIhosp.stratified,
            ncol = 1, 
            rel_heights = c(6,6), 
            labels = c("A) ", "B) "))

plt.ve.lit.allcause.stratified.extend <- 
  plot_grid(plt.ve.lit.allcauseLRTI.stratified.extend,
            plt.ve.lit.allcauseLRTIhosp.stratified.extend,
            ncol = 1, 
            rel_heights = c(6,6), 
            labels = c("A) ", "B) "))

plt.ve.lit.allcause.stratified.extend

confounif(savenewplot){
  ggsave(plot = plt.ve.lit.allcause.stratified.extend, filename = "../figs_tabs/figures/ve.lit.allcause.stratified.extend.pdf", height = 6, width = 10)
}

if(savenewplot){
  ggsave(plot = plt.ve.lit.allcause.stratified.extend, filename = "../figs_tabs/figures/ve.lit.allcause.stratified.extend.adjotherviruses.pdf", height = 6, width = 10)
}

```

#### Main outcomes with stratified all-cause VE
```{r fig.width = 10, fig.height=14}
plt.ve.lit.main.stratified <- 
  plot_grid(plt.ve.lit.infection, 
          plt.ve.lit.outpatient,
          plt.ve.lit.hosp,
          plt.ve.lit.severe,
          plt.ve.lit.allcauseLRTI.stratified,
          plt.ve.lit.allcauseLRTIhosp.stratified,
          ncol = 1, 
          rel_heights = c(3.8,4.2,6,5,6.6,5.5),
          labels = c("A)", "B)", "C)", "D)", "E)", "F)")
          )


plt.ve.lit.main.stratified

if(savenewplot){
  ggsave(plot = plt.ve.lit.main.stratified, filename = "../figs_tabs/figures/ve.lit.main.stratified.pdf", height = 14, width = 10)
}
```


#### all outcomes (all-cause LRTI stratified)
```{r fig.height = 18, fig.width = 9}
# combine the main outcomes and the stratified outcomes
# combine all 
plt.ve.lit.all.stratified <- 
  plot_grid(plt.ve.lit.infection, 
          plt.ve.lit.outpatient,
          plt.ve.lit.hosp,
          plt.ve.lit.severe,
          plt.ve.lit.LRTI,
          plt.ve.lit.LRTIhosp,
          plt.ve.lit.allcauseLRTI.stratified,
          plt.ve.lit.allcauseLRTIhosp.stratified,
          ncol = 1, 
          rel_heights = c(3.8,4.2,6,5,3.8,4.5,6.6,5.5),
          labels = c("A)", "B)", "C)", "D)", "E)", "F)", "G)", "H)")
          )


plt.ve.lit.all.stratified

if(savenewplot){
  ggsave(plot = plt.ve.lit.all.stratified, filename = "../figs_tabs/figures/ve.lit.all.stratified.pdf", height = 16, width = 9)
}
```



<br>

### Earlier records
Look at when restricting to records up to March, if the results are the same as what was reported in the ACIP meeting by CDC.
```{r warning=F,fig.width = 12, fig.height= 3.5}

df.early <- df %>% filter(collection_date <= as.Date("2024-03-31"))
# df.early <- df %>% filter(collection_date <= as.Date("2023-12-31"))
# df.early <- df %>% filter(collection_date <= as.Date("2023-12-31") & collection_date >= as.Date("2023-12-1"))

# all-cause LRTI 
# df.ve <- df.early %>% mutate(case_control = ifelse(is.na(symp_LRT_distress), 0, 1))


tab.counter <- tab.counter + 1
##########################
# Against RSV infection (inpatient + outpatient)
##########################
df.ve <- df.early %>% mutate(case_control = positive_rsv)

ve.1 <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended RSV infection")


##########################
# Against RSV hospitalizations
##########################
df.ve <- df.early %>% 
  filter(encounter_type == "inpatient") %>% mutate(case_control = positive_rsv)

ve.2 <- regress_unmatch(df.ve = df.ve, confounders = confounders_inpatient) %>% 
 mutate(against = "RSV-associated hospitalization")


##########################
# Against RSV ED visit
##########################
# remove those "Specimen"? 
df.ve <- df.early %>% 
  filter(encounter_type == "outpatient") %>% mutate(case_control = positive_rsv)

ve.3 <- regress_unmatch(df.ve = df.ve, confounders = confounders_ed) %>% 
 mutate(against = "RSV-associated outpatient visit")

##########################
# Against RSV-associated LRTI
##########################
df.ve <- df.early %>% 
  filter(symp_LRT_distress == 1) %>% mutate(case_control = positive_rsv)

ve.4 <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "RSV-associated LRTI")


##########################
# Against RSV-associated LRTI hospitalization
##########################
df.ve <- df.early %>% 
  filter(symp_LRT_distress == 1 & encounter_type == "inpatient") %>% 
  mutate(case_control = positive_rsv)

ve.5 <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "RSV-associated LRTI hospitalization")




##########################
# Against RSV-associated severe disease outcomes
##########################
# severe disease outcome includes: ICU admissions or high flow rate oxygen support
df.ve <- df.early %>% 
  filter(icu_admitted == "yes" | highflow_oxygen == 1) %>% 
  mutate(case_control = positive_rsv)

ve.6 <- regress_unmatch(df.ve = df.ve, confounders = confounders_severe) %>% 
 mutate(against = "RSV-associated severe outcomes")


## combine the results 
# combine the tables together 
ve.early <- 
  rbind(
  ve.1, ve.2, ve.3, ve.4, ve.5, ve.6
) %>% 
  dplyr::select(against, n_cases_mab, n_cases_nomab, n_controls_mab, n_controls_nomab, ve_unadj, ve_adj) 


# select the main outcomes
ve.early <- rbind(ve.early[1,], ve.early[3,], ve.early[2,], ve.early[6,]) %>%
  mutate(across(starts_with("n_"), ~str_replace(., " \\s*\\([^\\)]+\\)", "")))


plt.ve.early <- ve_forest_2rows(df.plot = ve.early)

plt.ve.early

if(savenewplot){
  ggsave(plot = plt.ve.early, filename = "../figs_tabs/figures/ve.early.pdf", height = 3.5, width = 12)
}


#### restricting to only ED visit
df.ve <- df.early %>% 
  filter(`Encounter.Type` == "Emergency") %>% mutate(case_control = positive_rsv)

ve.3.ed <- regress_unmatch(df.ve = df.ve, confounders = confounders_ed) %>% 
 mutate(against = "RSV-associated outpatient visit")


```

<br>
<br>

### Look at whether dosage has an influence on VE. {.tabset}

#### Table `r tab.counter` Compare infants who took 100mg and 50mg dosage  
```{r}
tab.counter <- tab.counter + 1

df_table1_dosage <- df_table1 %>%
  mutate(rsv_mab_dose = case_when(rsv_mab == "Yes, 100mg dose" ~ "100mg",
                                  rsv_mab == "Yes, 50mg dose" ~ "50mg")) %>%
  filter(!is.na(rsv_mab_dose))

table1_dosage <- df_table1_dosage %>% 
  dplyr::select(-rsv_mab, -encounter_type, -positive_rsv, -symp_LRT_distress) %>%
  tbl_summary(by = rsv_mab_dose,
              
              type = list(all_continuous() ~ "continuous2"),       # indicate that you want to print multiple statistics 
         statistic = list(all_continuous() ~ c("{mean} ({sd})", 
                                               "{median} ({p25}, {p75})",
                                               "{N_miss} ({p_miss}%)"),                 
                          all_categorical() ~ "{n} ({p}%)"),
         
              digits = list(all_categorical() ~ c(0, 1),
                            all_continuous() ~ 1),
         
              label  = list(  
                Sex ~ "Sex", 
                age_at_test_in_months ~ "Age at testing (months)",
                age_at_test_in_months_cat_2 ~ "Age at testing",
                month_when_tested_cat ~ "Time tested", 
                race_ethnicity ~ "Race and ethnicity",
                risk_factor_pulmonary ~ "Pulmonary diseases", 
                risk_factor_cardiac ~ "Cardiac diseases",
                risk_factor_anemia ~ "Anemia",
                risk_factor_gestagelessthan37wks ~ "Gestational age",
                risk_factor_atleastone ~ "Having at least one risk factor",
                insurance_type ~ "Insurance type",
                birth_weight ~ "Birth weight"
                ),
         
        missing_text = "Missing"
        #,
         #     percent = "row"
        #      missing= "no"
                      ) %>% 
  add_p(pvalue_fun = ~ style_pvalue(., digits = 3)) %>% 
  add_overall(last = F) %>%
  bold_labels() %>%
  modify_table_styling(
    columns = label,
    rows = label == "Other non-Hispanic",
    footnote = footnote_otherraces
  ) %>%
   modify_table_styling(
    columns = label,
    rows = label == "Having at least one risk factor",
    footnote = footnote_atleastoneriskfactor
  )


table1_dosage %>% as_flex_table() %>% 
  flextable::set_table_properties( width = 1, layout = "autofit") 


if(savenewplot){
  table1_dosage %>%
    as_gt() %>%
    gt::gtsave(filename = "../figs_tabs/tables/table1_dosage.docx")
}
  
```

#### Table `r tab.counter` VE by dosage (100mg vs. not vaccinated)
```{r warning=F}
tab.counter <- tab.counter + 1

df.100mg <- df %>% 
  mutate(rsv_mab = case_when(rsv_mab_dose == "100mg" ~ 1,
                             rsv_mab == 0 ~ 0))

##########################
# Against RSV infection (inpatient + outpatient)
##########################
df.ve <- df.100mg %>% mutate(case_control = positive_rsv)

ve.1 <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended RSV infection")


##########################
# Against RSV hospitalizations
##########################
df.ve <- df.100mg %>% 
  filter(encounter_type == "inpatient") %>% mutate(case_control = positive_rsv)

ve.2 <- regress_unmatch(df.ve = df.ve, confounders = confounders_inpatient) %>% 
 mutate(against = "RSV-associated hospitalization")


##########################
# Against RSV ED visit
##########################
# remove those "Specimen"? 
df.ve <- df.100mg %>% 
  filter(encounter_type == "outpatient") %>% mutate(case_control = positive_rsv)

ve.3 <- regress_unmatch(df.ve = df.ve, confounders = confounders_ed) %>% 
 mutate(against = "RSV-associated outpatient visit")

##########################
# Against RSV-associated LRTI
##########################
df.ve <- df.100mg %>% 
  filter(symp_LRT_distress == 1) %>% mutate(case_control = positive_rsv)

ve.4 <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "RSV-associated LRTI")


##########################
# Against RSV-associated LRTI hospitalization
##########################
df.ve <- df.100mg %>% 
  filter(symp_LRT_distress == 1 & encounter_type == "inpatient") %>% 
  mutate(case_control = positive_rsv)

ve.5 <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "RSV-associated LRTI hospitalization")




##########################
# Against RSV-associated severe disease outcomes
##########################
# severe disease outcome includes: ICU admissions or high flow rate oxygen support
df.ve <- df.100mg %>% 
  filter(icu_admitted == "yes" | highflow_oxygen == 1) %>% 
  mutate(case_control = positive_rsv)

ve.6 <- regress_unmatch(df.ve = df.ve, confounders = confounders_severe) %>% 
 mutate(against = "RSV-associated severe outcomes")


## combine the results 
# combine the tables together 
ve.100mg <- 
  rbind(
  ve.1, ve.2, ve.3, ve.4, ve.5, ve.6
) %>% 
  dplyr::select(against, n_cases_mab, n_cases_nomab, n_controls_mab, n_controls_nomab, ve_unadj, ve_adj) 

ve.100mg %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T, defaultPageSize = 20)
```

#### Table `r tab.counter` VE by dosage (50mg vs. not vaccinated)
```{r warning=F}
tab.counter <- tab.counter + 1

df.50mg <- df %>% 
  mutate(rsv_mab = case_when(rsv_mab_dose == "50mg" ~ 1,
                             rsv_mab == 0 ~ 0))


##########################
# Against RSV infection (inpatient + outpatient)
##########################
df.ve <- df.50mg %>% mutate(case_control = positive_rsv)

ve.1 <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended RSV infection")


##########################
# Against RSV hospitalizations
##########################
df.ve <- df.50mg %>% 
  filter(encounter_type == "inpatient") %>% mutate(case_control = positive_rsv)

ve.2 <- regress_unmatch(df.ve = df.ve, confounders = confounders_inpatient) %>% 
 mutate(against = "RSV-associated hospitalization")


##########################
# Against RSV ED visit
##########################
# remove those "Specimen"? 
df.ve <- df.50mg %>% 
  filter(encounter_type == "outpatient") %>% mutate(case_control = positive_rsv)

ve.3 <- regress_unmatch(df.ve = df.ve, confounders = confounders_ed) %>% 
 mutate(against = "RSV-associated outpatient visit")

##########################
# Against RSV-associated LRTI
##########################
df.ve <- df.50mg %>% 
  filter(symp_LRT_distress == 1) %>% mutate(case_control = positive_rsv)

ve.4 <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "RSV-associated LRTI")


##########################
# Against RSV-associated LRTI hospitalization
##########################
df.ve <- df.50mg %>% 
  filter(symp_LRT_distress == 1 & encounter_type == "inpatient") %>% 
  mutate(case_control = positive_rsv)

ve.5 <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "RSV-associated LRTI hospitalization")




##########################
# Against RSV-associated severe disease outcomes
##########################
# severe disease outcome includes: ICU admissions or high flow rate oxygen support
df.ve <- df.50mg %>% 
  filter(icu_admitted == "yes" | highflow_oxygen == 1) %>% 
  mutate(case_control = positive_rsv)

ve.6 <- regress_unmatch(df.ve = df.ve, confounders = confounders_severe) %>% 
 mutate(against = "RSV-associated severe outcomes")


## combine the results 
# combine the tables together 
ve.50mg <- 
  rbind(
  ve.1, ve.2, ve.3, ve.4, ve.5, ve.6
) %>% 
  dplyr::select(against, n_cases_mab, n_cases_nomab, n_controls_mab, n_controls_nomab, ve_unadj, ve_adj) 

ve.50mg %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T, defaultPageSize = 20)
```

#### Table `r tab.counter`. Compare VE from 50mg and 100mg dosage
```{r}
tab.counter <- tab.counter + 1

ve.50mg %>% 
  dplyr::select(against, ve_unadj, ve_adj) %>%
  rename(VE.unadjusted.50mg = ve_unadj, VE.adjusted.50mg = ve_adj) %>%
  left_join(
    ve.100mg %>% 
      dplyr::select(against, ve_unadj, ve_adj) %>%
      rename(VE.unadjusted.100mg = ve_unadj, VE.adjusted.100mg = ve_adj) 
  ) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T,  defaultPageSize = 20,
           columnGroups = list(
    colGroup(name = "100mg", columns = c("VE.unadjusted.100mg", "VE.adjusted.100mg")),
    colGroup(name = "50mg", columns = c("VE.unadjusted.50mg", "VE.adjusted.50mg"))
  ),
  columns = list(
    VE.unadjusted.100mg = colDef(name = "VE.unadjusted"),
    VE.adjusted.100mg= colDef(name = "VE.adjusted"),
    VE.unadjusted.50mg = colDef(name = "VE.unadjusted"),
    VE.adjusted.50mg = colDef(name = "VE.adjusted")
  ))
```

<br>

#### Combine plot of any dose, 100mg, 50mg
```{r fig.width = 12, fig.height = 5.5}
# rearrange data frame for plotting
ve.dose <- 
  cbind(
    ve.100mg %>% 
      dplyr::rename(n_cases_mab_100mg = n_cases_mab, 
                    n_controls_mab_100mg = n_controls_mab,
                    ve_unadj_100mg = ve_unadj,
                    ve_adj_100mg = ve_adj) %>%
      dplyr::select(against, n_cases_mab_100mg, n_cases_nomab, n_controls_mab_100mg, n_controls_nomab, ve_unadj_100mg, ve_adj_100mg),
    ve.50mg %>% 
      dplyr::rename(n_cases_mab_50mg = n_cases_mab, 
                    n_controls_mab_50mg = n_controls_mab,
                    ve_unadj_50mg = ve_unadj,
                    ve_adj_50mg = ve_adj) %>%
      dplyr::select(n_cases_mab_50mg, n_controls_mab_50mg, ve_unadj_50mg, ve_adj_50mg),
    ve %>% 
      dplyr::rename(n_cases_mab_anydose = n_cases_mab, 
                    n_controls_mab_anydose = n_controls_mab,
                    ve_unadj_anydose = ve_unadj,
                    ve_adj_anydose = ve_adj) %>%
      dplyr::select(n_cases_mab_anydose, n_controls_mab_anydose, ve_unadj_anydose, ve_adj_anydose)
  ) %>% 
  mutate(across(starts_with("n_"), ~str_replace(., " \\s*\\([^\\)]+\\)", "")))

ve.dose <- rbind(ve.dose[1,],
                            ve.dose[3,],
                            ve.dose[2,],
                            ve.dose[6,])


source("utils_mAb_VE.R")

plt.ve.bydose <- ve_forest_dose_addanydose(df.plot = ve.dose)

plt.ve.bydose

if(savenewplot){
  ggsave(plot = plt.ve.bydose, filename = "../figs_tabs/figures/ve.bydose.pdf", height = 5.5, width = 12)
}

```


<br>
<br>

### what if we look at the VE against different age groups? 
Per ACIP's meeting slides, it would be good to look at VE among <8 months and 8-12 months.
Should we classify age using age when being tested or age when nirsevimab became available (chose this). 

```{r warning=FALSE}
df <- df %>% mutate(DOB = as.Date(DOB))

# Classifying method 1: classify using DOB (whether younger than 8 months on 2023-10-1) 
df.young <- df %>% filter(DOB > as.Date("2023-2-1")) # 2648
df.old <- df %>% filter(DOB <= as.Date("2023-2-1")) # 499 # this is not possible to do as there is no vaccinated cases among this older age group

# Classifying method 2: classify using age when being tested 
#df.young <- df %>% filter(age_at_test_in_months < 8) # 1885
#df.old <- df %>% filter(age_at_test_in_months >= 8) # 1262

################################################################################
# First, VE against younger kids 
################################################################################


##########################
# Against RSV infection (inpatient + outpatient)
##########################
df.ve <- df.young %>% mutate(case_control = positive_rsv)

ve.1 <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended RSV infection")


##########################
# Against RSV hospitalizations
##########################
df.ve <- df.young %>% 
  filter(encounter_type == "inpatient") %>% mutate(case_control = positive_rsv)

ve.2 <- regress_unmatch(df.ve = df.ve, confounders = confounders_inpatient) %>% 
 mutate(against = "RSV-associated hospitalization")


##########################
# Against RSV ED visit
##########################
# remove those "Specimen"? 
df.ve <- df.young %>% 
  filter(encounter_type == "outpatient") %>% mutate(case_control = positive_rsv)

ve.3 <- regress_unmatch(df.ve = df.ve, confounders = confounders_ed) %>% 
 mutate(against = "RSV-associated outpatient visit")

##########################
# Against RSV-associated LRTI
##########################
df.ve <- df.young %>% 
  filter(symp_LRT_distress == 1) %>% mutate(case_control = positive_rsv)

ve.4 <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTI) %>% 
 mutate(against = "RSV-associated LRTI")


##########################
# Against RSV-associated LRTI hospitalization
##########################
df.ve <- df.young %>% 
  filter(symp_LRT_distress == 1 & encounter_type == "inpatient") %>% 
  mutate(case_control = positive_rsv)

ve.5 <- regress_unmatch(df.ve = df.ve, confounders = confounders_LRTIhosp) %>% 
 mutate(against = "RSV-associated LRTI hospitalization")




##########################
# Against RSV-associated severe disease outcomes
##########################
# severe disease outcome includes: ICU admissions or high flow rate oxygen support
df.ve <- df.young %>% 
  filter(icu_admitted == "yes" | highflow_oxygen == 1) %>% 
  mutate(case_control = positive_rsv)

ve.6 <- regress_unmatch(df.ve = df.ve, confounders = confounders_severe) %>% 
 mutate(against = "RSV-associated severe outcomes")


## combine the results 
# combine the tables together 
ve.young <- 
  rbind(
  ve.1, ve.2, ve.3, ve.4, ve.5, ve.6
) %>% 
  dplyr::select(against, n_cases_mab, n_cases_nomab, n_controls_mab, n_controls_nomab, ve_unadj, ve_adj) 

# ve.young %>%
#   reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
#             defaultExpanded = T, defaultPageSize = 20)


################################################################################
# too few vaccinated cases to calculate VE for older kids
################################################################################
```

#### convert VE under 8m to forest plot
```{r fig.width = 11, fig.height = 5}
ve.young <- ve.young %>% 
  mutate(across(starts_with("n_"), ~str_replace(., " \\s*\\([^\\)]+\\)", "")))

# rearrange the outcomes
ve.young <- rbind(
  ve.young[1, ],
  ve.young[2, ],
  ve.young[2, ],
  ve.young[6, ],
  ve.young[4, ],
  ve.young[5, ]
)



plt.ve.under8m.eligibleage <- ve_forest_2rows(ve.young)

plt.ve.under8m.eligibleage

if(savenewplot){
  ggsave(plot = plt.ve.under8m.eligibleage, filename = "../figs_tabs/figures/ve.under8.eligibleage.pdf", height = 5, width = 11)
}
```

<br>

### Sample size, power or minimum detectable odds ratio for an unmatched or matched case-control study (using epi.sscc() function) {.tabset}
  * Another tool (shinyapp) for sample size calculation: https://apps.p-95.com/app/drivesamplesize
  
#### MA RSV infection
```{r echo=T}
library(epiR)

# for medically attended RSV infection
epi.sscc(N = 3090, # total number of subjects included
         OR = NA,  # expected study odds ratio
         p1 = 0.031,  # the prevalence of exposure amongst the cases.
         p0 = 0.128,  # the prevalence of exposure amongst the controls.
         n = 3090,  # the total number of subjects in the study (i.e., the number of cases plus the number of controls). what is the difference from N??
         power = 0.8, # the required study power. ( Ideally, minimum power of a study required is 80%.)
         r = 3.54,  # number in the control group divided by number in the case group. In our study: 2410/680
         sided.test = 2, # use a one- or two-sided test
         nfractional = FALSE, # whether to return fractional sample size
         conf.level = 0.95, 
         method = "unmatched")
# returning: OR = 0.662: the expected detectable odds ratio given the number of study subjects. 
# VE = 1-OR = 0.338 

```

#### RSV outpatient
```{r echo = T}
# for RSV outpatient
epi.sscc(N = 2505, # total number of subjects included
         OR = NA,  # expected study odds ratio
         p1 = 0.031,  # the prevalence of exposure amongst the cases.
         p0 = 0.116,  # the prevalence of exposure amongst the controls.
         n = 2050,  # the total number of subjects in the study (i.e., the number of cases plus the number of controls). what is the difference from N??
         power = 0.8, # the required study power. ( Ideally, minimum power of a study required is 80%.)
         r = 3.87,  # number in the control group divided by number in the case group. here: 
         sided.test = 2, # use a one- or two-sided test
         nfractional = FALSE, # whether to return fractional sample size
         conf.level = 0.95, 
         method = "unmatched")
# returning: OR = 0.5629488: the expected detectable odds ratio given the number of study subjects. 
# VE = 1-OR = 0.4370512


```

#### RSV inpatient
```{r echo = T}
# for RSV inpatient
epi.sscc(N = 543, # total number of subjects included
         OR = NA,  # expected study odds ratio
         p1 = 0.0301,  # the prevalence of exposure amongst the cases.
         p0 = 0.1856764,  # the prevalence of exposure amongst the controls.
         n = 2050,  # the total number of subjects in the study (i.e., the number of cases plus the number of controls). what is the difference from N??
         power = 0.8, # the required study power. ( Ideally, minimum power of a study required is 80%.)
         r = 2.27,  # number in the control group divided by number in the case group. here: 
         sided.test = 2, # use a one- or two-sided test
         nfractional = FALSE, # whether to return fractional sample size
         conf.level = 0.95, 
         method = "unmatched")
# returning: OR = 0.6856783: the expected detectable odds ratio given the number of study subjects. 
# VE = 1-OR = 0.3143217
```

#### RSV severe outcomess
```{r echo = T}
# for severe outcomes
epi.sscc(N = 435, # total number of subjects included
         OR = NA,  # expected study odds ratio
         p1 = 0.02758621,  # the prevalence of exposure amongst the cases.
         p0 = 0.2689655,  # the prevalence of exposure amongst the controls.
         n = 435,  # the total number of subjects in the study (i.e., the number of cases plus the number of controls). what is the difference from N??
         power = 0.8, # the required study power. ( Ideally, minimum power of a study required is 80%.)
         r = 2,  # number in the control group divided by number in the case group. here: 
         sided.test = 2, # use a one- or two-sided test
         nfractional = FALSE, # whether to return fractional sample size
         conf.level = 0.95, 
         method = "unmatched")
# returning: OR = 0.4767214, the expected detectable odds ratio given the number of study subjects. 
# VE = 1-OR = 0.5232786


```

```{r}
# get the test-positive rate during peak time (Nov-Dec)
df.peak <- df %>% filter(collection_date >= as.Date("2023-11-1") & collection_date <= as.Date("2023-12-31"))
df.peak %>% count(positive_rsv)

df.offpeak <- df %>% filter(collection_date >= as.Date("2024-2-1"))
df.offpeak %>% count(positive_rsv)

```

<br>
<br>

### Analyses After Submission

#### look at VE by gestational age
  * preterm (<37 wks)
  * early term (37-38 wks)
  * full term (39-40 wks)
```{r fig.width = 11, fig.height = 5}
df.early <- df %>% filter(risk_factor_gestage == "early term") 
df.ve <- df.early %>% mutate(case_control = positive_rsv)
ve.early <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended RSV infection")

df.full <- df %>% filter(risk_factor_gestage == "full term") 
df.ve <- df.full %>% mutate(case_control = positive_rsv)
ve.full <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended RSV infection")

df.preterm <- df %>% filter(risk_factor_gestage == "preterm") 
df.ve <- df.preterm %>% mutate(case_control = positive_rsv)
ve.preterm <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended RSV infection")

# preterm kids without other risk factors
df.preterm.heatlhy <- df %>% filter(risk_factor_gestage == "preterm")  %>% 
  dplyr::select(-risk_factor_small_for_gestage, 
                -risk_factor_gestage,
                -risk_factor_gestagelessthan37wks,
                -risk_factor_atleastone) %>%
  filter(risk_factor_anemia == "no",
         risk_factor_immunodeficiency == "no",
         risk_factor_cardiac == "no",
         risk_factor_pulmonary == "no",
         risk_factor_down == "no")
df.ve <- df.preterm.heatlhy %>% mutate(case_control = positive_rsv)
ve.preterm.healthy <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended RSV infection")
  

# early term kids without other risk factors
df.early.heatlhy <- df %>% filter(risk_factor_gestage == "early term")  %>% 
  dplyr::select(-risk_factor_small_for_gestage, 
                -risk_factor_gestage,
                -risk_factor_gestagelessthan37wks,
                -risk_factor_atleastone) %>%
  filter(risk_factor_anemia == "no",
         risk_factor_immunodeficiency == "no",
         risk_factor_cardiac == "no",
         risk_factor_pulmonary == "no",
         risk_factor_down == "no")
df.ve <- df.early.heatlhy %>% mutate(case_control = positive_rsv)
ve.early.healthy <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended RSV infection")
  

# full term kids without other risk factors
df.full.heatlhy <- df %>% filter(risk_factor_gestage == "full term")  %>% 
  dplyr::select(-risk_factor_small_for_gestage, 
                -risk_factor_gestage,
                -risk_factor_gestagelessthan37wks,
                -risk_factor_atleastone) %>%
  filter(risk_factor_anemia == "no",
         risk_factor_immunodeficiency == "no",
         risk_factor_cardiac == "no",
         risk_factor_pulmonary == "no",
         risk_factor_down == "no")
df.ve <- df.full.heatlhy %>% mutate(case_control = positive_rsv)
ve.full.healthy <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended RSV infection")
  


ve.gest <- 
  rbind(
  ve.preterm %>% mutate(against = "Preterm (<37wks, all)"),
  ve.preterm.healthy %>% mutate(against = "Preterm (<37wks, healthy)"),
  ve.early %>% mutate(against = "Early term (37-38wks, all)"),
  ve.early.healthy %>% mutate(against = "Early term (37-38wks, healthy)"),
  ve.full %>% mutate(against = "Full term (39-40wks, all)"),
  ve.full.healthy %>% mutate(against = "Full term (39-40wks, healthy)")
) %>% 
  dplyr::select(against, n_cases_mab, n_cases_nomab, n_controls_mab, n_controls_nomab, ve_unadj, ve_adj) 


ve.gest <- ve.gest %>% 
  mutate(across(starts_with("n_"), ~str_replace(., " \\s*\\([^\\)]+\\)", "")))


plt.ve.gestage <- ve_forest_2rows(ve.gest, ssa = TRUE)

plt.ve.gestage

if(savenewplot){
  ggsave(plot = plt.ve.gestage, filename = "../figs_tabs/figures/ve.gestage.pdf", height = 5, width = 11)
}
```

<br>
<br>


### VE against other respiratory viruses
```{r fig.width = 11, fig.height = 4}
# against medically attended influenza infection 
df.ve <- df %>% mutate(case_control = positive_flu)
ve.flu <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended flu infection")


# against medically attended hmpv infection 
df.ve <- df %>% mutate(case_control = positive_hmpv)
ve.hmpv <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended hmpv infection")

# against medically attended rhinovirus infection
df.ve <- df %>% mutate(case_control = positive_rhino)
ve.rhino <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended rhinovirus infection")


# against medically attended adeno infection
df.ve <- df %>% mutate(case_control = positive_adeno)
ve.adeno <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection) %>% 
 mutate(against = "Medically attended adenovirus infection")

ve.otherviruses <- 
  rbind(
  ve.flu,
  ve.hmpv,
  ve.rhino,
  ve.adeno
) %>% 
  dplyr::select(against, n_cases_mab, n_cases_nomab, n_controls_mab, n_controls_nomab, ve_unadj, ve_adj) 


ve.otherviruses <- ve.otherviruses %>% 
  mutate(across(starts_with("n_"), ~str_replace(., " \\s*\\([^\\)]+\\)", "")))


plt.ve.otherviruses <- ve_forest_2rows(ve.otherviruses, ssa = T)

plt.ve.otherviruses

if(savenewplot){
  ggsave(plot = plt.ve.otherviruses, filename = "../figs_tabs/figures/ve.otherviruses.pdf", height = 4, width = 11)
}

```


<br>

## Revision (2024.12)

### How VE differs by subgroup. {.tabset}

#### Selecting confounders using backward selection
```{r}


all_confounders_race <- c(
  "age_at_test_in_months_cat_2",
  "month_when_tested_cat",
  "risk_factor_atleastone",  
  "insurance_type"
)


# test which confounders to include using backwards selection


######## race_ethnicity ###########

# -------------------- hispanic --------------------
temp <-  df %>% filter(race_ethnicity == "Hispanic") 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_race), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_hispanic <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
)

aic.infection.hispanic <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (Hispanic)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(race_ethnicity == "Hispanic") %>% mutate(case_control = positive_rsv)
ve.infection.hispanic <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_hispanic) %>% 
 mutate(against = "Medically attended RSV infection (Hispanic)")

# ------------------- White non-Hispanic -------------------- (why for this group the confidence interval is very wide)
temp <-  df %>% filter(race_ethnicity == "White non-Hispanic") 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_race), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab +  age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_white <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat",
  "risk_factor_atleastone"
  #"insurance_type"
)

aic.infection.white <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (White non-Hispanic)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(race_ethnicity == "White non-Hispanic") %>% mutate(case_control = positive_rsv)
ve.infection.white <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_white) %>% 
 mutate(against = "Medically attended RSV infection (White non-Hispanic)")

# ------------------- Black non-Hispanic -------------------- 
temp <-  df %>% filter(race_ethnicity == "Black non-Hispanic") 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_race), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_black <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
  #"risk_factor_atleastone"
  #"insurance_type"
)

aic.infection.black <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (Black non-Hispanic)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(race_ethnicity == "Black non-Hispanic") %>% mutate(case_control = positive_rsv)
ve.infection.black <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_black) %>% 
 mutate(against = "Medically attended RSV infection (Black non-Hispanic)")

# ------------------- Other non-Hispanic -------------------- 
temp <-  df %>% filter(race_ethnicity == "Other non-Hispanic") 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_race), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_other <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat",
  "risk_factor_atleastone",
  "insurance_type"
)

aic.infection.other <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (Other non-Hispanic)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(race_ethnicity == "Other non-Hispanic") %>% mutate(case_control = positive_rsv)
ve.infection.other <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_other) %>% 
 mutate(against = "Medically attended RSV infection (Other non-Hispanic)")

# ------------------- Unknown -------------------- 
temp <-  df %>% filter(race_ethnicity == "unknown") 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_race), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_unknown <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
  # "risk_factor_atleastone",
  # "insurance_type"
)

aic.infection.unknown <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (unknown)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(race_ethnicity == "unknown") %>% mutate(case_control = positive_rsv)
ve.infection.unknown <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_unknown) %>% 
 mutate(against = "Medically attended RSV infection (unknown)")


###### Insurance type ######

all_confounders_insurance <- c(
  "age_at_test_in_months_cat_2",
  "month_when_tested_cat",
  "risk_factor_atleastone",  
  "race_ethnicity"
)

# ------------------- private insurance -------------------- 
temp <-  df %>% filter(insurance_type == "private") 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_insurance), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_private <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
  # "risk_factor_atleastone",
  # "insurance_type"
)

aic.infection.private <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (Private)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(insurance_type == "private") %>% mutate(case_control = positive_rsv)
ve.infection.private <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_private) %>% 
 mutate(against = "Medically attended RSV infection (Private)")



# ------------------- public insurance -------------------- 
temp <-  df %>% filter(insurance_type == "public") 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_insurance), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_public <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
  # "risk_factor_atleastone",
  # "insurance_type"
)

aic.infection.public <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (Public)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(insurance_type == "public") %>% mutate(case_control = positive_rsv)
ve.infection.public <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_public) %>% 
 mutate(against = "Medically attended RSV infection (Public)")



######## Birth weight ##############

all_confounders_bw<- c(
  "age_at_test_in_months_cat_2",
  "month_when_tested_cat",
  #"risk_factor_atleastone",  
  "race_ethnicity",
  "insurance_type"
)

# ------------------- gestational age < 2500 g -------------------- 
temp <-  df %>% filter(risk_factor_small_for_gestage == 1) 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_bw), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_lowbw <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
  # "risk_factor_atleastone",
  # "insurance_type"
)

aic.infection.lowbw <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (Birth weight < 2500g)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(risk_factor_small_for_gestage == 1 ) %>% mutate(case_control = positive_rsv)
ve.infection.lowbw <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_lowbw) %>% 
 mutate(against = "Medically attended RSV infection (Birth weight < 2500g)")


# ------------------- gestational age >= 2500 g -------------------- 
temp <-  df %>% filter(risk_factor_small_for_gestage == 0) 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_bw), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_highbw <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
  # "risk_factor_atleastone",
  # "insurance_type"
)

aic.infection.highbw <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (Birth weight ≥ 2500g)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(risk_factor_small_for_gestage == 0 ) %>% mutate(case_control = positive_rsv)
ve.infection.highbw <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_highbw) %>% 
 mutate(against = "Medically attended RSV infection (Birth weight ≥ 2500g)")


####### age at test #########

all_confounders_age <- c(
  "age_at_test_in_months_cat_2",
  "month_when_tested_cat",
  "risk_factor_atleastone",  
  "race_ethnicity",
  "insurance_type"
)

# ------------------- age when tested < 8 months -------------------- 
temp <-  df %>% filter(age_at_test_in_months < 8) 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_age), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_under8m <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
  # "risk_factor_atleastone",
  # "insurance_type"
)

aic.infection.under8m <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (under 8 months)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(age_at_test_in_months < 8 ) %>% mutate(case_control = positive_rsv)
ve.infection.under8m <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_under8m) %>% 
 mutate(against = "Medically attended RSV infection (under 8 months)")

# ------------------- age when tested >= 8 months -------------------- 
temp <-  df %>% filter(age_at_test_in_months >= 8) 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_age), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_above8m <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
  # "risk_factor_atleastone",
  # "insurance_type"
)

aic.infection.above8m <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (8 months and above)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(age_at_test_in_months >= 8 ) %>% mutate(case_control = positive_rsv)
ve.infection.above8m <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_above8m) %>% 
 mutate(against = "Medically attended RSV infection (8 months and above)")


######## prematurity ##########

all_confounders_gestage <- c(
  "age_at_test_in_months_cat_2",
  "month_when_tested_cat",
  #"risk_factor_atleastone",  
  "race_ethnicity",
  "insurance_type"
)

# ------------------- preterm -------------------- 
temp <-  df %>% filter(risk_factor_gestage== "preterm") 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_gestage), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_preterm <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
  # "risk_factor_atleastone",
  # "insurance_type"
)

aic.infection.preterm <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (<37 weeks)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(risk_factor_gestage == "preterm" ) %>% mutate(case_control = positive_rsv)
ve.infection.preterm <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_preterm) %>% 
 mutate(against = "Medically attended RSV infection (<37 weeks)")


# ------------------- early term -------------------- 
temp <-  df %>% filter(risk_factor_gestage== "early term") 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_gestage), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_earlyterm <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat",
  # "risk_factor_atleastone",
  "insurance_type"
)

aic.infection.earlyterm <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (37-38 weeks)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(risk_factor_gestage == "early term" ) %>% mutate(case_control = positive_rsv)
ve.infection.earlyterm <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_earlyterm) %>% 
 mutate(against = "Medically attended RSV infection (37-38 weeks)")


# ------------------- full term or longer -------------------- 
temp <-  df %>% filter(risk_factor_gestage %in% c("full term", "late term", "post term") ) 
formula <- as.formula(paste(c("positive_rsv ~ rsv_mab", all_confounders_gestage), collapse = " + ")) 
full.model <- glm(formula, data = temp, family = "binomial")
step.model <- stepAIC(full.model, 
                      scope = list(lower = ~ rsv_mab + age_at_test_in_months_cat_2 + month_when_tested_cat ,
                                   upper = formula),
                      direction = "backward", trace = FALSE)
confounders_infection_fullterm <- c(
  "age_at_test_in_months_cat_2", # 3-month interval
  "month_when_tested_cat"
  # "risk_factor_atleastone",
  #"insurance_type"
)

aic.infection.fullterm <- as.data.frame(step.model$anova) %>% dplyr::select(Step, AIC) %>% 
  mutate(endpoint = "Medically attended RSV infection (≥39 weeks)") %>% 
  mutate(Step = ifelse(Step == "", str_replace(as.character(formula[3]), "rsv_mab \\+ ", ""), Step)) %>% 
  rename(Confounders = Step)

df.ve <- df %>% filter(risk_factor_gestage == "full term" ) %>% mutate(case_control = positive_rsv)
ve.infection.fullterm <- regress_unmatch(df.ve = df.ve, confounders = confounders_infection_fullterm) %>% 
 mutate(against = "Medically attended RSV infection (≥39 weeks)")


# stack all results together 
ve.subgroup.backselect <- 
  ve.infection.hispanic %>%
  rbind(
    ve.infection.white, ve.infection.black, ve.infection.other, ve.infection.unknown,
    ve.infection.private, ve.infection.public,
    ve.infection.lowbw, ve.infection.highbw,
    ve.infection.under8m, ve.infection.above8m,
    ve.infection.preterm, ve.infection.earlyterm, ve.infection.fullterm
  ) %>% 
  mutate(subgroup = case_when(str_detect(against, "Hispanic|White|Black|Other|unknown") ~ "Race/ethnicity",
                              str_detect(against, "Private|Public") ~ "Insurance",
                              str_detect(against, "Birth weight") ~ "Birth weight",
                              str_detect(against,"8 months") ~ "Age at test",
                              str_detect(against, "weeks") ~ "Gestational age")) %>%
  mutate(subgroup_cat =  str_extract(against, "\\(([^)]*)\\)")) %>%
  mutate(subgroup_cat = gsub("[()]", "", subgroup_cat)) %>% 
  mutate(across(starts_with("n_"), ~str_replace(., " \\s*\\([^\\)]+\\)", ""))) %>% 
  mutate(
    ve_adj_median = as.numeric(str_extract(ve_adj, "^[0-9.-]+")),
    ve_adj_lower = as.numeric(str_extract(ve_adj, "(?<=\\()[-\\d\\.]+(?=-)")),
    ve_adj_upper = as.numeric(str_extract(ve_adj, "(?<=-)[\\d\\.]+(?=\\))"))
  )


```

<br>

### (revision) Main VE using pre-specified confounders
```{r, fig.width = 12, fig.height = 3.5}
confounders_prespecified <- c(
  "age_at_test_in_months_cat_2",
  "month_when_tested_cat",
  "race_ethnicity",
  "risk_factor_atleastone",     
  "insurance_type"
)

##########################
# Against RSV infection (inpatient + outpatient)
##########################
df.ve <- df %>% mutate(case_control = positive_rsv)

ve.1 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "Medically attended RSV infection")


##########################
# Against RSV hospitalizations
##########################
df.ve <- df %>% 
  filter(encounter_type == "inpatient") %>% mutate(case_control = positive_rsv)

ve.2 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated hospitalization")


##########################
# Against RSV ED visit
##########################
# remove those "Specimen"? 
df.ve <- df %>% 
  filter(encounter_type == "outpatient") %>% mutate(case_control = positive_rsv)

ve.3 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated outpatient visit")

##########################
# Against RSV-associated LRTI
##########################
df.ve <- df %>% 
  filter(symp_LRT_distress == 1) %>% mutate(case_control = positive_rsv)
ve.4 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated LRTI")



##########################
# Against RSV-associated LRTI hospitalization
##########################
df.ve <- df %>% 
  filter(symp_LRT_distress == 1 & encounter_type == "inpatient") %>% 
  mutate(case_control = positive_rsv)
ve.5 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated LRTI hospitalization")



##########################
# Against RSV-associated severe disease outcomes
##########################
# severe disease outcome includes: ICU admissions or high flow rate oxygen support
df.ve <- df %>% 
  filter(icu_admitted == "yes" | highflow_oxygen == 1) %>% 
  mutate(case_control = positive_rsv)

ve.6 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated severe outcomes")


## combine the results for the main outcome
ve.prespecified <- 
  rbind(
  ve.1, ve.2, ve.3, ve.4, ve.5, ve.6
) %>% 
  dplyr::select(against, n_cases_mab, n_cases_nomab, n_controls_mab, n_controls_nomab, ve_unadj, ve_adj) 

ve.prespecified %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T, defaultPageSize = 20)


source("utils_mAb_VE.R")

# select the main outcomes
ve.main.prespecified <- rbind(ve.prespecified[1,], ve.prespecified[3,], ve.prespecified[2,], ve.prespecified[6,]) %>%
  mutate(across(starts_with("n_"), ~str_replace(., " \\s*\\([^\\)]+\\)", "")))


plt.ve.main.prespecified <- ve_forest_2rows(df.plot = ve.main.prespecified)

plt.ve.main.prespecified

if(savenewplot){
  ggsave(plot = plt.ve.main.prespecified, filename = "../figs_tabs/figures/ve.main.prespecified.pdf", height = 3.5, width = 12)
}
```

<br>

### (revision) Main VE using penalized regression
```{r}
library(glmnet)

# run through different outcomes 

# infection
df.ve <- df %>% mutate(case_control = positive_rsv)
ve.infection.penalized <- regress_penalized(df.ve = df.ve, confounder = confounders_prespecified, against = "Medically attended RSV infection")

# hospitalization
df.ve <- df %>% filter(encounter_type == "inpatient") %>% mutate(case_control = positive_rsv)
ve.hosp.penalized <- regress_penalized(df.ve = df.ve, confounder = confounders_prespecified, against = "RSV-associated hospitalization")


# outpatient
df.ve <- df %>% filter(encounter_type == "outpatient") %>% mutate(case_control = positive_rsv)
ve.ed.penalized <- regress_penalized(df.ve = df.ve, confounder = confounders_prespecified, against = "RSV-associated outpatient visit")

# severe outcomes
df.ve <- df %>% filter(icu_admitted == "yes" | highflow_oxygen == 1) %>% mutate(case_control = positive_rsv)
ve.severe.penalized <- regress_penalized(df.ve = df.ve, confounder = confounders_prespecified, against = "RSV-associated severe outcomes")

ve.penalized <- rbind(
  ve.infection.penalized, 
  ve.ed.penalized,
  ve.hosp.penalized,
  ve.severe.penalized
)

ve.penalized

```


<br>

### (revision) Comment: The study does not explore interactions between key variables (e.g., age and dose, or risk factors and immunization status), which could provide insights into differential effectiveness across subgroups.

#### Conduct subgroup analysis

```{r, fig.width= 9, fig.height = 6}
library(glmnet)
##################################
# Having at least one risk factor 
##################################
confounders <- all_confounders[! all_confounders %in% c("risk_factor_atleastone")]
ve.highrisk <- run_subgroup_outcomes(df.subgroup = df %>% filter(risk_factor_atleastone == "yes")) %>% mutate(strata = "Yes")
ve.lowrisk <- run_subgroup_outcomes(df.subgroup = df %>% filter(risk_factor_atleastone == "no")) %>% mutate(strata = "No")

ve.highrisk.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(risk_factor_atleastone == "yes")) %>% mutate(strata = "Yes")
ve.lowrisk.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(risk_factor_atleastone == "no")) %>% mutate(strata = "No")

ve.risk <- rbind(ve.highrisk, ve.lowrisk) %>% mutate(subgroup = "Having at least one risk factor")
ve.risk.penalized <- rbind(ve.highrisk.penalized, ve.lowrisk.penalized) %>% mutate(subgroup = "Having at least one risk factor")

##################################
# age when being tested
##################################
confounders <- c(all_confounders[! all_confounders %in% c("age_at_test_in_months_cat_2")], "age_at_test_in_months")
ve.under6m <- run_subgroup_outcomes(df.subgroup = df %>% filter(age_at_test_in_months < 6)) %>% mutate(strata = "Under 6 months")
ve.above6m <- run_subgroup_outcomes(df.subgroup = df %>% filter(age_at_test_in_months >= 6)) %>% mutate(strata = "6 months and above")

ve.under6m.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(age_at_test_in_months < 6)) %>% mutate(strata = "Under 6 months")
ve.above6m.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(age_at_test_in_months >= 6)) %>% mutate(strata = "6 months and above")

ve.age <- rbind(ve.under6m, ve.above6m) %>% mutate(subgroup = "Age when being tested")
ve.age.penalized <- rbind(ve.under6m.penalized, ve.above6m.penalized) %>% mutate(subgroup = "Age when being tested")


##################################
# ethnicity
##################################
confounders <- all_confounders[! all_confounders %in% c("race_ethnicity")]
ve.hispanic <- run_subgroup_outcomes(df.subgroup = df %>% filter(ethnicity == "Hispanic or Latino")) %>% mutate(strata = "Hispanic or Latino")
ve.nothispanic <- run_subgroup_outcomes(df.subgroup = df %>% filter(ethnicity == "Not Hispanic or Latino")) %>% mutate(strata = "Not Hispanic or Latino")

ve.hispanic.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(ethnicity == "Hispanic or Latino")) %>% mutate(strata = "Hispanic or Latino")
ve.nothispanic.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(ethnicity == "Not Hispanic or Latino")) %>% mutate(strata = "Not Hispanic or Latino")

ve.ethnicity <- rbind(ve.hispanic, ve.nothispanic) %>% mutate(subgroup = "Ethnicity")
ve.ethnicity.penalized <- rbind(ve.hispanic.penalized, ve.nothispanic.penalized) %>% mutate(subgroup = "Ethnicity")


##################################
# race 
##################################
confounders <- all_confounders[! all_confounders %in% c("race_ethnicity")]
ve.white <- run_subgroup_outcomes(df.subgroup = df %>% filter(race == "White")) %>% mutate(strata = "White")
ve.black <- run_subgroup_outcomes(df.subgroup = df %>% filter(race == "Black")) %>% mutate(strata = "Black")

ve.white.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(race == "White")) %>% mutate(strata = "White")
ve.black.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(race == "Black")) %>% mutate(strata = "Black")

ve.race <- rbind(ve.white, ve.black) %>% mutate(subgroup = "Race")
ve.race.penalized <- rbind(ve.white.penalized, ve.black.penalized) %>% mutate(subgroup = "Race")


##################################
# month tested
##################################
confounders <- all_confounders[! all_confounders %in% c("month_when_tested_cat")]
ve.OctNov <- run_subgroup_outcomes(df.subgroup = df %>% filter(month_when_tested_cat == "Oct-Nov")) %>% mutate(strata = "Oct-Nov")
ve.DecJan <- run_subgroup_outcomes(df.subgroup = df %>% filter(month_when_tested_cat == "Dec-Jan")) %>% mutate(strata = "Dec-Jan")
ve.FebMay <- run_subgroup_outcomes(df.subgroup = df %>% filter(month_when_tested_cat == "Feb-Mar" | month_when_tested_cat == "April and after")) %>% mutate(strata = "Feb-May")

ve.peak <- run_subgroup_outcomes(df.subgroup = df %>% filter(month_when_tested %in% c("Dec", "Jan"))) %>% mutate(strata = "Peak (Dec.-Jan.)")
ve.offpeak <- run_subgroup_outcomes(df.subgroup = df %>% filter(!month_when_tested %in% c("Dec", "Jan"))) %>% mutate(strata = "Off-peak (other months)")

ve.peak.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(month_when_tested %in% c("Dec", "Jan"))) %>% mutate(strata = "Peak (Dec.-Jan.)")
ve.offpeak.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(!month_when_tested %in% c("Dec", "Jan"))) %>% mutate(strata = "Off-peak (other months)")

ve.monthtested <- rbind(ve.peak, ve.offpeak) %>% mutate(subgroup = "Month tested")
ve.monthtested.penalized <- rbind(ve.peak.penalized, ve.offpeak.penalized) %>% mutate(subgroup = "Month tested")


##################################
# insurance type
##################################
confounders <- all_confounders[! all_confounders %in% c("insurance_type")]
ve.private <- run_subgroup_outcomes(df.subgroup = df %>% filter(insurance_type == "private")) %>% mutate(strata = "Private")
ve.public <- run_subgroup_outcomes(df.subgroup = df %>% filter(insurance_type != "private")) %>% mutate(strata = "Public or uninsured")

ve.private.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(insurance_type == "private")) %>% mutate(strata = "Private")
ve.public.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(insurance_type != "private")) %>% mutate(strata = "Public or uninsured")

ve.insurance <- rbind(ve.private, ve.public) %>% mutate(subgroup = "Insurance type")
ve.insurance.penalized <- rbind(ve.private.penalized, ve.public.penalized) %>% mutate(subgroup = "Insurance type")


##################################
# Gestational age
##################################
confounders <- all_confounders[! all_confounders %in% c("risk_factor_atleastone")]
ve.preterm <- run_subgroup_outcomes(df.subgroup = df %>% filter(risk_factor_gestage == "preterm")) %>% mutate(strata = "Less than 37 weeks")
ve.notpreterm <- run_subgroup_outcomes(df.subgroup = df %>% filter(risk_factor_gestage != "preterm")) %>% mutate(strata = "37 weeks and more")

ve.preterm.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(risk_factor_gestage == "preterm")) %>% mutate(strata = "Less than 37 weeks")
ve.notpreterm.penalied <- run_subgroup_outcomes_penalized(df.subgroup = df %>% filter(risk_factor_gestage != "preterm")) %>% mutate(strata = "37 weeks and more")

ve.gestage <- rbind(ve.preterm, ve.notpreterm) %>% mutate(subgroup = "Gestational age")
ve.gestage.penalized <- rbind(ve.preterm.penalized, ve.notpreterm.penalied) %>% mutate(subgroup = "Gestational age")


#------------------------------------
### stacking all the results together 
#------------------------------------

ve.subgroup <- rbind(
  ve.risk, 
  ve.age,
  ve.ethnicity,
  ve.race,
  ve.monthtested,
  ve.insurance,
  ve.gestage
) %>% mutate(ve_unadj = ifelse(n_cases_mab == 0, "NA", ve_unadj),
             ve_adj = ifelse(n_cases_mab == 0, "NA", ve_adj)) 

ve.subgroup.infection <- ve.subgroup %>% filter(against == "infection") %>% dplyr::select(-against)

# # get overall 
# ve.overall <- run_subgroup_outcomes(df.subgroup = df) %>% mutate(strata = "Overall") %>% filter(against == "infection") %>% mutate(subgroup = "Overall")
confounders <- all_confounders
ve.overall.penalized <- run_subgroup_outcomes_penalized(df.subgroup = df) %>% filter(against == "infection") 

  
ve.subgroup.infection <- rbind(
  ve.subgroup.infection
) %>% mutate(immunized = paste0(n_cases_mab, "/", n_cases_mab + n_controls_mab),
             unimmunized = paste0(n_cases_nomab, "/", n_cases_nomab + n_controls_nomab)) %>% 
  dplyr::select(-starts_with("n"))



### penalized
ve.subgroup.penalized <- rbind(
  ve.risk.penalized, 
  ve.age.penalized,
  ve.ethnicity.penalized,
  ve.race.penalized,
  ve.monthtested.penalized,
  ve.insurance.penalized,
  ve.gestage.penalized
) 

ve.subgroup.infection.penalized <- ve.subgroup.penalized %>% filter(against == "infection") %>% dplyr::select(-against)

# # get overall 
# ve.overall <- run_subgroup_outcomes(df.subgroup = df) %>% mutate(strata = "Overall") %>% filter(against == "infection") %>% mutate(subgroup = "Overall")

ve.subgroup.infection.penalized <- rbind(
  ve.subgroup.infection.penalized
) %>% mutate(immunized = paste0(n_cases_mab, "/", n_cases_mab + n_controls_mab),
             unimmunized = paste0(n_cases_nomab, "/", n_cases_nomab + n_controls_nomab)) %>% 
  dplyr::select(-starts_with("n"))


plt.ve.subgroup <- ve_forest_subgroup(df.ve = ve.subgroup.infection.penalized)

plt.ve.subgroup

if(savenewplot){
  ggsave(plot = plt.ve.subgroup, filename = "../figs_tabs/figures/ve.subgroup.pdf", height = 6, width = 9)
}

```

```{r}
# what if we include interaction term 
```


<br>

### Lower coverage issue (comment of reviewer 3) 
```{r}
# coverage for those entering 

# coverage among those <8 m when being tested 
df %>% filter(age_at_test_in_months < 8) %>% count(rsv_mab)
287/(287 +1575) # 15.4%

# coverage among those >=8 m when being tested 
df %>% filter(age_at_test_in_months >= 8) %>% count(rsv_mab)
43/(43 + 1185) # 3.5%


## age when immunized 
hist(df$age_at_mab_in_days) 
df %>% filter(rsv_mab == 1) %>% filter(age_at_mab_in_days <= 60) %>% count(rsv_mab_dose)
df %>% filter(rsv_mab == 1) %>% filter(age_at_mab_in_days > 60) %>% count(rsv_mab)

df %>% filter(rsv_mab_dose == "100mg") 
hist(as.Date((df %>% filter(rsv_mab_dose == "100mg"))$mab_date), breaks = "week")
hist(as.Date((df %>% filter(rsv_mab_dose == "50mg"))$mab_date), breaks = "week")
  

df %>% filter(rsv_mab == 1) %>% nrow()



212/330

# ve among under 8m low risk individuals 
temp <- df %>% filter(age_at_test_in_months < 8 & risk_factor_atleastone == "no") %>% mutate(case_control = positive_rsv)
regress_unmatch(df.ve = temp, confounders = all_confounders[! all_confounders %in% c("risk_factor_atleastone")])

```

<br>

### Test difference by dosage
```{r}
# using 50mg as reference group 

test_diff_by_dosage <- function(df.ve, confounders){
  
  df.ve <- df.ve %>% mutate(rsv_mab_dose = factor(rsv_mab_dose, levels = c("50mg", "100mg", "no mAb")))
  
  formula <- as.formula(paste(c("case_control ~ rsv_mab_dose", confounders), collapse = " + ")) 
  model <- glm(formula, data = df.ve, family = binomial)
  p_diff <- summary(model)$coefficients["rsv_mab_dose100mg", "Pr(>|z|)"] # comparing 100mg to 50mg
  
  return(p_diff)
  
}

# infection 
df.ve <- df %>% mutate(case_control = positive_rsv)
p_diff_infection <- test_diff_by_dosage(df.ve = df.ve, confounders = confounders_prespecified)

# ed 
df.ve <- df %>% filter(encounter_type == "outpatient") %>% mutate(case_control = positive_rsv)
p_diff_ed <- test_diff_by_dosage(df.ve = df.ve, confounders = confounders_prespecified)

# ed 
df.ve <- df %>% filter(encounter_type == "inpatient") %>% mutate(case_control = positive_rsv)
p_diff_hosp <- test_diff_by_dosage(df.ve = df.ve, confounders = confounders_prespecified)

# severe outcomes
df.ve <- df %>% filter(icu_admitted == "yes" | highflow_oxygen == 1) %>% mutate(case_control = positive_rsv)
p_diff_severe <- test_diff_by_dosage(df.ve = df.ve, confounders = confounders_prespecified)

p_diff <- 
  data.frame(
    outcome = c("Medically attended RSV infection", "RSV-associated outpatient visit", "RSV-associated hospitalization", "RSV-associated severe outcomes"),
    p_value = c(p_diff_infection, p_diff_ed, p_diff_hosp, p_diff_severe)
  )

```

<br>


### Effectiveness estimates for broader outcomes (e.g., all-cause LRTI) are presented but not adjusted for competing risks or varying pathogen prevalence, which may bias these results.
```{r}


```

<br>

### (revision) adjusting for multiple tests of one individual 

```{r, fig.height =3.5, fig.width = 12}
# using Generalized estimating equations (GEE)
# which accounts for the dependence that occurs with multiple observations per person
library(geepack)

####### Main effect ##################

# infection 
df.ve <- df %>% mutate(case_control = positive_rsv)
ve.infection <- regress_geeglm(df.ve = df.ve, confounders = confounders_prespecified, against = "Medically attended RSV infecion")


# outpatient (ed visit)
df.ve <- df %>% filter(encounter_type == "outpatient") %>% mutate(case_control = positive_rsv)
ve.ed <- regress_geeglm(df.ve = df.ve, confounders = confounders_prespecified, against = "RSV-associated outpatient visit")

# outpatient (ed visit)
df.ve <- df %>% filter(encounter_type == "inpatient") %>% mutate(case_control = positive_rsv)
ve.hosp <- regress_geeglm(df.ve = df.ve, confounders = confounders_prespecified, against = "RSV-associated hospitalization")

# severe outcome 
df.ve <- df %>% filter(icu_admitted == "yes" | highflow_oxygen == 1) %>% mutate(case_control = positive_rsv)
ve.severe <- regress_geeglm(df.ve = df.ve, confounders = confounders_prespecified, against = "RSV-associated severe outcomes")

ve.main.geeglm <- rbind(
  ve.infection, ve.ed, ve.hosp, ve.severe
)

ve.main.geeglm

plt.ve.main.geeglm <- ve_forest_2rows(df.plot = ve.main.geeglm)

plt.ve.main.geeglm

if(savenewplot){
  ggsave(plot = plt.ve.main.geeglm, filename = "../figs_tabs/figures/ve.main.geeglm.pdf", height = 3.5, width = 12)
}

```

### (revision) how effectiveness of nirsevimab changes over time (using INLA model, pooled)
```{r fig.width = 8, fig.height = 5}
# there were no vaccinated case before 12.1
df.inla <- df %>% filter(collection_date >= as.Date("2023-11-16") & collection_date <= as.Date("2024-5-9")) 
# recode weekN
df.inla <- df.inla %>% 
  # cut into weeks 
  mutate(time_point_week = cut(collection_date, breaks = "week", start.on.monday = TRUE)) %>%
  mutate(time_point_week = as.Date(time_point_week)) 

df.inla <- df.inla %>%
  mutate(weekN = ceiling(as.numeric(difftime(time_point_week, min(df.inla$time_point_week), units = "weeks"))))

# df.inla %>% dplyr::select(collection_date, time_point_week, weekN) %>% arrange(collection_date)

form.INLA.RW2 <- as.formula(
  case_control ~ 1 + 
    # random effect
    f(weekN, rsv_mab, model = "rw2", hyper = list(prec = list(prior = "pc.prec", param = c(1, 0.01))), constr = T) + 
     # fixed effect
    rsv_mab +
    age_at_test_in_months_cat_2
)

## prepare data for inla model 
df.inla.infection <- df.inla %>% mutate(case_control = positive_rsv) 

## run inla to get results for each outcome 
result.infection <- inla(form.INLA.RW2, family = "binomial", data = df.inla.infection, control.compute = list(dic = TRUE, waic = TRUE, config = TRUE))

# get posterior samples 
# the samples are at the very end of "latent" element, 
# e.g. see by: tail(post1.infection[[1]]$latent[,1], n= 100)
n.iter <- 5000
post.infection <- inla.posterior.sample(n.iter, result.infection)


# index the week 
get_actual_tp <- function(df.inla){
  week_index <- df.inla %>% dplyr::select(time_point_week, weekN) %>% distinct() %>% 
    arrange(weekN) %>% rename(actual_weekN = weekN) %>% 
    cbind(inla_weekN = 1:length(unique(df.inla$weekN)))
  actual_tp <- week_index$time_point_week
  return(actual_tp)
}


tp_infection <- get_actual_tp(df.inla.infection)

process_inla_post <- function(post, # posterior output
                         tp # time points
                         ){

  for(i in 1:n.iter){
    temp <- post[[i]]$latent[grepl("^(week|rsv_mab)", rownames(post[[i]]$latent)), ] %>%
      as.data.frame()
    temp$parm <- rownames(temp)
    temp <- temp %>% pivot_wider(names_from = "parm", values_from = ".") %>% as.data.frame()
    
    if(i == 1){df.post <- temp}
    if(i != 1){df.post <- rbind(df.post, temp)}
  }
  
  # calculate VE for each time point
  df.post <- df.post %>% mutate(across(starts_with("weekN:"), ~ . + `rsv_mab:1`))
  
  df.ve <- t(apply(df.post %>% dplyr::select(starts_with("weekN:")), 2, 
        function(x) quantile(x, probs = c(0.025, 0.5, 0.975)))) %>%
    as.data.frame() %>% 
    mutate(time_point_week = tp) %>%
    mutate(VE = 100 * (1-exp(`50%`)),
           VE_upper = 100 * (1-exp(`2.5%`)),
           VE_lower = 100 * (1-exp(`97.5%`))) %>%
    dplyr::select(time_point_week, VE, VE_lower, VE_upper)

  return(df.ve)
}

df.ve.inla <- rbind(
  process_inla_post(post.infection, tp = tp_infection) %>% mutate(outcome = "RSV infection")
) %>% mutate(time_point_week = as.Date(time_point_week))


# plot infection over time
plt.inla.infection <- 
  df.ve.inla %>% 
  filter(outcome == "RSV infection") %>%
  mutate(outcome = factor(outcome, levels = c("RSV infection", "RSV outpatient", "RSV hosp",
                                              "RSV LRTI", "RSV LRTI hosp", "RSV severe outcomes"))) %>%
  ggplot() +
  geom_point(aes(x = time_point_week, y = VE), size = 0.5) +
  geom_line(aes(x = time_point_week, y = VE)) +
  geom_ribbon(aes(x = time_point_week, ymin = VE_upper, ymax = VE_lower), alpha = 0.2) +
  coord_cartesian(ylim = c(0, 100)) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_x_date(breaks = "2 weeks", date_labels = "%y-%m-%d") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1.2, size = 10),
        axis.title = element_text(size = 15),
        axis.text.y = element_text(size = 12)) +
  # ggtitle("Against medically attended RSV infection (23/24 season)") +
  #geom_text(aes(x = time_point_week, y = VE - 5, label = round(VE)), size = 3) +
  ylab("Effectiveness of nirsevimab against \nmedically attended RSV infection (%)") + xlab("Date")



if(savenewplot){
  ggsave(plot = plt.inla.infection, filename = "../figs_tabs/figures/inla.infection.pdf", height = 5, width = 8)
}

# breakthrough case 
df.breakthrough <- (df %>% filter(positive_rsv == 1 & rsv_mab == 1))
hist(df.breakthrough$collection_date, breaks = "day", freq = T)


plt.breakthrough <- 
  df.breakthrough %>% 
  ggplot() +
  geom_histogram(aes(x = as.Date(collection_date)), fill = "orange", color = "white") +
  scale_x_date(limits = c(min(df.ve.inla$time_point_week), max(df.ve.inla$time_point_week)), breaks = "2 weeks", date_labels = "%y-%m-%d") +
      theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1.2, size = 10),
        axis.title = element_text(size = 15),
        axis.text.y = element_text(size = 12))  +
  ylab("Number of breakthrough infections") +
  xlab("Date")

plot_grid(plt.inla.infection, plt.breakthrough, nrow = 2, labels = "AUTO")

# combine the two into one plot 
    
```


```{r, fig.height = 5, fig.width = 8}
# combine the above two plot together with two y axis 

# Calculate the scaling factor for secondary axis
scale_factor <- max(df.ve.inla$VE, na.rm = TRUE) / 4

# Combined plot
plt.inla.pooled <- 
  ggplot() +
  # First layer: VE line and ribbon
  geom_line(data = df.ve.inla %>% filter(outcome == "RSV infection"),
            aes(x = time_point_week, y = VE)) +
  geom_point(data = df.ve.inla %>% filter(outcome == "RSV infection"),
             aes(x = time_point_week, y = VE), size = 0.5) +
  geom_ribbon(data = df.ve.inla %>% filter(outcome == "RSV infection"),
              aes(x = time_point_week, ymin = VE_upper, ymax = VE_lower), 
              alpha = 0.2) +
  # Second layer: Breakthrough cases
  geom_histogram(data = df.breakthrough,
                 aes(x = as.Date(collection_date), y = after_stat(count) * scale_factor),
                 fill = "orange", alpha = 0.5, bins = 30) +
  # Scales and theme
  scale_y_continuous(
    name = "Effectiveness of nirsevimab against \nmedically attended RSV infection (%)",
    sec.axis = sec_axis(~./scale_factor, 
                       name = "Number of breakthrough infections")
  ) +
  scale_x_date(breaks = "2 weeks", 
               date_labels = "%y-%m-%d",
               limits = c(min(df.ve.inla$time_point_week), 
                         max(df.ve.inla$time_point_week))) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10),
    axis.title = element_text(size = 15),
    axis.text.y = element_text(size = 12),
    axis.title.y.right = element_text(color = "black"),
    axis.text.y.right = element_text(color = "black")
  ) +
  xlab("Date of sample collection") +
  coord_cartesian(ylim = c(5, 100)) 

plt.inla.pooled

if(savenewplot){
  ggsave(plot = plt.inla.pooled, filename = "../figs_tabs/figures/inla.pooled.pdf", height = 5, width = 8)
}

# cases by risk factor (whether there are more high risk individuals at the peak / beginning of the season?, seems not)
# df %>% 
#   filter(positive_rsv == 1) %>%
#   ggplot() +
#   geom_histogram(aes(x = as.Date(collection_date), fill = risk_factor_atleastone), position = )


# df %>% 
#   filter(positive_rsv == 1) %>%
#   ggplot() +
#   geom_histogram(aes(x = as.Date(collection_date), 
#                      fill = risk_factor_atleastone),
#                  position = "fill") +
#   scale_y_continuous(labels = scales::percent) +
#   theme_minimal()
```


### (revision) how effectiveness of nirsevimab changes over time (using INLA model, stratified by time since vax)
```{r}

df.inla <- df %>% filter(collection_date >= as.Date("2023-11-16") & collection_date <= as.Date("2024-5-9")) 

df.inla <- df.inla %>%
  # cut into weeks 
  mutate(time_point_week = cut(collection_date, breaks = "week", start.on.monday = TRUE)) %>%
  mutate(time_point_week = as.Date(time_point_week))

# create some dummy variables to indicate the time since vaccination 
df.inla <- df.inla %>%
  mutate(weeks_btw_mab_collection_cat_2 =
           case_when(weeks_btw_mab_collection_cat %in% c("(0, 2)", "[2, 4)") ~ "(0, 4)",
                     weeks_btw_mab_collection_cat %in% c("[4, 6)", "[6, 8)") ~ "[4, 8)",
                     weeks_btw_mab_collection_cat %in% c("[8, 10)", "[10, 12)") ~ "[8, 12)",
                     weeks_btw_mab_collection_cat %in% c("[12, 14)", "[14, 16)", "[16, )") ~ "[12, )",
                     weeks_btw_mab_collection_cat == "no mAb" ~ "no mAb"
                     )) %>% 
  mutate(weeks_btw_mab_collection_cat_2 = factor(weeks_btw_mab_collection_cat_2,
                                                 levels = c("no mAb", "(0, 4)", "[4, 8)", "[8, 12)", "[12, )")))


# create dummy variables using weeks_btw_mab_collection_cat
dummies <- fastDummies::dummy_cols(df.inla %>% dplyr::select(weeks_btw_mab_collection_cat_2))
dummies <- dummies[, -c(1,2)]
colnames(dummies) <- paste0("weeks_since_vax_4wks", seq(1:ncol(dummies)))
df.inla <- cbind(df.inla, dummies)

df.inla <- df.inla %>% 
  # used in the unstratified analysis
  mutate(weekN = ceiling(as.numeric(difftime(time_point_week, min(df.inla$time_point_week), units = "weeks")))) %>%
  mutate(weekN_global = weekN) %>% # intercept
  # used in the stratified analysis by time since vax 
  mutate(weekN1 = weekN,
         weekN2 = weekN,
         weekN3 = weekN,
         weekN4 = weekN)

form2  <- as.formula(
  case_control ~ 1 +
    # global intercept
    # f(weekN_global, model = "ar1", hyper = list(prec = list(prior = "loggamma", param = c(3, 2))), constr = T) +
    # random effect (fluctuation with week)
    f(weekN1, weeks_since_vax_4wks1, model = "rw2", hyper = list(prec = list(prior = "pc.prec", param = c(1, 0.01))), constr = T) + 
    f(weekN2, weeks_since_vax_4wks2, model = "rw2", hyper = list(prec = list(prior = "pc.prec", param = c(1, 0.01))), constr = T) + 
    f(weekN3, weeks_since_vax_4wks3, model = "rw2", hyper = list(prec = list(prior = "pc.prec", param = c(1, 0.01))), constr = T) + 
    f(weekN4, weeks_since_vax_4wks4, model = "rw2", hyper = list(prec = list(prior = "pc.prec", param = c(1, 0.01))), constr = T) + 
    # fixed effect
    weeks_since_vax_4wks1 +
    weeks_since_vax_4wks2 +
    weeks_since_vax_4wks3 +
    weeks_since_vax_4wks4 +
    # confounders
    age_at_test_in_months_cat_2 +
    # month_when_tested_cat + # don't need this anymore as it has been included above
    risk_factor_atleastone
    )


## prepare data for inla model 
df.inla.infection <- df.inla %>% mutate(case_control = positive_rsv) 

## run inla to get results for each outcome 
result2.infection <- inla(form2, family = "binomial", data = df.inla.infection, 
                         control.compute = list(dic = TRUE, waic = TRUE, config = TRUE))


# get posterior samples
n.iter <- 5000
post2.infection <- inla.posterior.sample(n.iter, result2.infection)

# index the week 
get_actual_tp <- function(df.inla){
  week_index <- df.inla %>% dplyr::select(time_point_week, weekN) %>% distinct() %>% 
    arrange(weekN) %>% rename(actual_weekN = weekN) %>% 
    cbind(inla_weekN = 1:length(unique(df.inla$weekN)))
  actual_tp <- week_index$time_point_week
  return(actual_tp)
}


tp_infection <- get_actual_tp(df.inla.infection)


```

```{r}

get_ve <- function(df.temp){
    temp <- t(apply(df.temp, 2, 
        function(x) quantile(x, probs = c(0.025, 0.5, 0.975)))) %>%
    as.data.frame() %>% 
    mutate(VE = 100 * (1-exp(`50%`)),
           VE_upper = 100 * (1-exp(`2.5%`)),
           VE_lower = 100 * (1-exp(`97.5%`))) %>%
    dplyr::select(VE, VE_lower, VE_upper) 
    return(temp)
}


# function to process post samples
process_post2 <- function(post, # posterior output
                          tp # time points
                         ){

  for(i in 1:n.iter){
    temp <- post[[i]]$latent[grepl("^(weekN|weeks_since_vax_4wks)", rownames(post[[i]]$latent)), ] %>%
      as.data.frame()
    temp$parm <- rownames(temp)
    temp <- temp %>% pivot_wider(names_from = "parm", values_from = ".") %>% as.data.frame()
    
    if(i == 1){df.post <- temp}
    if(i != 1){df.post <- rbind(df.post, temp)}
  }
  
  # process by weeks_since_vax cat
  for(i in 1:4){
    temp <- df.post %>%
      dplyr::select(starts_with(paste0("weekN", i)), starts_with(paste0("weeks_since_vax_4wks", i, ":1")))
    
    colname <- paste0("weeks_since_vax_4wks", i, ":1")
    weeks_since_vax <- c("(0, 4)", "[4, 8)", "[8, 12)", "[12, )")
    
    df.temp <- temp %>% 
      mutate(across(starts_with("weekN"), ~ . + get(colname))) %>%
      dplyr::select(starts_with("weekN")) %>% get_ve() %>% 
      mutate(weeks_since_vax = weeks_since_vax[i]) %>% 
      cbind(data.frame(time_point_week = tp))
    
    if(i == 1){df.ve <- df.temp}
    if(i != 1){df.ve <- rbind(df.ve, df.temp)}
  
  }
  
  return(df.ve)
}
```

```{r fig.height = 7, fig.width = 8}
df.ve2 <- rbind(
  process_post2(post2.infection, tp = tp_infection) %>% mutate(outcome = "RSV infection")) %>% mutate(time_point_week = as.Date(time_point_week))


# plot 
df.ve2 %>% 
  mutate(outcome = factor(outcome, levels = c("RSV infection", "RSV outpatient", "RSV hosp",
                                              "RSV LRTI", "RSV LRTI hosp", "RSV severe outcomes"))) %>%
  filter(outcome %in% c("RSV LRTI", "RSV LRTI hosp") == F) %>%
  mutate(weeks_since_vax = factor(weeks_since_vax, levels = c("(0, 4)", "[4, 8)", "[8, 12)", "[12, )"))) %>%
  ggplot() +
  geom_point(aes(x = time_point_week, y = VE), size = 0.5) +
  geom_line(aes(x = time_point_week, y = VE), linewidth = 0.5) +
  geom_ribbon(aes(x = time_point_week, ymin = VE_upper, ymax = VE_lower), alpha = 0.2) +
  coord_cartesian(ylim = c(0, 100)) +
  facet_grid(outcome ~ weeks_since_vax) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_x_date(breaks = "month") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  ggtitle("From INLA model (by time since vax cat)") +
  geom_vline(xintercept = as.Date("2024-5-9"), color = "steelblue", linetype = "dashed") +
  geom_vline(xintercept = as.Date("2024-9-30"), color = "steelblue", linetype = "dashed") 
  

df.breakthrough.stratified <- df.inla %>% filter(positive_rsv == 1 & rsv_mab==1)

# function plot one panel of weeks_since_vax 
plot_one_panel <- function(weeks){
  plt <- ggplot() +
  # First layer: VE line and ribbon
  geom_line(data = df.ve2 %>% filter(weeks_since_vax == weeks),
            aes(x = time_point_week, y = VE)) +
  geom_point(data = df.ve2 %>% filter(weeks_since_vax == weeks),
             aes(x = time_point_week, y = VE), size = 0.5) +
  geom_ribbon(data = df.ve2 %>% filter(weeks_since_vax == weeks),
              aes(x = time_point_week, ymin = VE_upper, ymax = VE_lower), 
              alpha = 0.2) +
  # Second layer: Breakthrough cases
  geom_histogram(data = df.breakthrough.stratified %>% filter(weeks_btw_mab_collection_cat_2 == weeks),
                 aes(x = as.Date(collection_date), y = after_stat(count) * scale_factor),
                 fill = "orange", alpha = 0.5, bins = 30) +
  # Scales and theme
  scale_y_continuous(
    name = "",
    sec.axis = sec_axis(~./scale_factor,
                       #name = ""
                       )
  ) +
  scale_x_date(breaks = "1 month", 
               date_labels = "%y-%m-%d",
               limits = c(min(df.ve.inla$time_point_week), 
                         max(df.ve.inla$time_point_week))) +
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  facet_grid(. ~ c(weeks_since_vax)) +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 10),
    axis.title = element_text(size = 15),
    axis.text.y = element_text(size = 12),
    axis.title.y.right = element_text(color = "black"),
    axis.text.y.right = element_text(color = "black"),
    strip.text = element_text(size = 13),
    #panel.spacing = unit(10, "lines")  # Reduce space between panels
  plot.margin = unit(c(0, 0.4, 0, 0.1), "cm") # Remove outer margins
  ) +
  xlab("") +
  coord_cartesian(ylim = c(5, 100)) 
  
  return(plt)
}


# sample size
df.inla %>% filter(positive_rsv == 1 & rsv_mab==1) %>% count(weeks_btw_mab_collection_cat_2)


combined_plot <- plot_grid(
  plot_one_panel(weeks = "(0, 4)"),
  plot_one_panel(weeks = "[4, 8)"),
  plot_one_panel(weeks = "[8, 12)"),
  plot_one_panel(weeks = "[12, )"),
  nrow = 2, ncol = 2,
  align = "hv",
  axis = "tblr",
  spacing = -0.1  # Reduce space between panels
)


plt.inla.stratified <- combined_plot +
  # Add more bottom margin for x-axis label
  theme(plot.margin = margin(t = 10, r = 30, b = 25, l = 25, unit = "pt")) +
  # Add common axis labels
  draw_label("Date of sample collection", 
            x = 0.5, y = 0.02,
            size = 15, hjust = 0.5) +
  draw_label("Effectiveness of nirsevimab against\nmedically attended RSV infection (%)", 
            x = 0, y = 0.5,
            angle = 90, size = 15, vjust = 0.5) +
  draw_label("Number of breakthrough infections",
            x = 1, y = 0.5,
            angle = 270, size = 15, vjust = 0.5)

plt.inla.stratified 

if(savenewplot){
  ggsave(plot = plt.inla.stratified, filename = "../figs_tabs/figures/inla.stratified.pdf", height = 7, width = 8)
}

```

```{r, fig.width=8, fig.height=12}
# combine time since vax plots 
plt.inla.pooled.stratified <- plot_grid(
  plt.inla.pooled, plt.inla.stratified, labels = "AUTO", nrow = 2, rel_heights = c(4,5)
)

if(savenewplot){
  ggsave(plot = plt.inla.pooled.stratified, filename = "../figs_tabs/figures/inla.pooled.stratified.pdf", height = 12, width = 8)
}
``` 

### (revision) Effectiveness estimates for broader outcomes (e.g., all-cause LRTI) are presented but not adjusted for competing risks or varying pathogen prevalence, which may bias these results.
```{r}
# how many were positive for other viruses (regardless of RSV result)
df %>% count(positive_otherviruses) # 208/3090 = 6.7%

temp <- df %>% filter(positive_otherviruses == 1)

hist(as.Date(temp$collection_date), breaks = "month")

# what if we adjust for positive_otherviruses 

##########################
# Against all-cause LRTI 
##########################
# assume those NA for positive_otherviruses = 0
df.compete<- df %>% mutate(positive_otherviruses = ifelse(is.na(positive_otherviruses), 0, positive_otherviruses))

confounders_compete <- c(confounders_LRTI, "positive_otherviruses")


# all time 
df.ve <- df.compete %>% mutate(case_control = symp_LRT_distress)
ve.7.alltime <- regress_unmatch(df.ve = df.ve, confounders = confounders_compete) %>% 
 mutate(against = "All-cause LRTI (Oct-May)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2024-1-31"))
ve.7.OctJan <- regress_unmatch(df.ve = df.ve, confounders = confounders_compete) %>% 
 mutate(against = "All-cause LRTI (Oct-Jan)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2023-12-31"))
ve.7.OctDec <- regress_unmatch(df.ve = df.ve, confounders = confounders_compete) %>% 
 mutate(against = "All-cause LRTI (Oct-Dec)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2023-12-31") & collection_date >= as.Date("2023-11-1"))
ve.7.NovDec <- regress_unmatch(df.ve = df.ve, confounders = confounders_compete) %>% 
 mutate(against = "All-cause LRTI (Nov-Dec)")

df.ve <- df.compete %>% mutate(case_control = symp_LRT_distress) %>%  filter(collection_date >= as.Date("2024-2-1"))
ve.7.FebMay <- regress_unmatch(df.ve = df.ve, confounders = confounders_compete) %>% 
 mutate(against = "All-cause LRTI (Feb-May)")



##########################
# Against all-cause LRTI hospitalization
##########################

# case: hospitalized LRTI; control: hospitalized non-LRTI (?)
df.ve <- df.compete %>% mutate(case_control = symp_LRT_distress) %>% 
  filter(encounter_type == "inpatient")
ve.8.alltime <- regress_unmatch(df.ve = df.ve, confounders = confounders_compete) %>% 
 mutate(against = "All-cause LRTI hospitalization (Oct-May)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2024-1-31"))
ve.8.OctJan <- regress_unmatch(df.ve = df.ve, confounders = confounders_compete) %>% 
 mutate(against = "All-cause LRTI hospitalization (Oct-Jan)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2023-12-31"))
ve.8.OctDec <- regress_unmatch(df.ve = df.ve, confounders = confounders_compete) %>% 
 mutate(against = "All-cause LRTI hospitalization (Oct-Dec)")

df.ve <- df.ve %>% filter(collection_date <= as.Date("2023-12-31") & collection_date >= as.Date("2023-11-1"))
ve.8.NovDec <- regress_unmatch(df.ve = df.ve, confounders = confounders_compete) %>% 
 mutate(against = "All-cause LRTI hospitalization (Nov-Dec)")

df.ve <- df.compete %>% mutate(case_control = symp_LRT_distress) %>% 
  filter(encounter_type == "inpatient") %>%
  filter(collection_date >= as.Date("2024-2-1"))
ve.8.FebMay <- regress_unmatch(df.ve = df.ve, confounders = confounders_compete) %>% 
 mutate(against = "All-cause LRTI hospitalization (Feb-May)")


```


<br>

### (revision) addressing issue of missingness {.tabset}
Carlos' comment:  I initially said that we can do a sensitivity analysis were we drop the patients with missing birthweight. But maybe a better solution would be to do a sensitivity analysis were we impute this variable, or maybe  assign all missing birthweight as all premature and see if this changes the VE, I assume that it won't. 

#### Drop those that miss birthweight or gestational age
```{r fig.width = 11, fig.height = 4}
df.drop.missing <- df %>% filter(!is.na(risk_factor_gestage))

##########################
# Against RSV infection (inpatient + outpatient)
##########################
df.ve <- df.drop.missing %>% mutate(case_control = positive_rsv)

ve.1 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "Medically attended RSV infection")


##########################
# Against RSV hospitalizations
##########################
df.ve <- df.drop.missing %>% 
  filter(encounter_type == "inpatient") %>% mutate(case_control = positive_rsv)

ve.2 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated hospitalization")


##########################
# Against RSV ED visit
##########################
# remove those "Specimen"? 
df.ve <- df.drop.missing %>% filter(encounter_type == "outpatient") %>% mutate(case_control = positive_rsv)

ve.3 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated outpatient visit")

##########################
# Against RSV-associated LRTI
##########################
df.ve <- df.drop.missing %>% 
  filter(symp_LRT_distress == 1) %>% mutate(case_control = positive_rsv)
ve.4 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated LRTI (Oct-May)")


##########################
# Against RSV-associated LRTI hospitalization
##########################
df.ve <- df.drop.missing %>% 
  filter(symp_LRT_distress == 1 & encounter_type == "inpatient") %>% 
  mutate(case_control = positive_rsv)
ve.5 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated LRTI hospitalization (Oct-May)")



##########################
# Against RSV-associated severe disease outcomes
##########################
# severe disease outcome includes: ICU admissions or high flow rate oxygen support
df.ve <- df.drop.missing %>% 
  filter(icu_admitted == "yes" | highflow_oxygen == 1) %>% 
  mutate(case_control = positive_rsv)

ve.6 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated severe outcomes")



## combine the results for the main outcome
ve.drop.missing <- 
  rbind(
  ve.1, ve.2, ve.3, ve.4, ve.5, ve.6
) %>% 
  dplyr::select(against, n_cases_mab, n_cases_nomab, n_controls_mab, n_controls_nomab, ve_unadj, ve_adj) 

ve.drop.missing %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T, defaultPageSize = 20)



# select the main outcomes
ve.main.drop.missing<- rbind(ve.drop.missing[1,], ve.drop.missing[3,], ve.drop.missing[2,], ve.drop.missing[6,]) %>%
  mutate(across(starts_with("n_"), ~str_replace(., " \\s*\\([^\\)]+\\)", "")))


plt.ve.main.drop.missing <- ve_forest_2rows(df.plot = ve.main.drop.missing)

plt.ve.main.drop.missing

if(savenewplot){
  ggsave(plot = plt.ve.main.drop.missing, filename = "../figs_tabs/figures/ve.main.drop.missing.pdf", height = 3.5, width = 12)
}

# the difference from main result is less than 2% 


```

<br>

#### Impute the variable: assign all missing birthweight as all premature and see if this changes the VE, I assume that it won't.  (then this assumes all individuals missing for birth weight or gestational age are assumed to be "premature", thus they all had at least one risk factor)
```{r, fig.width = 11, fig.height = 4}

# assume all missing are premature (then these are assume to have at least one risk factor)
df.impute <- df %>% mutate(risk_factor_atleastone = ifelse(is.na(risk_factor_gestage), "yes", risk_factor_atleastone))


##########################
# Against RSV infection (inpatient + outpatient)
##########################
df.ve <- df.impute %>% mutate(case_control = positive_rsv)

ve.1 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "Medically attended RSV infection")


##########################
# Against RSV hospitalizations
##########################
df.ve <- df.impute %>% 
  filter(encounter_type == "inpatient") %>% mutate(case_control = positive_rsv)

ve.2 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated hospitalization")


##########################
# Against RSV ED visit
##########################
# remove those "Specimen"? 
df.ve <- df.impute %>% filter(encounter_type == "outpatient") %>% mutate(case_control = positive_rsv)

ve.3 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated outpatient visit")

##########################
# Against RSV-associated LRTI
##########################
df.ve <- df.impute %>% 
  filter(symp_LRT_distress == 1) %>% mutate(case_control = positive_rsv)
ve.4 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated LRTI (Oct-May)")


##########################
# Against RSV-associated LRTI hospitalization
##########################
df.ve <- df.impute %>% 
  filter(symp_LRT_distress == 1 & encounter_type == "inpatient") %>% 
  mutate(case_control = positive_rsv)
ve.5 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated LRTI hospitalization (Oct-May)")



##########################
# Against RSV-associated severe disease outcomes
##########################
# severe disease outcome includes: ICU admissions or high flow rate oxygen support
df.ve <- df.impute %>% 
  filter(icu_admitted == "yes" | highflow_oxygen == 1) %>% 
  mutate(case_control = positive_rsv)

ve.6 <- regress_unmatch(df.ve = df.ve, confounders = confounders_prespecified) %>% 
 mutate(against = "RSV-associated severe outcomes")



## combine the results for the main outcome
ve.impute <- 
  rbind(
  ve.1, ve.2, ve.3, ve.4, ve.5, ve.6
) %>% 
  dplyr::select(against, n_cases_mab, n_cases_nomab, n_controls_mab, n_controls_nomab, ve_unadj, ve_adj) 

ve.impute %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T, defaultPageSize = 20)



# select the main outcomes
ve.main.impute <- rbind(ve.impute[1,], ve.impute[3,], ve.impute[2,], ve.impute[6,]) %>%
  mutate(across(starts_with("n_"), ~str_replace(., " \\s*\\([^\\)]+\\)", "")))


plt.ve.main.impute <- ve_forest_2rows(df.plot = ve.main.impute)

plt.ve.main.impute

if(savenewplot){
  ggsave(plot = plt.ve.main.impute, filename = "../figs_tabs/figures/ve.main.impute.pdf", height = 3.5, width = 12)
}

```





















