---
title: "Waning VE of Nirsevimab"
output: 
  html_document:
    toc: true
    toc_float: true
---

#### Date: `r Sys.Date()`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

library(dplyr)
library(tidyr)
library(tidyverse)
library(readxl)
library(writexl)
library(reactable)
library(ggplot2)
library(stringr)
library(flextable)
library(lubridate)
library(rjags)


library(gtsummary) # for table 1
library(multcomp)
library(survival) # for matched case-control

fig.counter <- 1
tab.counter <- 1

source("utils_mAb_VE.R")
source("jags_waning.R")

rerun <- FALSE
savenewplot <- TRUE
```


```{r}
# read in dataset
df <- read.csv("../data/clean_data/df.mab.csv") %>% 
  mutate(collection_date = as.Date(collection_date))
colnames <- as.data.frame(colnames(df))

# add some variables 
df <- process_df(df)


df <- df %>% 
  # recode confounders
  mutate(cf_birth_weight = birth_weight) %>% # about 25% missing 
  mutate(cf_age = case_when(age_at_test_in_months_cat_2 == "under 3m" ~ 1,
                            age_at_test_in_months_cat_2 == "3-6m" ~ 2,
                            age_at_test_in_months_cat_2 == "6-9m" ~ 3,
                            age_at_test_in_months_cat_2 == "9-12m" ~ 4,
                            age_at_test_in_months_cat_2 == "above 1 yo" ~ 5)) %>%
  mutate(cf_month_tested = case_when(month_when_tested_cat == "Oct-Nov" ~ 1,
                                     month_when_tested_cat == "Dec-Jan" ~ 2,
                                     month_when_tested_cat == "Feb-Mar" ~ 3,
                                     month_when_tested_cat == "April and after" ~ 4
                                     )) %>%
  # convert confounders to dummy variables 
  mutate(cf_age_1 = ifelse(cf_age == 1, 1, 0),
         cf_age_2 = ifelse(cf_age == 2, 1, 0),
         cf_age_3 = ifelse(cf_age == 3, 1, 0),
         cf_age_4 = ifelse(cf_age == 4, 1, 0), 
         cf_age_5 = ifelse(cf_age == 5, 1, 0)) %>%
  mutate(cf_month_tested_1 = ifelse(cf_month_tested == 1, 1, 0),
         cf_month_tested_2 = ifelse(cf_month_tested == 2, 1, 0),
         cf_month_tested_3 = ifelse(cf_month_tested == 3, 1, 0),
         cf_month_tested_4 = ifelse(cf_month_tested == 4, 1, 0))
```

<br>

### VE over time by **1-month** interval {.tabset}

  * classify time since vax to testing into three groups: 0-1, 1-2, 2-3, 3-4 and >4 months
  * included confounders: age tested, month tested.
  * uninformative prior for precision of the non-negative increment d's.
    + d ~ dnorm(0, tau)T(0,)
    + tau_d ~ dgamma(0.01, 0.01)
    
#### Table
```{r}
source("jags_waning.R")

df <- df %>%
  # vax time groups 
  mutate(vax_time_group1 = ifelse(days_btw_mab_collection_cat_3 == "0-1 months", 1, 0)) %>%
  mutate(vax_time_group2 = ifelse(days_btw_mab_collection_cat_3 == "1-2 months", 1, 0)) %>%
  mutate(vax_time_group3 = ifelse(days_btw_mab_collection_cat_3 == "2-3 months", 1, 0)) %>%
  mutate(vax_time_group4 = ifelse(days_btw_mab_collection_cat_3 == "3-4 months", 1, 0)) %>%
  mutate(vax_time_group5 = ifelse(days_btw_mab_collection_cat_3 == "4 months +", 1, 0))

###################################
# Against RSV infection 
###################################

# prepare the input dataset for jags 
df.jags <- df %>% mutate(case_control = positive_rsv) 

# # include birth weight and gestage<37wks as confounders 
# df.jags <- df.jags %>%
#   filter(!is.na(cf_birth_weight) & !is.na(risk_factor_gestagelessthan37wks))
  

dataset_1monthinterval_infection <- 
            list(
                N_records = nrow(df.jags),
                vax = df.jags$rsv_mab,
                vax_time_group1 = df.jags$vax_time_group1,
                vax_time_group2 = df.jags$vax_time_group2,
                vax_time_group3 = df.jags$vax_time_group3,
                vax_time_group4 = df.jags$vax_time_group4,
                vax_time_group5 = df.jags$vax_time_group5,
                case_status = df.jags$case_control,
                # confounders
                cf_birth_weight = df.jags$birth_weight,
                cf_gestage = df.jags$risk_factor_gestagelessthan37wks,
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4
                )

source("jags_waning.R")

if(rerun){
  
  jags.post <- rjags::jags.model(textConnection(model_string_waning_1monthinterval), 
                          data = dataset_1monthinterval_infection,
                          n.chains = 3)

  samples <- rjags::coda.samples(jags.post, 
                          variable.names=c("beta1", "beta2", "beta3", "beta4", "beta5"),
                          n.iter = 5000)
  saveRDS(samples, "../data/jags/post/wane_1monthinterval_infection.rds")

}else{
  samples <- readRDS("../data/jags/post/wane_1monthinterval_infection.rds")
}

post1 <- as.data.frame(as.matrix(samples[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples[[3]][-c(1:4500),])) 
post <- bind_rows(post1, post2, post3)

ve.median.0_1m <- round((1 - exp(median(post$beta1)))*100,1)
ve.lb.0_1m <- round((1 - exp(quantile(post$beta1, 0.975))) *100,1)
ve.ub.0_1m <- round((1 - exp(quantile(post$beta1, 0.025)))*100, 1)

ve.median.1_2m <- round((1 - exp(median(post$beta2)))*100,1)
ve.lb.1_2m <- round((1 - exp(quantile(post$beta2, 0.975))) *100,1)
ve.ub.1_2m <- round((1 - exp(quantile(post$beta2, 0.025)))*100, 1)

ve.median.2_3m <- round((1 - exp(median(post$beta3)))*100,1)
ve.lb.2_3m <- round((1 - exp(quantile(post$beta3, 0.975))) *100,1)
ve.ub.2_3m <- round((1 - exp(quantile(post$beta3, 0.025)))*100, 1)

ve.median.3_4m <- round((1 - exp(median(post$beta4)))*100,1)
ve.lb.3_4m <- round((1 - exp(quantile(post$beta4, 0.975))) *100,1)
ve.ub.3_4m <- round((1 - exp(quantile(post$beta4, 0.025)))*100, 1)

ve.median.4m <- round((1 - exp(median(post$beta5)))*100,1)
ve.lb.4m <- round((1 - exp(quantile(post$beta5, 0.975))) *100,1)
ve.ub.4m <- round((1 - exp(quantile(post$beta5, 0.025)))*100, 1)

# look at the result
ve.1monthinterval.infection <- 
  data.frame(
  against = rep("RSV infection", 6),
  vax_time = c("not vaccinated",
               "vaccinated 0-1 months ago",
               "vaccinated 1-2 months ago",
               "vaccinated 2-3 months ago",
               "vaccinated 3-4 months ago",
               "vaccinated 4+ months ago"),
  VE.adjusted = c(
    "REF",
    paste0(ve.median.0_1m, " (", ve.lb.0_1m, "-", ve.ub.0_1m, ")"),
    paste0(ve.median.1_2m, " (", ve.lb.1_2m, "-", ve.ub.1_2m, ")"),
    paste0(ve.median.2_3m, " (", ve.lb.2_3m, "-", ve.ub.2_3m, ")"),
    paste0(ve.median.3_4m, " (", ve.lb.3_4m, "-", ve.ub.3_4m, ")"),
    paste0(ve.median.4m, " (", ve.lb.4m, "-", ve.ub.4m, ")")
  )
) %>% 
  cbind(
    table(df.jags$days_btw_mab_collection_cat_3, df.jags$case_control) %>%
      matrix(ncol = 2)
  ) %>%
  dplyr::rename(n_cases = `2`, n_controls = `1`)
  
# for plotting 
df.ve.1monthinterval.infection <- 
  data.frame(
  against = rep("RSV infection", 5),
  vax_time = c(
               "vaccinated 0-1 months ago",
               "vaccinated 1-2 months ago",
               "vaccinated 2-3 months ago",
               "vaccinated 3-4 months ago",
               "vaccinated 4+ months ago"),
  VE.median = c(ve.median.0_1m, ve.median.1_2m, ve.median.2_3m, ve.median.3_4m, ve.median.4m),
  VE.lb = c(ve.lb.0_1m, ve.lb.1_2m, ve.lb.2_3m, ve.lb.3_4m, ve.lb.4m),
  VE.ub = c(ve.ub.0_1m, ve.ub.1_2m, ve.ub.2_3m, ve.ub.3_4m, ve.ub.4m)
  )



# 
# plot(samples[, "beta1"])
# title("beta1")
# plot(samples[, "beta2"])
# title("beta2")
# plot(samples[, "beta3"])
# title("beta3")
# plot(samples[, "beta4"])
# title("beta4")
# plot(samples[, "beta5"])
# title("beta5")


###################################
# Against RSV LRTI
###################################

# prepare the input dataset for jags 
df.jags <- df %>% 
  filter(symp_LRT_distress == 1) %>%
  mutate(case_control = positive_rsv)

# # include birth weight and gestage<37wks as confounders 
# df.jags <- df.jags %>%
#   filter(!is.na(cf_birth_weight) & !is.na(risk_factor_gestagelessthan37wks))


dataset_1monthinterval_RSVLRTI <- 
            list(
                N_records = nrow(df.jags),
                vax = df.jags$rsv_mab,
                vax_time_group1 = df.jags$vax_time_group1,
                vax_time_group2 = df.jags$vax_time_group2,
                vax_time_group3 = df.jags$vax_time_group3,
                vax_time_group4 = df.jags$vax_time_group4,
                vax_time_group5 = df.jags$vax_time_group5,
                case_status = df.jags$case_control,
                # confounders
                cf_birth_weight = df.jags$birth_weight,
                cf_gestage = df.jags$risk_factor_gestagelessthan37wks,
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4
                )

source("jags_waning.R")

if(rerun){
  
  jags.post <- rjags::jags.model(textConnection(model_string_waning_1monthinterval), 
                          data = dataset_1monthinterval_RSVLRTI,
                          n.chains = 3)

  samples <- rjags::coda.samples(jags.post, 
                          variable.names=c("beta1", "beta2", "beta3", "beta4", "beta5"),
                          n.iter = 5000)
  saveRDS(samples, "../data/jags/post/wane_1monthinterval_RSVLRTI.rds")

}else{
  samples <- readRDS("../data/jags/post/wane_1monthinterval_RSVLRTI.rds")
}

post1 <- as.data.frame(as.matrix(samples[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples[[3]][-c(1:4500),])) 
post <- bind_rows(post1, post2, post3)

ve.median.0_1m <- round((1 - exp(median(post$beta1)))*100,1)
ve.lb.0_1m <- round((1 - exp(quantile(post$beta1, 0.975))) *100,1)
ve.ub.0_1m <- round((1 - exp(quantile(post$beta1, 0.025)))*100, 1)

ve.median.1_2m <- round((1 - exp(median(post$beta2)))*100,1)
ve.lb.1_2m <- round((1 - exp(quantile(post$beta2, 0.975))) *100,1)
ve.ub.1_2m <- round((1 - exp(quantile(post$beta2, 0.025)))*100, 1)

ve.median.2_3m <- round((1 - exp(median(post$beta3)))*100,1)
ve.lb.2_3m <- round((1 - exp(quantile(post$beta3, 0.975))) *100,1)
ve.ub.2_3m <- round((1 - exp(quantile(post$beta3, 0.025)))*100, 1)

ve.median.3_4m <- round((1 - exp(median(post$beta4)))*100,1)
ve.lb.3_4m <- round((1 - exp(quantile(post$beta4, 0.975))) *100,1)
ve.ub.3_4m <- round((1 - exp(quantile(post$beta4, 0.025)))*100, 1)

ve.median.4m <- round((1 - exp(median(post$beta5)))*100,1)
ve.lb.4m <- round((1 - exp(quantile(post$beta5, 0.975))) *100,1)
ve.ub.4m <- round((1 - exp(quantile(post$beta5, 0.025)))*100, 1)

# look at the result
ve.1monthinterval.RSVLRTI <- 
  data.frame(
  against = rep("RSV LRTI", 6),
  vax_time = c("not vaccinated",
               "vaccinated 0-1 months ago",
               "vaccinated 1-2 months ago",
               "vaccinated 2-3 months ago",
               "vaccinated 3-4 months ago",
               "vaccinated 4+ months ago"),
  VE.adjusted = c(
    "REF",
    paste0(ve.median.0_1m, " (", ve.lb.0_1m, "-", ve.ub.0_1m, ")"),
    paste0(ve.median.1_2m, " (", ve.lb.1_2m, "-", ve.ub.1_2m, ")"),
    paste0(ve.median.2_3m, " (", ve.lb.2_3m, "-", ve.ub.2_3m, ")"),
    paste0(ve.median.3_4m, " (", ve.lb.3_4m, "-", ve.ub.3_4m, ")"),
    paste0(ve.median.4m, " (", ve.lb.4m, "-", ve.ub.4m, ")")
  )
) %>% 
  cbind(
    table(df.jags$days_btw_mab_collection_cat_3, df.jags$case_control) %>%
      matrix(ncol = 2)
  ) %>%
  dplyr::rename(n_cases = `2`, n_controls = `1`)
  

# for plotting 
df.ve.1monthinterval.RSVLRTI <- 
  data.frame(
  against = rep("RSV LRTI", 5),
  vax_time = c(
               "vaccinated 0-1 months ago",
               "vaccinated 1-2 months ago",
               "vaccinated 2-3 months ago",
               "vaccinated 3-4 months ago",
               "vaccinated 4+ months ago"),
  VE.median = c(ve.median.0_1m, ve.median.1_2m, ve.median.2_3m, ve.median.3_4m, ve.median.4m),
  VE.lb = c(ve.lb.0_1m, ve.lb.1_2m, ve.lb.2_3m, ve.lb.3_4m, ve.lb.4m),
  VE.ub = c(ve.ub.0_1m, ve.ub.1_2m, ve.ub.2_3m, ve.ub.3_4m, ve.ub.4m)
  )

###################################
# Against RSV outpatient visit
###################################

# prepare the input dataset for jags 
df.jags <- df %>% 
  filter(encounter_type == "outpatient") %>%
  mutate(case_control = positive_rsv)

# # include birth weight and gestage<37wks as confounders 
# df.jags <- df.jags %>%
#   filter(!is.na(cf_birth_weight) & !is.na(risk_factor_gestagelessthan37wks))

dataset_1monthinterval_RSVoutpatient <- 
            list(
                N_records = nrow(df.jags),
                vax = df.jags$rsv_mab,
                vax_time_group1 = df.jags$vax_time_group1,
                vax_time_group2 = df.jags$vax_time_group2,
                vax_time_group3 = df.jags$vax_time_group3,
                vax_time_group4 = df.jags$vax_time_group4,
                vax_time_group5 = df.jags$vax_time_group5,
                case_status = df.jags$case_control,
                # confounders
                cf_birth_weight = df.jags$birth_weight,
                cf_gestage = df.jags$risk_factor_gestagelessthan37wks,
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4
                )

source("jags_waning.R")

if(rerun){
  
  jags.post <- rjags::jags.model(textConnection(model_string_waning_1monthinterval), 
                          data = dataset_1monthinterval_RSVoutpatient,
                          n.chains = 3)

  samples <- rjags::coda.samples(jags.post, 
                          variable.names=c("beta1", "beta2", "beta3", "beta4", "beta5"),
                          n.iter = 5000)
  saveRDS(samples, "../data/jags/post/wane_1monthinterval_RSVoutpatient.rds")

}else{
  samples <- readRDS("../data/jags/post/wane_1monthinterval_RSVoutpatient.rds")
}

post1 <- as.data.frame(as.matrix(samples[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples[[3]][-c(1:4500),])) 
post <- bind_rows(post1, post2, post3)

ve.median.0_1m <- round((1 - exp(median(post$beta1)))*100,1)
ve.lb.0_1m <- round((1 - exp(quantile(post$beta1, 0.975))) *100,1)
ve.ub.0_1m <- round((1 - exp(quantile(post$beta1, 0.025)))*100, 1)

ve.median.1_2m <- round((1 - exp(median(post$beta2)))*100,1)
ve.lb.1_2m <- round((1 - exp(quantile(post$beta2, 0.975))) *100,1)
ve.ub.1_2m <- round((1 - exp(quantile(post$beta2, 0.025)))*100, 1)

ve.median.2_3m <- round((1 - exp(median(post$beta3)))*100,1)
ve.lb.2_3m <- round((1 - exp(quantile(post$beta3, 0.975))) *100,1)
ve.ub.2_3m <- round((1 - exp(quantile(post$beta3, 0.025)))*100, 1)

ve.median.3_4m <- round((1 - exp(median(post$beta4)))*100,1)
ve.lb.3_4m <- round((1 - exp(quantile(post$beta4, 0.975))) *100,1)
ve.ub.3_4m <- round((1 - exp(quantile(post$beta4, 0.025)))*100, 1)

ve.median.4m <- round((1 - exp(median(post$beta5)))*100,1)
ve.lb.4m <- round((1 - exp(quantile(post$beta5, 0.975))) *100,1)
ve.ub.4m <- round((1 - exp(quantile(post$beta5, 0.025)))*100, 1)

# look at the result
ve.1monthinterval.RSVoutpatient <- 
  data.frame(
  against = rep("RSV outpatient visit", 6),
  vax_time = c("not vaccinated",
               "vaccinated 0-1 months ago",
               "vaccinated 1-2 months ago",
               "vaccinated 2-3 months ago",
               "vaccinated 3-4 months ago",
               "vaccinated 4+ months ago"),
  VE.adjusted = c(
    "REF",
    paste0(ve.median.0_1m, " (", ve.lb.0_1m, "-", ve.ub.0_1m, ")"),
    paste0(ve.median.1_2m, " (", ve.lb.1_2m, "-", ve.ub.1_2m, ")"),
    paste0(ve.median.2_3m, " (", ve.lb.2_3m, "-", ve.ub.2_3m, ")"),
    paste0(ve.median.3_4m, " (", ve.lb.3_4m, "-", ve.ub.3_4m, ")"),
    paste0(ve.median.4m, " (", ve.lb.4m, "-", ve.ub.4m, ")")
  )
) %>% 
  cbind(
    table(df.jags$days_btw_mab_collection_cat_3, df.jags$case_control) %>%
      matrix(ncol = 2)
  ) %>%
  dplyr::rename(n_cases = `2`, n_controls = `1`)

# for plotting 
df.ve.1monthinterval.RSVoutpatient <- 
  data.frame(
  against = rep("RSV outpatient visit", 5),
  vax_time = c(
               "vaccinated 0-1 months ago",
               "vaccinated 1-2 months ago",
               "vaccinated 2-3 months ago",
               "vaccinated 3-4 months ago",
               "vaccinated 4+ months ago"),
  VE.median = c(ve.median.0_1m, ve.median.1_2m, ve.median.2_3m, ve.median.3_4m, ve.median.4m),
  VE.lb = c(ve.lb.0_1m, ve.lb.1_2m, ve.lb.2_3m, ve.lb.3_4m, ve.lb.4m),
  VE.ub = c(ve.ub.0_1m, ve.ub.1_2m, ve.ub.2_3m, ve.ub.3_4m, ve.ub.4m)
  )




###################################
# Against RSV hosp
###################################

# prepare the input dataset for jags 
df.jags <- df %>% 
  filter(encounter_type == "inpatient") %>%
  mutate(case_control = positive_rsv)

# # include birth weight and gestage<37wks as confounders 
# df.jags <- df.jags %>%
#   filter(!is.na(cf_birth_weight) & !is.na(risk_factor_gestagelessthan37wks))

dataset_1monthinterval_RSVhosp <- 
            list(
                N_records = nrow(df.jags),
                vax = df.jags$rsv_mab,
                vax_time_group1 = df.jags$vax_time_group1,
                vax_time_group2 = df.jags$vax_time_group2,
                vax_time_group3 = df.jags$vax_time_group3,
                vax_time_group4 = df.jags$vax_time_group4,
                vax_time_group5 = df.jags$vax_time_group5,
                case_status = df.jags$case_control,
                # confounders
                cf_birth_weight = df.jags$birth_weight,
                cf_gestage = df.jags$risk_factor_gestagelessthan37wks,
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4
                )

source("jags_waning.R")

if(rerun){
  
  jags.post <- rjags::jags.model(textConnection(model_string_waning_1monthinterval), 
                          data = dataset_1monthinterval_RSVhosp,
                          n.chains = 3)

  samples <- rjags::coda.samples(jags.post, 
                          variable.names=c("beta1", "beta2", "beta3", "beta4", "beta5"),
                          n.iter = 5000)
  saveRDS(samples, "../data/jags/post/wane_1monthinterval_RSVhosp.rds")

}else{
  samples <- readRDS("../data/jags/post/wane_1monthinterval_RSVhosp.rds")
}

post1 <- as.data.frame(as.matrix(samples[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples[[3]][-c(1:4500),])) 
post <- bind_rows(post1, post2, post3)

ve.median.0_1m <- round((1 - exp(median(post$beta1)))*100,1)
ve.lb.0_1m <- round((1 - exp(quantile(post$beta1, 0.975))) *100,1)
ve.ub.0_1m <- round((1 - exp(quantile(post$beta1, 0.025)))*100, 1)

ve.median.1_2m <- round((1 - exp(median(post$beta2)))*100,1)
ve.lb.1_2m <- round((1 - exp(quantile(post$beta2, 0.975))) *100,1)
ve.ub.1_2m <- round((1 - exp(quantile(post$beta2, 0.025)))*100, 1)

ve.median.2_3m <- round((1 - exp(median(post$beta3)))*100,1)
ve.lb.2_3m <- round((1 - exp(quantile(post$beta3, 0.975))) *100,1)
ve.ub.2_3m <- round((1 - exp(quantile(post$beta3, 0.025)))*100, 1)

ve.median.3_4m <- round((1 - exp(median(post$beta4)))*100,1)
ve.lb.3_4m <- round((1 - exp(quantile(post$beta4, 0.975))) *100,1)
ve.ub.3_4m <- round((1 - exp(quantile(post$beta4, 0.025)))*100, 1)

ve.median.4m <- round((1 - exp(median(post$beta5)))*100,1)
ve.lb.4m <- round((1 - exp(quantile(post$beta5, 0.975))) *100,1)
ve.ub.4m <- round((1 - exp(quantile(post$beta5, 0.025)))*100, 1)

# look at the result
ve.1monthinterval.RSVhosp <- 
  data.frame(
  against = rep("RSV hospitalization", 6),
  vax_time = c("not vaccinated",
               "vaccinated 0-1 months ago",
               "vaccinated 1-2 months ago",
               "vaccinated 2-3 months ago",
               "vaccinated 3-4 months ago",
               "vaccinated 4+ months ago"),
  VE.adjusted = c(
    "REF",
    paste0(ve.median.0_1m, " (", ve.lb.0_1m, "-", ve.ub.0_1m, ")"),
    paste0(ve.median.1_2m, " (", ve.lb.1_2m, "-", ve.ub.1_2m, ")"),
    paste0(ve.median.2_3m, " (", ve.lb.2_3m, "-", ve.ub.2_3m, ")"),
    paste0(ve.median.3_4m, " (", ve.lb.3_4m, "-", ve.ub.3_4m, ")"),
    paste0(ve.median.4m, " (", ve.lb.4m, "-", ve.ub.4m, ")")
  )
) %>% 
  cbind(
    table(df.jags$days_btw_mab_collection_cat_3, df.jags$case_control) %>%
      matrix(ncol = 2)
  ) %>%
  dplyr::rename(n_cases = `2`, n_controls = `1`)

# for plotting 
df.ve.1monthinterval.RSVhosp <- 
  data.frame(
  against = rep("RSV hospitalization", 5),
  vax_time = c(
               "vaccinated 0-1 months ago",
               "vaccinated 1-2 months ago",
               "vaccinated 2-3 months ago",
               "vaccinated 3-4 months ago",
               "vaccinated 4+ months ago"),
  VE.median = c(ve.median.0_1m, ve.median.1_2m, ve.median.2_3m, ve.median.3_4m, ve.median.4m),
  VE.lb = c(ve.lb.0_1m, ve.lb.1_2m, ve.lb.2_3m, ve.lb.3_4m, ve.lb.4m),
  VE.ub = c(ve.ub.0_1m, ve.ub.1_2m, ve.ub.2_3m, ve.ub.3_4m, ve.ub.4m)
  )

###################################
# Against RSV LRTI hosp
###################################

# prepare the input dataset for jags 
df.jags <- df %>% 
  filter(encounter_type == "inpatient" & symp_LRT_distress == 1) %>%
  mutate(case_control = positive_rsv)

# # include birth weight and gestage<37wks as confounders 
# df.jags <- df.jags %>%
#   filter(!is.na(cf_birth_weight) & !is.na(risk_factor_gestagelessthan37wks))

dataset_1monthinterval_RSVLRTIhosp <- 
            list(
                N_records = nrow(df.jags),
                vax = df.jags$rsv_mab,
                vax_time_group1 = df.jags$vax_time_group1,
                vax_time_group2 = df.jags$vax_time_group2,
                vax_time_group3 = df.jags$vax_time_group3,
                vax_time_group4 = df.jags$vax_time_group4,
                vax_time_group5 = df.jags$vax_time_group5,
                case_status = df.jags$case_control,
                # confounders
                cf_birth_weight = df.jags$birth_weight,
                cf_gestage = df.jags$risk_factor_gestagelessthan37wks,
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4
                )

source("jags_waning.R")

if(rerun){
  
  jags.post <- rjags::jags.model(textConnection(model_string_waning_1monthinterval), 
                          data = dataset_1monthinterval_RSVLRTIhosp,
                          n.chains = 3)

  samples <- rjags::coda.samples(jags.post, 
                          variable.names=c("beta1", "beta2", "beta3", "beta4", "beta5"),
                          n.iter = 5000)
  saveRDS(samples, "../data/jags/post/wane_1monthinterval_RSVLRTIhosp.rds")

}else{
  samples <- readRDS("../data/jags/post/wane_1monthinterval_RSVLRTIhosp.rds")
}

post1 <- as.data.frame(as.matrix(samples[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples[[3]][-c(1:4500),])) 
post <- bind_rows(post1, post2, post3)

ve.median.0_1m <- round((1 - exp(median(post$beta1)))*100,1)
ve.lb.0_1m <- round((1 - exp(quantile(post$beta1, 0.975))) *100,1)
ve.ub.0_1m <- round((1 - exp(quantile(post$beta1, 0.025)))*100, 1)

ve.median.1_2m <- round((1 - exp(median(post$beta2)))*100,1)
ve.lb.1_2m <- round((1 - exp(quantile(post$beta2, 0.975))) *100,1)
ve.ub.1_2m <- round((1 - exp(quantile(post$beta2, 0.025)))*100, 1)

ve.median.2_3m <- round((1 - exp(median(post$beta3)))*100,1)
ve.lb.2_3m <- round((1 - exp(quantile(post$beta3, 0.975))) *100,1)
ve.ub.2_3m <- round((1 - exp(quantile(post$beta3, 0.025)))*100, 1)

ve.median.3_4m <- round((1 - exp(median(post$beta4)))*100,1)
ve.lb.3_4m <- round((1 - exp(quantile(post$beta4, 0.975))) *100,1)
ve.ub.3_4m <- round((1 - exp(quantile(post$beta4, 0.025)))*100, 1)

ve.median.4m <- round((1 - exp(median(post$beta5)))*100,1)
ve.lb.4m <- round((1 - exp(quantile(post$beta5, 0.975))) *100,1)
ve.ub.4m <- round((1 - exp(quantile(post$beta5, 0.025)))*100, 1)

# look at the result
ve.1monthinterval.RSVLRTIhosp <- 
  data.frame(
  against = rep("RSV LRTI hospitalization", 6),
  vax_time = c("not vaccinated",
               "vaccinated 0-1 months ago",
               "vaccinated 1-2 months ago",
               "vaccinated 2-3 months ago",
               "vaccinated 3-4 months ago",
               "vaccinated 4+ months ago"),
  VE.adjusted = c(
    "REF",
    paste0(ve.median.0_1m, " (", ve.lb.0_1m, "-", ve.ub.0_1m, ")"),
    paste0(ve.median.1_2m, " (", ve.lb.1_2m, "-", ve.ub.1_2m, ")"),
    paste0(ve.median.2_3m, " (", ve.lb.2_3m, "-", ve.ub.2_3m, ")"),
    paste0(ve.median.3_4m, " (", ve.lb.3_4m, "-", ve.ub.3_4m, ")"),
    paste0(ve.median.4m, " (", ve.lb.4m, "-", ve.ub.4m, ")")
  )
) %>% 
  cbind(
    table(df.jags$days_btw_mab_collection_cat_3, df.jags$case_control) %>%
      matrix(ncol = 2)
  ) %>%
  dplyr::rename(n_cases = `2`, n_controls = `1`)

# for plotting 
df.ve.1monthinterval.RSVLRTIhosp <- 
  data.frame(
  against = rep("RSV LRTI hospitalization", 5),
  vax_time = c(
               "vaccinated 0-1 months ago",
               "vaccinated 1-2 months ago",
               "vaccinated 2-3 months ago",
               "vaccinated 3-4 months ago",
               "vaccinated 4+ months ago"),
  VE.median = c(ve.median.0_1m, ve.median.1_2m, ve.median.2_3m, ve.median.3_4m, ve.median.4m),
  VE.lb = c(ve.lb.0_1m, ve.lb.1_2m, ve.lb.2_3m, ve.lb.3_4m, ve.lb.4m),
  VE.ub = c(ve.ub.0_1m, ve.ub.1_2m, ve.ub.2_3m, ve.ub.3_4m, ve.ub.4m)
  )


###################################
# Against RSV severe outcomes
###################################

# prepare the input dataset for jags 
df.jags <- df %>% 
  filter(icu_admitted == "yes" | highflow_oxygen == 1) %>%
  mutate(case_control = positive_rsv)

# # include birth weight and gestage<37wks as confounders 
# df.jags <- df.jags %>%
#   filter(!is.na(cf_birth_weight) & !is.na(risk_factor_gestagelessthan37wks))

dataset_1monthinterval_RSVsevere <- 
            list(
                N_records = nrow(df.jags),
                vax = df.jags$rsv_mab,
                vax_time_group1 = df.jags$vax_time_group1,
                vax_time_group2 = df.jags$vax_time_group2,
                vax_time_group3 = df.jags$vax_time_group3,
                vax_time_group4 = df.jags$vax_time_group4,
                vax_time_group5 = df.jags$vax_time_group5,
                case_status = df.jags$case_control,
                # confounders
                cf_birth_weight = df.jags$birth_weight,
                cf_gestage = df.jags$risk_factor_gestagelessthan37wks,
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4
                )

source("jags_waning.R")

if(rerun){
  
  jags.post <- rjags::jags.model(textConnection(model_string_waning_1monthinterval), 
                          data = dataset_1monthinterval_RSVsevere,
                          n.chains = 3)

  samples <- rjags::coda.samples(jags.post, 
                          variable.names=c("beta1", "beta2", "beta3", "beta4", "beta5"),
                          n.iter = 5000)
  saveRDS(samples, "../data/jags/post/wane_1monthinterval_RSVsevere.rds")

}else{
  samples <- readRDS("../data/jags/post/wane_1monthinterval_RSVsevere.rds")
}

post1 <- as.data.frame(as.matrix(samples[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples[[3]][-c(1:4500),])) 
post <- bind_rows(post1, post2, post3)

ve.median.0_1m <- round((1 - exp(median(post$beta1)))*100,1)
ve.lb.0_1m <- round((1 - exp(quantile(post$beta1, 0.975))) *100,1)
ve.ub.0_1m <- round((1 - exp(quantile(post$beta1, 0.025)))*100, 1)

ve.median.1_2m <- round((1 - exp(median(post$beta2)))*100,1)
ve.lb.1_2m <- round((1 - exp(quantile(post$beta2, 0.975))) *100,1)
ve.ub.1_2m <- round((1 - exp(quantile(post$beta2, 0.025)))*100, 1)

ve.median.2_3m <- round((1 - exp(median(post$beta3)))*100,1)
ve.lb.2_3m <- round((1 - exp(quantile(post$beta3, 0.975))) *100,1)
ve.ub.2_3m <- round((1 - exp(quantile(post$beta3, 0.025)))*100, 1)

ve.median.3_4m <- round((1 - exp(median(post$beta4)))*100,1)
ve.lb.3_4m <- round((1 - exp(quantile(post$beta4, 0.975))) *100,1)
ve.ub.3_4m <- round((1 - exp(quantile(post$beta4, 0.025)))*100, 1)

ve.median.4m <- round((1 - exp(median(post$beta5)))*100,1)
ve.lb.4m <- round((1 - exp(quantile(post$beta5, 0.975))) *100,1)
ve.ub.4m <- round((1 - exp(quantile(post$beta5, 0.025)))*100, 1)

# look at the result
ve.1monthinterval.RSVsevere <- 
  data.frame(
  against = rep("RSV severe outcomes", 6),
  vax_time = c("not vaccinated",
               "vaccinated 0-1 months ago",
               "vaccinated 1-2 months ago",
               "vaccinated 2-3 months ago",
               "vaccinated 3-4 months ago",
               "vaccinated 4+ months ago"),
  VE.adjusted = c(
    "REF",
    paste0(ve.median.0_1m, " (", ve.lb.0_1m, "-", ve.ub.0_1m, ")"),
    paste0(ve.median.1_2m, " (", ve.lb.1_2m, "-", ve.ub.1_2m, ")"),
    paste0(ve.median.2_3m, " (", ve.lb.2_3m, "-", ve.ub.2_3m, ")"),
    paste0(ve.median.3_4m, " (", ve.lb.3_4m, "-", ve.ub.3_4m, ")"),
    paste0(ve.median.4m, " (", ve.lb.4m, "-", ve.ub.4m, ")")
  )
) %>% 
  cbind(
    table(df.jags$days_btw_mab_collection_cat_3, df.jags$case_control) %>%
      matrix(ncol = 2)
  ) %>%
  dplyr::rename(n_cases = `2`, n_controls = `1`)

# for plotting 
df.ve.1monthinterval.RSVsevere <- 
  data.frame(
  against = rep("RSV severe outcomes", 5),
  vax_time = c(
               "vaccinated 0-1 months ago",
               "vaccinated 1-2 months ago",
               "vaccinated 2-3 months ago",
               "vaccinated 3-4 months ago",
               "vaccinated 4+ months ago"),
  VE.median = c(ve.median.0_1m, ve.median.1_2m, ve.median.2_3m, ve.median.3_4m, ve.median.4m),
  VE.lb = c(ve.lb.0_1m, ve.lb.1_2m, ve.lb.2_3m, ve.lb.3_4m, ve.lb.4m),
  VE.ub = c(ve.ub.0_1m, ve.ub.1_2m, ve.ub.2_3m, ve.ub.3_4m, ve.ub.4m)
  )



  

# look at all the results with 1-month interval
ve.1monthinterval.infection %>%
  rbind(ve.1monthinterval.RSVoutpatient, 
        ve.1monthinterval.RSVhosp,
        ve.1monthinterval.RSVLRTI, 
        ve.1monthinterval.RSVLRTIhosp,
        ve.1monthinterval.RSVsevere) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T, groupBy = "against") 

# save the data table 
tab.ve.wane.1m <- 
  ve.1monthinterval.infection %>%
  rbind(ve.1monthinterval.RSVoutpatient, 
        ve.1monthinterval.RSVhosp,
        ve.1monthinterval.RSVLRTI, 
        ve.1monthinterval.RSVLRTIhosp,
        ve.1monthinterval.RSVsevere) %>%
  mutate(vax_time = case_when(vax_time == "not vaccinated" ~ "Not vaccinated",
                                    vax_time == "vaccinated 0-1 months ago" ~ "(0, 1)",
                                    vax_time == "vaccinated 1-2 months ago" ~ "[1, 2)", 
                                    vax_time == "vaccinated 2-3 months ago" ~ "[2, 3)", 
                                    vax_time == "vaccinated 3-4 months ago" ~ "[3, 4)", 
                                    vax_time == "vaccinated 4+ months ago" ~ "[4, )")) %>%
  dplyr::select(against, vax_time, n_cases, n_controls, VE.adjusted) %>%
  flextable() %>%
  set_header_labels(against = "Outcome prevented",
                    vax_time = "Time since vaccination (months)",
                    n_cases = "RSV positive",
                    n_controls = "RSV negative",
                    VE.adjusted = "Adjusted VE (95% CI)"
                    ) %>%
  merge_at(i = 1:6, j = 1) %>%
  merge_at(i = 7:12, j = 1) %>%
  merge_at(i = 13:18, j = 1) %>%
  merge_at(i = 19:24, j = 1) %>%
  merge_at(i = 25:30, j = 1) %>%
  width(j = c(1,2,5), width = 2) %>%
  vline() %>%
  hline()

if(savenewplot){
  save_as_docx(tab.ve.wane.1m, path = "../figs_tabs/tables/jags.wane.1m.docx")
}
  
```

#### waning figure, showing full CIs
```{r fig.width = 12, fig.height = 4}
df.plt.wane <- 
  df.ve.1monthinterval.infection %>%
  rbind(df.ve.1monthinterval.RSVoutpatient, 
        df.ve.1monthinterval.RSVhosp,
        df.ve.1monthinterval.RSVLRTI, 
        df.ve.1monthinterval.RSVLRTIhosp,
        df.ve.1monthinterval.RSVsevere) %>% 
  mutate(time_since_vax = case_when(vax_time == "vaccinated 0-1 months ago" ~ "1",
                                    vax_time == "vaccinated 1-2 months ago" ~ "2", 
                                    vax_time == "vaccinated 2-3 months ago" ~ "3", 
                                    vax_time == "vaccinated 3-4 months ago" ~ "4", 
                                    vax_time == "vaccinated 4+ months ago" ~ "4+")) %>%
  mutate(VE = paste0(round(VE.median), " (", round(VE.lb), ", ", round(VE.ub), ")")) %>% 
  mutate(time_since_vax = factor(time_since_vax, levels = c("1", "2","3","4","4+"))) %>% 
  mutate(against = paste0("Against ", against)) %>%
  mutate(against = factor(against, levels = c("Against RSV infection",
                                              "Against RSV outpatient visit",
                                              "Against RSV hospitalization",
                                              "Against RSV LRTI",
                                              "Against RSV LRTI hospitalization",
                                              "Against RSV severe outcomes")))

df.plt.wane %>%
  ggplot() +
  geom_point(aes(x = time_since_vax, y = VE.median, color = against), 
             position = position_dodge(0.5)) +
  geom_errorbar(aes(x = time_since_vax, ymin = VE.lb, ymax = VE.ub, color = against), 
                width = 0, position = position_dodge(0.5)) +
  geom_text(aes(x = time_since_vax, y = VE.median, color = against, label = VE), 
            angle = 90, position = position_dodge(0.5), vjust = - 0.7, show_guide = F,
            size = 2.5) +
  theme_classic() +
  scale_color_brewer(palette = "Dark2") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ylab("Effectiveness of Nirsevimab (%)") +
  xlab("Time since vaccination (months)") +
  labs(color = "Clinical endpoint")

```

#### Waning figure, showing partial CIs
```{r fig.width = 12, fig.height = 4}
df.no.arrow <- 
  df.plt.wane %>%
  mutate(add_arrow = ifelse(VE.lb <= -25, 1, 0)) %>%
  mutate(VE.lb = ifelse(add_arrow == 1, -25, VE.lb)) %>% 
  mutate(across(starts_with("VE"), ~ ifelse(add_arrow == 1, NA, .)))

df.add.arrow <- 
  df.plt.wane %>%
  mutate(add_arrow = ifelse(VE.lb <= -25, 1, 0)) %>%
  mutate(VE.lb = ifelse(add_arrow == 1, -25, VE.lb)) %>% 
  mutate(across(starts_with("VE"), ~ ifelse(add_arrow != 1, NA, .)))

# adjusted arrows to parallel
# https://stackoverflow.com/questions/67853990/geom-segment-parallel-dodging
space_between_bars <- 0.145
df.add.arrow$against_x_adj = scale(as.numeric(as.factor(df.add.arrow$against))) * space_between_bars
df.add.arrow$x = as.numeric(as.factor(df.add.arrow$time_since_vax)) + df.add.arrow$against_x_adj


ggplot() +
  # if lb > -25
  geom_point(aes(x = time_since_vax, y = VE.median, color = against), 
             position = position_dodge(0.5), data = df.no.arrow) +
  geom_errorbar(aes(x = time_since_vax, ymin = VE.lb, ymax = VE.ub, color = against), 
                width = 0, position = position_dodge(0.5), data = df.no.arrow) +
  geom_text(aes(x = time_since_vax, y = VE.median, color = against, label = VE), 
            angle = 90, position = position_dodge(0.5), vjust = - 0.7, show_guide = F,
            size = 3, data = df.no.arrow) +
  # if lb < -25
  geom_point(aes(x = time_since_vax, y = VE.median, color = against), 
             position = position_dodge(0.5), data = df.add.arrow) +
  geom_segment(aes(x = x, xend = x, 
                   y = VE.ub, yend = VE.lb, color = against),
               arrow = arrow(length = unit(2, "mm")),
               position = position_dodge(0.5),
               data = df.add.arrow, show_guide = F) +
  geom_text(aes(x = time_since_vax, y = VE.median, color = against, label = VE), 
            angle = 90, position = position_dodge(0.5), vjust = - 0.7, show_guide = F,
            size = 3, data = df.add.arrow) +
  theme_classic() +
  scale_color_brewer(palette = "Dark2") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ylab("Effectiveness of Nirsevimab (%)") +
  xlab("Time since vaccination (months)") +
  labs(color = "Clinical endpoint") +
  ylim(c(-25,100))  +
  scale_y_continuous(breaks = c(-25, 0, 25, 50, 75, 100),
                     labels = c("-25", "0", "25", "50", "75", "100"))
```

#### one outcome per panel
```{r fig.width = 9, fig.height = 6}
plt.jags.wane.1m <- 
  ggplot() +
  # if lb > -25
  geom_point(aes(x = time_since_vax, y = VE.median), 
             position = position_dodge(0.5), data = df.no.arrow) +
  geom_errorbar(aes(x = time_since_vax, ymin = VE.lb, ymax = VE.ub), 
                width = 0, position = position_dodge(0.5), data = df.no.arrow) +
  geom_text(aes(x = time_since_vax, y = VE.median-10, label = VE), 
            angle = 90, position = position_dodge(0.5), vjust = - 0.7, show_guide = F,
            size = 4, data = df.no.arrow) +
  # if lb < -25
  geom_point(aes(x = time_since_vax, y = VE.median), 
             position = position_dodge(0.5), data = df.add.arrow) +
  geom_segment(aes(x = time_since_vax, xend = time_since_vax, 
                   y = VE.ub, yend = VE.lb),
               arrow = arrow(length = unit(2, "mm")),
               position = position_dodge(0.5),
               data = df.add.arrow, show_guide = F) +
  geom_text(aes(x = time_since_vax, y = (VE.ub+30)/2, label = VE), 
            angle = 90, position = position_dodge(0.5), vjust = - 0.7, show_guide = F,
            size = 4, data = df.add.arrow) +
  theme_classic() +
  scale_color_brewer(palette = "Dark2") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ylab("Effectiveness of Nirsevimab (%)") +
  xlab("Time since vaccination (months)") +
  labs(color = "Clinical endpoint") +
  ylim(c(-25,100)) +
  scale_y_continuous(breaks = c(-25, 0, 25, 50, 75, 100),
                     labels = c("-25", "0", "25", "50", "75", "100")) +
  facet_wrap( ~ against) +
   theme(
    #panel.grid.major = element_line(color = "grey", linewidth = 0.1), 
    #panel.grid.minor = element_blank(),
    axis.text.x = element_text(size = 12),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 11)
     )
        

plt.jags.wane.1m

if(savenewplot){
  ggsave(plot = plt.jags.wane.1m, filename = "../figs_tabs/figures/jags.wane.1m.pdf", height = 6, width = 9)
}
```

<br>


### VE over time by **biweek** interval {.tabset}

  * classify time since vax to testing by biweek interval.
  * included confounders : age tested, month tested
  * uninformative prior for precision of the non-negative increment d's.
    + d ~ dnorm(0, tau)T(0,)
    + tau_d ~ dgamma(0.01, 0.01)
    
#### Table
```{r}
source("jags_waning.R")

df <- df %>%
  mutate(vax_time_group1 = ifelse(weeks_btw_mab_collection_cat == "(0, 2)", 1, 0),
         vax_time_group2 = ifelse(weeks_btw_mab_collection_cat == "[2, 4)", 1, 0),
         vax_time_group3 = ifelse(weeks_btw_mab_collection_cat == "[4, 6)", 1, 0),
         vax_time_group4 = ifelse(weeks_btw_mab_collection_cat == "[6, 8)", 1, 0),
         vax_time_group5 = ifelse(weeks_btw_mab_collection_cat == "[8, 10)", 1, 0),
         vax_time_group6 = ifelse(weeks_btw_mab_collection_cat == "[10, 12)", 1, 0),
         vax_time_group7 = ifelse(weeks_btw_mab_collection_cat == "[12, 14)", 1, 0),
         vax_time_group8 = ifelse(weeks_btw_mab_collection_cat == "[14, 16)", 1, 0),
         vax_time_group9 = ifelse(weeks_btw_mab_collection_cat == "[16, )", 1, 0)
         ) 

###################################
# Against RSV infection 
###################################

# prepare the input dataset for jags 
df.jags <- df %>% mutate(case_control = positive_rsv) 

# # include birth weight and gestage<37wks as confounders 
# df.jags <- df.jags %>%
#   filter(!is.na(cf_birth_weight) & !is.na(risk_factor_gestagelessthan37wks))
  

dataset_biwkinterval_infection <- 
            list(
                N_records = nrow(df.jags),
                vax = df.jags$rsv_mab,
                vax_time_group1 = df.jags$vax_time_group1,
                vax_time_group2 = df.jags$vax_time_group2,
                vax_time_group3 = df.jags$vax_time_group3,
                vax_time_group4 = df.jags$vax_time_group4,
                vax_time_group5 = df.jags$vax_time_group5,
                vax_time_group6 = df.jags$vax_time_group6,
                vax_time_group7 = df.jags$vax_time_group7,
                vax_time_group8 = df.jags$vax_time_group8,
                vax_time_group9 = df.jags$vax_time_group9,
                case_status = df.jags$case_control,
                # confounders
                cf_birth_weight = df.jags$birth_weight,
                cf_gestage = df.jags$risk_factor_gestagelessthan37wks,
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4
                )

source("jags_waning.R")

if(rerun){
  
  jags.post <- rjags::jags.model(textConnection(model_string_waning_biwkinterval), 
                          data = dataset_biwkinterval_infection,
                          n.chains = 3)

  samples <- rjags::coda.samples(jags.post, 
                          variable.names=c("beta1", "beta2", "beta3", "beta4", "beta5", "beta6",
                                           "beta7", "beta8", "beta9"),
                          n.iter = 5000)
  saveRDS(samples, "../data/jags/post/wane_biwkinterval_infection.rds")

}else{
  samples <- readRDS("../data/jags/post/wane_biwkinterval_infection.rds")
}

post1 <- as.data.frame(as.matrix(samples[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples[[3]][-c(1:4500),])) 
post <- bind_rows(post1, post2, post3)

ve.median.1 <- round((1 - exp(median(post$beta1)))*100,1)
ve.lb.1 <- round((1 - exp(quantile(post$beta1, 0.975))) *100,1)
ve.ub.1 <- round((1 - exp(quantile(post$beta1, 0.025)))*100, 1)

ve.median.2 <- round((1 - exp(median(post$beta2)))*100,1)
ve.lb.2 <- round((1 - exp(quantile(post$beta2, 0.975))) *100,1)
ve.ub.2 <- round((1 - exp(quantile(post$beta2, 0.025)))*100, 1)

ve.median.3 <- round((1 - exp(median(post$beta3)))*100,1)
ve.lb.3 <- round((1 - exp(quantile(post$beta3, 0.975))) *100,1)
ve.ub.3 <- round((1 - exp(quantile(post$beta3, 0.025)))*100, 1)

ve.median.4 <- round((1 - exp(median(post$beta4)))*100,1)
ve.lb.4 <- round((1 - exp(quantile(post$beta4, 0.975))) *100,1)
ve.ub.4 <- round((1 - exp(quantile(post$beta4, 0.025)))*100, 1)

ve.median.5 <- round((1 - exp(median(post$beta5)))*100,1)
ve.lb.5 <- round((1 - exp(quantile(post$beta5, 0.975))) *100,1)
ve.ub.5 <- round((1 - exp(quantile(post$beta5, 0.025)))*100, 1)

ve.median.6 <- round((1 - exp(median(post$beta6)))*100,1)
ve.lb.6 <- round((1 - exp(quantile(post$beta6, 0.975))) *100,1)
ve.ub.6 <- round((1 - exp(quantile(post$beta6, 0.025)))*100, 1)

ve.median.7 <- round((1 - exp(median(post$beta7)))*100,1)
ve.lb.7 <- round((1 - exp(quantile(post$beta7, 0.975))) *100,1)
ve.ub.7 <- round((1 - exp(quantile(post$beta7, 0.025)))*100, 1)

ve.median.8 <- round((1 - exp(median(post$beta8)))*100,1)
ve.lb.8 <- round((1 - exp(quantile(post$beta8, 0.975))) *100,1)
ve.ub.8 <- round((1 - exp(quantile(post$beta8, 0.025)))*100, 1)

ve.median.9 <- round((1 - exp(median(post$beta9)))*100,1)
ve.lb.9 <- round((1 - exp(quantile(post$beta9, 0.975))) *100,1)
ve.ub.9 <- round((1 - exp(quantile(post$beta9, 0.025)))*100, 1)

# look at the result
ve.biwkinterval.infection <- 
  data.frame(
  against = rep("RSV infection", 10),
  vax_time = c("not vaccinated",
               "(0, 2)",
               "[2, 4)",
               "[4, 6)",
               "[6, 8)",
               "[8, 10)",
               "[10, 12)",
               "[12, 14)",
               "[14, 16)",
               "[16, )"),
  VE.adjusted = c(
    "REF",
    paste0(ve.median.1, " (", ve.lb.1, "-", ve.ub.1, ")"),
    paste0(ve.median.2, " (", ve.lb.2, "-", ve.ub.2, ")"),
    paste0(ve.median.3, " (", ve.lb.3, "-", ve.ub.3, ")"),
    paste0(ve.median.4, " (", ve.lb.4, "-", ve.ub.4, ")"),
    paste0(ve.median.5, " (", ve.lb.5, "-", ve.ub.5, ")"),
    paste0(ve.median.6, " (", ve.lb.6, "-", ve.ub.6, ")"),
    paste0(ve.median.7, " (", ve.lb.7, "-", ve.ub.7, ")"),
    paste0(ve.median.8, " (", ve.lb.8, "-", ve.ub.8, ")"),
    paste0(ve.median.9, " (", ve.lb.9, "-", ve.ub.9, ")")
  )
) %>% 
  cbind(
    table(df.jags$weeks_btw_mab_collection_cat, df.jags$case_control) %>%
      matrix(ncol = 2)
  ) %>%
  dplyr::rename(n_cases = `2`, n_controls = `1`)
  
# for plotting 
df.ve.biwkinterval.infection <- 
  data.frame(
  against = rep("RSV infection", 9),
  vax_time = c("(0, 2)",
               "[2, 4)",
               "[4, 6)",
               "[6, 8)",
               "[8, 10)",
               "[10, 12)",
               "[12, 14)",
               "[14, 16)",
               "[16, )"),
  VE.median = c(ve.median.1, ve.median.2, ve.median.3, ve.median.4, ve.median.5, ve.median.6,
                ve.median.7, ve.median.8, ve.median.9),
  VE.lb = c(ve.lb.1, ve.lb.2, ve.lb.3, ve.lb.4, ve.lb.5,
            ve.lb.6, ve.lb.7, ve.lb.8, ve.lb.9),
  VE.ub = c(ve.ub.1, ve.ub.2, ve.ub.3, ve.ub.4, ve.ub.5,
            ve.ub.6, ve.ub.7, ve.ub.8, ve.ub.9)
  )



# 
# plot(samples[, "beta1"])
# title("beta1")



###################################
# Against RSV LRTI
###################################

# prepare the input dataset for jags 
df.jags <- df %>% 
  filter(symp_LRT_distress == 1) %>%
  mutate(case_control = positive_rsv) 

# # include birth weight and gestage<37wks as confounders 
# df.jags <- df.jags %>%
#   filter(!is.na(cf_birth_weight) & !is.na(risk_factor_gestagelessthan37wks))
  

dataset_biwkinterval_RSVLRTI <- 
            list(
                N_records = nrow(df.jags),
                vax = df.jags$rsv_mab,
                vax_time_group1 = df.jags$vax_time_group1,
                vax_time_group2 = df.jags$vax_time_group2,
                vax_time_group3 = df.jags$vax_time_group3,
                vax_time_group4 = df.jags$vax_time_group4,
                vax_time_group5 = df.jags$vax_time_group5,
                vax_time_group6 = df.jags$vax_time_group6,
                vax_time_group7 = df.jags$vax_time_group7,
                vax_time_group8 = df.jags$vax_time_group8,
                vax_time_group9 = df.jags$vax_time_group9,
                case_status = df.jags$case_control,
                # confounders
                cf_birth_weight = df.jags$birth_weight,
                cf_gestage = df.jags$risk_factor_gestagelessthan37wks,
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4
                )

source("jags_waning.R")

if(rerun){
  
  jags.post <- rjags::jags.model(textConnection(model_string_waning_biwkinterval), 
                          data = dataset_biwkinterval_RSVLRTI,
                          n.chains = 3)

  samples <- rjags::coda.samples(jags.post, 
                          variable.names=c("beta1", "beta2", "beta3", "beta4", "beta5", "beta6",
                                           "beta7", "beta8", "beta9"),
                          n.iter = 5000)
  saveRDS(samples, "../data/jags/post/wane_biwkinterval_RSVLRTI.rds")

}else{
  samples <- readRDS("../data/jags/post/wane_biwkinterval_RSVLRTI.rds")
}

post1 <- as.data.frame(as.matrix(samples[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples[[3]][-c(1:4500),])) 
post <- bind_rows(post1, post2, post3)

ve.median.1 <- round((1 - exp(median(post$beta1)))*100,1)
ve.lb.1 <- round((1 - exp(quantile(post$beta1, 0.975))) *100,1)
ve.ub.1 <- round((1 - exp(quantile(post$beta1, 0.025)))*100, 1)

ve.median.2 <- round((1 - exp(median(post$beta2)))*100,1)
ve.lb.2 <- round((1 - exp(quantile(post$beta2, 0.975))) *100,1)
ve.ub.2 <- round((1 - exp(quantile(post$beta2, 0.025)))*100, 1)

ve.median.3 <- round((1 - exp(median(post$beta3)))*100,1)
ve.lb.3 <- round((1 - exp(quantile(post$beta3, 0.975))) *100,1)
ve.ub.3 <- round((1 - exp(quantile(post$beta3, 0.025)))*100, 1)

ve.median.4 <- round((1 - exp(median(post$beta4)))*100,1)
ve.lb.4 <- round((1 - exp(quantile(post$beta4, 0.975))) *100,1)
ve.ub.4 <- round((1 - exp(quantile(post$beta4, 0.025)))*100, 1)

ve.median.5 <- round((1 - exp(median(post$beta5)))*100,1)
ve.lb.5 <- round((1 - exp(quantile(post$beta5, 0.975))) *100,1)
ve.ub.5 <- round((1 - exp(quantile(post$beta5, 0.025)))*100, 1)

ve.median.6 <- round((1 - exp(median(post$beta6)))*100,1)
ve.lb.6 <- round((1 - exp(quantile(post$beta6, 0.975))) *100,1)
ve.ub.6 <- round((1 - exp(quantile(post$beta6, 0.025)))*100, 1)

ve.median.7 <- round((1 - exp(median(post$beta7)))*100,1)
ve.lb.7 <- round((1 - exp(quantile(post$beta7, 0.975))) *100,1)
ve.ub.7 <- round((1 - exp(quantile(post$beta7, 0.025)))*100, 1)

ve.median.8 <- round((1 - exp(median(post$beta8)))*100,1)
ve.lb.8 <- round((1 - exp(quantile(post$beta8, 0.975))) *100,1)
ve.ub.8 <- round((1 - exp(quantile(post$beta8, 0.025)))*100, 1)

ve.median.9 <- round((1 - exp(median(post$beta9)))*100,1)
ve.lb.9 <- round((1 - exp(quantile(post$beta9, 0.975))) *100,1)
ve.ub.9 <- round((1 - exp(quantile(post$beta9, 0.025)))*100, 1)

# look at the result
ve.biwkinterval.RSVLRTI <- 
  data.frame(
  against = rep("RSV LRTI", 10),
  vax_time = c("not vaccinated",
               "(0, 2)",
               "[2, 4)",
               "[4, 6)",
               "[6, 8)",
               "[8, 10)",
               "[10, 12)",
               "[12, 14)",
               "[14, 16)",
               "[16, )"),
  VE.adjusted = c(
    "REF",
    paste0(ve.median.1, " (", ve.lb.1, "-", ve.ub.1, ")"),
    paste0(ve.median.2, " (", ve.lb.2, "-", ve.ub.2, ")"),
    paste0(ve.median.3, " (", ve.lb.3, "-", ve.ub.3, ")"),
    paste0(ve.median.4, " (", ve.lb.4, "-", ve.ub.4, ")"),
    paste0(ve.median.5, " (", ve.lb.5, "-", ve.ub.5, ")"),
    paste0(ve.median.6, " (", ve.lb.6, "-", ve.ub.6, ")"),
    paste0(ve.median.7, " (", ve.lb.7, "-", ve.ub.7, ")"),
    paste0(ve.median.8, " (", ve.lb.8, "-", ve.ub.8, ")"),
    paste0(ve.median.9, " (", ve.lb.9, "-", ve.ub.9, ")")
  )
) %>% 
  cbind(
    table(df.jags$weeks_btw_mab_collection_cat, df.jags$case_control) %>%
      matrix(ncol = 2)
  ) %>%
  dplyr::rename(n_cases = `2`, n_controls = `1`)
  
# for plotting 
df.ve.biwkinterval.RSVLRTI <- 
  data.frame(
  against = rep("RSV LRTI", 9),
  vax_time = c("(0, 2)",
               "[2, 4)",
               "[4, 6)",
               "[6, 8)",
               "[8, 10)",
               "[10, 12)",
               "[12, 14)",
               "[14, 16)",
               "[16, )"),
  VE.median = c(ve.median.1, ve.median.2, ve.median.3, ve.median.4, ve.median.5, ve.median.6,
                ve.median.7, ve.median.8, ve.median.9),
  VE.lb = c(ve.lb.1, ve.lb.2, ve.lb.3, ve.lb.4, ve.lb.5,
            ve.lb.6, ve.lb.7, ve.lb.8, ve.lb.9),
  VE.ub = c(ve.ub.1, ve.ub.2, ve.ub.3, ve.ub.4, ve.ub.5,
            ve.ub.6, ve.ub.7, ve.ub.8, ve.ub.9)
  )


###################################
# Against RSV outpatient visit
###################################
# prepare the input dataset for jags 
df.jags <- df %>% 
  filter(encounter_type == "outpatient") %>%
  mutate(case_control = positive_rsv) 

# # include birth weight and gestage<37wks as confounders 
# df.jags <- df.jags %>%
#   filter(!is.na(cf_birth_weight) & !is.na(risk_factor_gestagelessthan37wks))
  

dataset_biwkinterval_RSVoutpatient <- 
            list(
                N_records = nrow(df.jags),
                vax = df.jags$rsv_mab,
                vax_time_group1 = df.jags$vax_time_group1,
                vax_time_group2 = df.jags$vax_time_group2,
                vax_time_group3 = df.jags$vax_time_group3,
                vax_time_group4 = df.jags$vax_time_group4,
                vax_time_group5 = df.jags$vax_time_group5,
                vax_time_group6 = df.jags$vax_time_group6,
                vax_time_group7 = df.jags$vax_time_group7,
                vax_time_group8 = df.jags$vax_time_group8,
                vax_time_group9 = df.jags$vax_time_group9,
                case_status = df.jags$case_control,
                # confounders
                cf_birth_weight = df.jags$birth_weight,
                cf_gestage = df.jags$risk_factor_gestagelessthan37wks,
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4
                )

source("jags_waning.R")

if(rerun){
  
  jags.post <- rjags::jags.model(textConnection(model_string_waning_biwkinterval), 
                          data = dataset_biwkinterval_RSVoutpatient,
                          n.chains = 3)

  samples <- rjags::coda.samples(jags.post, 
                          variable.names=c("beta1", "beta2", "beta3", "beta4", "beta5", "beta6",
                                           "beta7", "beta8", "beta9"),
                          n.iter = 5000)
  saveRDS(samples, "../data/jags/post/wane_biwkinterval_RSVoutpatient.rds")

}else{
  samples <- readRDS("../data/jags/post/wane_biwkinterval_RSVoutpatient.rds")
}

post1 <- as.data.frame(as.matrix(samples[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples[[3]][-c(1:4500),])) 
post <- bind_rows(post1, post2, post3)

ve.median.1 <- round((1 - exp(median(post$beta1)))*100,1)
ve.lb.1 <- round((1 - exp(quantile(post$beta1, 0.975))) *100,1)
ve.ub.1 <- round((1 - exp(quantile(post$beta1, 0.025)))*100, 1)

ve.median.2 <- round((1 - exp(median(post$beta2)))*100,1)
ve.lb.2 <- round((1 - exp(quantile(post$beta2, 0.975))) *100,1)
ve.ub.2 <- round((1 - exp(quantile(post$beta2, 0.025)))*100, 1)

ve.median.3 <- round((1 - exp(median(post$beta3)))*100,1)
ve.lb.3 <- round((1 - exp(quantile(post$beta3, 0.975))) *100,1)
ve.ub.3 <- round((1 - exp(quantile(post$beta3, 0.025)))*100, 1)

ve.median.4 <- round((1 - exp(median(post$beta4)))*100,1)
ve.lb.4 <- round((1 - exp(quantile(post$beta4, 0.975))) *100,1)
ve.ub.4 <- round((1 - exp(quantile(post$beta4, 0.025)))*100, 1)

ve.median.5 <- round((1 - exp(median(post$beta5)))*100,1)
ve.lb.5 <- round((1 - exp(quantile(post$beta5, 0.975))) *100,1)
ve.ub.5 <- round((1 - exp(quantile(post$beta5, 0.025)))*100, 1)

ve.median.6 <- round((1 - exp(median(post$beta6)))*100,1)
ve.lb.6 <- round((1 - exp(quantile(post$beta6, 0.975))) *100,1)
ve.ub.6 <- round((1 - exp(quantile(post$beta6, 0.025)))*100, 1)

ve.median.7 <- round((1 - exp(median(post$beta7)))*100,1)
ve.lb.7 <- round((1 - exp(quantile(post$beta7, 0.975))) *100,1)
ve.ub.7 <- round((1 - exp(quantile(post$beta7, 0.025)))*100, 1)

ve.median.8 <- round((1 - exp(median(post$beta8)))*100,1)
ve.lb.8 <- round((1 - exp(quantile(post$beta8, 0.975))) *100,1)
ve.ub.8 <- round((1 - exp(quantile(post$beta8, 0.025)))*100, 1)

ve.median.9 <- round((1 - exp(median(post$beta9)))*100,1)
ve.lb.9 <- round((1 - exp(quantile(post$beta9, 0.975))) *100,1)
ve.ub.9 <- round((1 - exp(quantile(post$beta9, 0.025)))*100, 1)

# look at the result
ve.biwkinterval.RSVoutpatient <- 
  data.frame(
  against = rep("RSV outpatient visit", 10),
  vax_time = c("not vaccinated",
               "(0, 2)",
               "[2, 4)",
               "[4, 6)",
               "[6, 8)",
               "[8, 10)",
               "[10, 12)",
               "[12, 14)",
               "[14, 16)",
               "[16, )"),
  VE.adjusted = c(
    "REF",
    paste0(ve.median.1, " (", ve.lb.1, "-", ve.ub.1, ")"),
    paste0(ve.median.2, " (", ve.lb.2, "-", ve.ub.2, ")"),
    paste0(ve.median.3, " (", ve.lb.3, "-", ve.ub.3, ")"),
    paste0(ve.median.4, " (", ve.lb.4, "-", ve.ub.4, ")"),
    paste0(ve.median.5, " (", ve.lb.5, "-", ve.ub.5, ")"),
    paste0(ve.median.6, " (", ve.lb.6, "-", ve.ub.6, ")"),
    paste0(ve.median.7, " (", ve.lb.7, "-", ve.ub.7, ")"),
    paste0(ve.median.8, " (", ve.lb.8, "-", ve.ub.8, ")"),
    paste0(ve.median.9, " (", ve.lb.9, "-", ve.ub.9, ")")
  )
) %>% 
  cbind(
    table(df.jags$weeks_btw_mab_collection_cat, df.jags$case_control) %>%
      matrix(ncol = 2)
  ) %>%
  dplyr::rename(n_cases = `2`, n_controls = `1`)
  
# for plotting 
df.ve.biwkinterval.RSVoutpatient <- 
  data.frame(
  against = rep("RSV outpatient visit", 9),
  vax_time = c("(0, 2)",
               "[2, 4)",
               "[4, 6)",
               "[6, 8)",
               "[8, 10)",
               "[10, 12)",
               "[12, 14)",
               "[14, 16)",
               "[16, )"),
  VE.median = c(ve.median.1, ve.median.2, ve.median.3, ve.median.4, ve.median.5, ve.median.6,
                ve.median.7, ve.median.8, ve.median.9),
  VE.lb = c(ve.lb.1, ve.lb.2, ve.lb.3, ve.lb.4, ve.lb.5,
            ve.lb.6, ve.lb.7, ve.lb.8, ve.lb.9),
  VE.ub = c(ve.ub.1, ve.ub.2, ve.ub.3, ve.ub.4, ve.ub.5,
            ve.ub.6, ve.ub.7, ve.ub.8, ve.ub.9)
  )

###################################
# Against RSV hosp
###################################

# prepare the input dataset for jags 
df.jags <- df %>% 
  filter(encounter_type == "inpatient") %>%
  mutate(case_control = positive_rsv) 

# # include birth weight and gestage<37wks as confounders 
# df.jags <- df.jags %>%
#   filter(!is.na(cf_birth_weight) & !is.na(risk_factor_gestagelessthan37wks))
  

dataset_biwkinterval_RSVhosp <- 
            list(
                N_records = nrow(df.jags),
                vax = df.jags$rsv_mab,
                vax_time_group1 = df.jags$vax_time_group1,
                vax_time_group2 = df.jags$vax_time_group2,
                vax_time_group3 = df.jags$vax_time_group3,
                vax_time_group4 = df.jags$vax_time_group4,
                vax_time_group5 = df.jags$vax_time_group5,
                vax_time_group6 = df.jags$vax_time_group6,
                vax_time_group7 = df.jags$vax_time_group7,
                vax_time_group8 = df.jags$vax_time_group8,
                vax_time_group9 = df.jags$vax_time_group9,
                case_status = df.jags$case_control,
                # confounders
                cf_birth_weight = df.jags$birth_weight,
                cf_gestage = df.jags$risk_factor_gestagelessthan37wks,
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4
                )

source("jags_waning.R")

if(rerun){
  
  jags.post <- rjags::jags.model(textConnection(model_string_waning_biwkinterval), 
                          data = dataset_biwkinterval_RSVhosp,
                          n.chains = 3)

  samples <- rjags::coda.samples(jags.post, 
                          variable.names=c("beta1", "beta2", "beta3", "beta4", "beta5", "beta6",
                                           "beta7", "beta8", "beta9"),
                          n.iter = 5000)
  saveRDS(samples, "../data/jags/post/wane_biwkinterval_RSVhosp.rds")

}else{
  samples <- readRDS("../data/jags/post/wane_biwkinterval_RSVhosp.rds")
}

post1 <- as.data.frame(as.matrix(samples[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples[[3]][-c(1:4500),])) 
post <- bind_rows(post1, post2, post3)

ve.median.1 <- round((1 - exp(median(post$beta1)))*100,1)
ve.lb.1 <- round((1 - exp(quantile(post$beta1, 0.975))) *100,1)
ve.ub.1 <- round((1 - exp(quantile(post$beta1, 0.025)))*100, 1)

ve.median.2 <- round((1 - exp(median(post$beta2)))*100,1)
ve.lb.2 <- round((1 - exp(quantile(post$beta2, 0.975))) *100,1)
ve.ub.2 <- round((1 - exp(quantile(post$beta2, 0.025)))*100, 1)

ve.median.3 <- round((1 - exp(median(post$beta3)))*100,1)
ve.lb.3 <- round((1 - exp(quantile(post$beta3, 0.975))) *100,1)
ve.ub.3 <- round((1 - exp(quantile(post$beta3, 0.025)))*100, 1)

ve.median.4 <- round((1 - exp(median(post$beta4)))*100,1)
ve.lb.4 <- round((1 - exp(quantile(post$beta4, 0.975))) *100,1)
ve.ub.4 <- round((1 - exp(quantile(post$beta4, 0.025)))*100, 1)

ve.median.5 <- round((1 - exp(median(post$beta5)))*100,1)
ve.lb.5 <- round((1 - exp(quantile(post$beta5, 0.975))) *100,1)
ve.ub.5 <- round((1 - exp(quantile(post$beta5, 0.025)))*100, 1)

ve.median.6 <- round((1 - exp(median(post$beta6)))*100,1)
ve.lb.6 <- round((1 - exp(quantile(post$beta6, 0.975))) *100,1)
ve.ub.6 <- round((1 - exp(quantile(post$beta6, 0.025)))*100, 1)

ve.median.7 <- round((1 - exp(median(post$beta7)))*100,1)
ve.lb.7 <- round((1 - exp(quantile(post$beta7, 0.975))) *100,1)
ve.ub.7 <- round((1 - exp(quantile(post$beta7, 0.025)))*100, 1)

ve.median.8 <- round((1 - exp(median(post$beta8)))*100,1)
ve.lb.8 <- round((1 - exp(quantile(post$beta8, 0.975))) *100,1)
ve.ub.8 <- round((1 - exp(quantile(post$beta8, 0.025)))*100, 1)

ve.median.9 <- round((1 - exp(median(post$beta9)))*100,1)
ve.lb.9 <- round((1 - exp(quantile(post$beta9, 0.975))) *100,1)
ve.ub.9 <- round((1 - exp(quantile(post$beta9, 0.025)))*100, 1)

# look at the result
ve.biwkinterval.RSVhosp <- 
  data.frame(
  against = rep("RSV hospitalization", 10),
  vax_time = c("not vaccinated",
               "(0, 2)",
               "[2, 4)",
               "[4, 6)",
               "[6, 8)",
               "[8, 10)",
               "[10, 12)",
               "[12, 14)",
               "[14, 16)",
               "[16, )"),
  VE.adjusted = c(
    "REF",
    paste0(ve.median.1, " (", ve.lb.1, "-", ve.ub.1, ")"),
    paste0(ve.median.2, " (", ve.lb.2, "-", ve.ub.2, ")"),
    paste0(ve.median.3, " (", ve.lb.3, "-", ve.ub.3, ")"),
    paste0(ve.median.4, " (", ve.lb.4, "-", ve.ub.4, ")"),
    paste0(ve.median.5, " (", ve.lb.5, "-", ve.ub.5, ")"),
    paste0(ve.median.6, " (", ve.lb.6, "-", ve.ub.6, ")"),
    paste0(ve.median.7, " (", ve.lb.7, "-", ve.ub.7, ")"),
    paste0(ve.median.8, " (", ve.lb.8, "-", ve.ub.8, ")"),
    paste0(ve.median.9, " (", ve.lb.9, "-", ve.ub.9, ")")
  )
) %>% 
  cbind(
    table(df.jags$weeks_btw_mab_collection_cat, df.jags$case_control) %>%
      matrix(ncol = 2)
  ) %>%
  dplyr::rename(n_cases = `2`, n_controls = `1`)
  
# for plotting 
df.ve.biwkinterval.RSVhosp <- 
  data.frame(
  against = rep("RSV hospitalization", 9),
  vax_time = c("(0, 2)",
               "[2, 4)",
               "[4, 6)",
               "[6, 8)",
               "[8, 10)",
               "[10, 12)",
               "[12, 14)",
               "[14, 16)",
               "[16, )"),
  VE.median = c(ve.median.1, ve.median.2, ve.median.3, ve.median.4, ve.median.5, ve.median.6,
                ve.median.7, ve.median.8, ve.median.9),
  VE.lb = c(ve.lb.1, ve.lb.2, ve.lb.3, ve.lb.4, ve.lb.5,
            ve.lb.6, ve.lb.7, ve.lb.8, ve.lb.9),
  VE.ub = c(ve.ub.1, ve.ub.2, ve.ub.3, ve.ub.4, ve.ub.5,
            ve.ub.6, ve.ub.7, ve.ub.8, ve.ub.9)
  )

###################################
# Against RSV LRTI hosp
###################################
# prepare the input dataset for jags 
df.jags <- df %>% 
  filter(symp_LRT_distress == 1 & encounter_type == "inpatient") %>%
  mutate(case_control = positive_rsv) 

# # include birth weight and gestage<37wks as confounders 
# df.jags <- df.jags %>%
#   filter(!is.na(cf_birth_weight) & !is.na(risk_factor_gestagelessthan37wks))
  

dataset_biwkinterval_RSVLRTIhosp <- 
            list(
                N_records = nrow(df.jags),
                vax = df.jags$rsv_mab,
                vax_time_group1 = df.jags$vax_time_group1,
                vax_time_group2 = df.jags$vax_time_group2,
                vax_time_group3 = df.jags$vax_time_group3,
                vax_time_group4 = df.jags$vax_time_group4,
                vax_time_group5 = df.jags$vax_time_group5,
                vax_time_group6 = df.jags$vax_time_group6,
                vax_time_group7 = df.jags$vax_time_group7,
                vax_time_group8 = df.jags$vax_time_group8,
                vax_time_group9 = df.jags$vax_time_group9,
                case_status = df.jags$case_control,
                # confounders
                cf_birth_weight = df.jags$birth_weight,
                cf_gestage = df.jags$risk_factor_gestagelessthan37wks,
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4
                )

source("jags_waning.R")

if(rerun){
  
  jags.post <- rjags::jags.model(textConnection(model_string_waning_biwkinterval), 
                          data = dataset_biwkinterval_RSVLRTIhosp,
                          n.chains = 3)

  samples <- rjags::coda.samples(jags.post, 
                          variable.names=c("beta1", "beta2", "beta3", "beta4", "beta5", "beta6",
                                           "beta7", "beta8", "beta9"),
                          n.iter = 5000)
  saveRDS(samples, "../data/jags/post/wane_biwkinterval_RSVLRTIhosp.rds")

}else{
  samples <- readRDS("../data/jags/post/wane_biwkinterval_RSVLRTIhosp.rds")
}

post1 <- as.data.frame(as.matrix(samples[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples[[3]][-c(1:4500),])) 
post <- bind_rows(post1, post2, post3)

ve.median.1 <- round((1 - exp(median(post$beta1)))*100,1)
ve.lb.1 <- round((1 - exp(quantile(post$beta1, 0.975))) *100,1)
ve.ub.1 <- round((1 - exp(quantile(post$beta1, 0.025)))*100, 1)

ve.median.2 <- round((1 - exp(median(post$beta2)))*100,1)
ve.lb.2 <- round((1 - exp(quantile(post$beta2, 0.975))) *100,1)
ve.ub.2 <- round((1 - exp(quantile(post$beta2, 0.025)))*100, 1)

ve.median.3 <- round((1 - exp(median(post$beta3)))*100,1)
ve.lb.3 <- round((1 - exp(quantile(post$beta3, 0.975))) *100,1)
ve.ub.3 <- round((1 - exp(quantile(post$beta3, 0.025)))*100, 1)

ve.median.4 <- round((1 - exp(median(post$beta4)))*100,1)
ve.lb.4 <- round((1 - exp(quantile(post$beta4, 0.975))) *100,1)
ve.ub.4 <- round((1 - exp(quantile(post$beta4, 0.025)))*100, 1)

ve.median.5 <- round((1 - exp(median(post$beta5)))*100,1)
ve.lb.5 <- round((1 - exp(quantile(post$beta5, 0.975))) *100,1)
ve.ub.5 <- round((1 - exp(quantile(post$beta5, 0.025)))*100, 1)

ve.median.6 <- round((1 - exp(median(post$beta6)))*100,1)
ve.lb.6 <- round((1 - exp(quantile(post$beta6, 0.975))) *100,1)
ve.ub.6 <- round((1 - exp(quantile(post$beta6, 0.025)))*100, 1)

ve.median.7 <- round((1 - exp(median(post$beta7)))*100,1)
ve.lb.7 <- round((1 - exp(quantile(post$beta7, 0.975))) *100,1)
ve.ub.7 <- round((1 - exp(quantile(post$beta7, 0.025)))*100, 1)

ve.median.8 <- round((1 - exp(median(post$beta8)))*100,1)
ve.lb.8 <- round((1 - exp(quantile(post$beta8, 0.975))) *100,1)
ve.ub.8 <- round((1 - exp(quantile(post$beta8, 0.025)))*100, 1)

ve.median.9 <- round((1 - exp(median(post$beta9)))*100,1)
ve.lb.9 <- round((1 - exp(quantile(post$beta9, 0.975))) *100,1)
ve.ub.9 <- round((1 - exp(quantile(post$beta9, 0.025)))*100, 1)

# look at the result
ve.biwkinterval.RSVLRTIhosp <- 
  data.frame(
  against = rep("RSV LRTI hospitalization", 10),
  vax_time = c("not vaccinated",
               "(0, 2)",
               "[2, 4)",
               "[4, 6)",
               "[6, 8)",
               "[8, 10)",
               "[10, 12)",
               "[12, 14)",
               "[14, 16)",
               "[16, )"),
  VE.adjusted = c(
    "REF",
    paste0(ve.median.1, " (", ve.lb.1, "-", ve.ub.1, ")"),
    paste0(ve.median.2, " (", ve.lb.2, "-", ve.ub.2, ")"),
    paste0(ve.median.3, " (", ve.lb.3, "-", ve.ub.3, ")"),
    paste0(ve.median.4, " (", ve.lb.4, "-", ve.ub.4, ")"),
    paste0(ve.median.5, " (", ve.lb.5, "-", ve.ub.5, ")"),
    paste0(ve.median.6, " (", ve.lb.6, "-", ve.ub.6, ")"),
    paste0(ve.median.7, " (", ve.lb.7, "-", ve.ub.7, ")"),
    paste0(ve.median.8, " (", ve.lb.8, "-", ve.ub.8, ")"),
    paste0(ve.median.9, " (", ve.lb.9, "-", ve.ub.9, ")")
  )
) %>% 
  cbind(
    table(df.jags$weeks_btw_mab_collection_cat, df.jags$case_control) %>%
      matrix(ncol = 2)
  ) %>%
  dplyr::rename(n_cases = `2`, n_controls = `1`)
  
# for plotting 
df.ve.biwkinterval.RSVLRTIhosp<- 
  data.frame(
  against = rep("RSV LRTI hospitalization", 9),
  vax_time = c("(0, 2)",
               "[2, 4)",
               "[4, 6)",
               "[6, 8)",
               "[8, 10)",
               "[10, 12)",
               "[12, 14)",
               "[14, 16)",
               "[16, )"),
  VE.median = c(ve.median.1, ve.median.2, ve.median.3, ve.median.4, ve.median.5, ve.median.6,
                ve.median.7, ve.median.8, ve.median.9),
  VE.lb = c(ve.lb.1, ve.lb.2, ve.lb.3, ve.lb.4, ve.lb.5,
            ve.lb.6, ve.lb.7, ve.lb.8, ve.lb.9),
  VE.ub = c(ve.ub.1, ve.ub.2, ve.ub.3, ve.ub.4, ve.ub.5,
            ve.ub.6, ve.ub.7, ve.ub.8, ve.ub.9)
  )

###################################
# Against RSV severe outcomes
###################################
# prepare the input dataset for jags 
df.jags <- df %>% 
  filter(icu_admitted == "yes" | highflow_oxygen == 1) %>%
  mutate(case_control = positive_rsv) 

# # include birth weight and gestage<37wks as confounders 
# df.jags <- df.jags %>%
#   filter(!is.na(cf_birth_weight) & !is.na(risk_factor_gestagelessthan37wks))
  

dataset_biwkinterval_RSVsevere <- 
            list(
                N_records = nrow(df.jags),
                vax = df.jags$rsv_mab,
                vax_time_group1 = df.jags$vax_time_group1,
                vax_time_group2 = df.jags$vax_time_group2,
                vax_time_group3 = df.jags$vax_time_group3,
                vax_time_group4 = df.jags$vax_time_group4,
                vax_time_group5 = df.jags$vax_time_group5,
                vax_time_group6 = df.jags$vax_time_group6,
                vax_time_group7 = df.jags$vax_time_group7,
                vax_time_group8 = df.jags$vax_time_group8,
                vax_time_group9 = df.jags$vax_time_group9,
                case_status = df.jags$case_control,
                # confounders
                cf_birth_weight = df.jags$birth_weight,
                cf_gestage = df.jags$risk_factor_gestagelessthan37wks,
                cf_age_1 = df.jags$cf_age_1, # age when tested
                cf_age_2 = df.jags$cf_age_2,
                cf_age_3 = df.jags$cf_age_3,
                cf_age_4 = df.jags$cf_age_4,
                cf_age_5 = df.jags$cf_age_5,
                cf_month_tested_1 = df.jags$cf_month_tested_1, # month when tested
                cf_month_tested_2 = df.jags$cf_month_tested_2,
                cf_month_tested_3 = df.jags$cf_month_tested_3,
                cf_month_tested_4 = df.jags$cf_month_tested_4
                )

source("jags_waning.R")

if(rerun){
  
  jags.post <- rjags::jags.model(textConnection(model_string_waning_biwkinterval), 
                          data = dataset_biwkinterval_RSVsevere,
                          n.chains = 3)

  samples <- rjags::coda.samples(jags.post, 
                          variable.names=c("beta1", "beta2", "beta3", "beta4", "beta5", "beta6",
                                           "beta7", "beta8", "beta9"),
                          n.iter = 5000)
  saveRDS(samples, "../data/jags/post/wane_biwkinterval_RSVsevere.rds")

}else{
  samples <- readRDS("../data/jags/post/wane_biwkinterval_RSVsevere.rds")
}

post1 <- as.data.frame(as.matrix(samples[[1]][-c(1:4500),]))  
post2 <- as.data.frame(as.matrix(samples[[2]][-c(1:4500),])) 
post3 <- as.data.frame(as.matrix(samples[[3]][-c(1:4500),])) 
post <- bind_rows(post1, post2, post3)

ve.median.1 <- round((1 - exp(median(post$beta1)))*100,1)
ve.lb.1 <- round((1 - exp(quantile(post$beta1, 0.975))) *100,1)
ve.ub.1 <- round((1 - exp(quantile(post$beta1, 0.025)))*100, 1)

ve.median.2 <- round((1 - exp(median(post$beta2)))*100,1)
ve.lb.2 <- round((1 - exp(quantile(post$beta2, 0.975))) *100,1)
ve.ub.2 <- round((1 - exp(quantile(post$beta2, 0.025)))*100, 1)

ve.median.3 <- round((1 - exp(median(post$beta3)))*100,1)
ve.lb.3 <- round((1 - exp(quantile(post$beta3, 0.975))) *100,1)
ve.ub.3 <- round((1 - exp(quantile(post$beta3, 0.025)))*100, 1)

ve.median.4 <- round((1 - exp(median(post$beta4)))*100,1)
ve.lb.4 <- round((1 - exp(quantile(post$beta4, 0.975))) *100,1)
ve.ub.4 <- round((1 - exp(quantile(post$beta4, 0.025)))*100, 1)

ve.median.5 <- round((1 - exp(median(post$beta5)))*100,1)
ve.lb.5 <- round((1 - exp(quantile(post$beta5, 0.975))) *100,1)
ve.ub.5 <- round((1 - exp(quantile(post$beta5, 0.025)))*100, 1)

ve.median.6 <- round((1 - exp(median(post$beta6)))*100,1)
ve.lb.6 <- round((1 - exp(quantile(post$beta6, 0.975))) *100,1)
ve.ub.6 <- round((1 - exp(quantile(post$beta6, 0.025)))*100, 1)

ve.median.7 <- round((1 - exp(median(post$beta7)))*100,1)
ve.lb.7 <- round((1 - exp(quantile(post$beta7, 0.975))) *100,1)
ve.ub.7 <- round((1 - exp(quantile(post$beta7, 0.025)))*100, 1)

ve.median.8 <- round((1 - exp(median(post$beta8)))*100,1)
ve.lb.8 <- round((1 - exp(quantile(post$beta8, 0.975))) *100,1)
ve.ub.8 <- round((1 - exp(quantile(post$beta8, 0.025)))*100, 1)

ve.median.9 <- round((1 - exp(median(post$beta9)))*100,1)
ve.lb.9 <- round((1 - exp(quantile(post$beta9, 0.975))) *100,1)
ve.ub.9 <- round((1 - exp(quantile(post$beta9, 0.025)))*100, 1)

# look at the result
ve.biwkinterval.RSVsevere <- 
  data.frame(
  against = rep("RSV severe outcomes", 10),
  vax_time = c("not vaccinated",
               "(0, 2)",
               "[2, 4)",
               "[4, 6)",
               "[6, 8)",
               "[8, 10)",
               "[10, 12)",
               "[12, 14)",
               "[14, 16)",
               "[16, )"),
  VE.adjusted = c(
    "REF",
    paste0(ve.median.1, " (", ve.lb.1, "-", ve.ub.1, ")"),
    paste0(ve.median.2, " (", ve.lb.2, "-", ve.ub.2, ")"),
    paste0(ve.median.3, " (", ve.lb.3, "-", ve.ub.3, ")"),
    paste0(ve.median.4, " (", ve.lb.4, "-", ve.ub.4, ")"),
    paste0(ve.median.5, " (", ve.lb.5, "-", ve.ub.5, ")"),
    paste0(ve.median.6, " (", ve.lb.6, "-", ve.ub.6, ")"),
    paste0(ve.median.7, " (", ve.lb.7, "-", ve.ub.7, ")"),
    paste0(ve.median.8, " (", ve.lb.8, "-", ve.ub.8, ")"),
    paste0(ve.median.9, " (", ve.lb.9, "-", ve.ub.9, ")")
  )
) %>% 
  cbind(
    table(df.jags$weeks_btw_mab_collection_cat, df.jags$case_control) %>%
      matrix(ncol = 2)
  ) %>%
  dplyr::rename(n_cases = `2`, n_controls = `1`)
  
# for plotting 
df.ve.biwkinterval.RSVsevere <- 
  data.frame(
  against = rep("RSV severe outcomes", 9),
  vax_time = c("(0, 2)",
               "[2, 4)",
               "[4, 6)",
               "[6, 8)",
               "[8, 10)",
               "[10, 12)",
               "[12, 14)",
               "[14, 16)",
               "[16, )"),
  VE.median = c(ve.median.1, ve.median.2, ve.median.3, ve.median.4, ve.median.5, ve.median.6,
                ve.median.7, ve.median.8, ve.median.9),
  VE.lb = c(ve.lb.1, ve.lb.2, ve.lb.3, ve.lb.4, ve.lb.5,
            ve.lb.6, ve.lb.7, ve.lb.8, ve.lb.9),
  VE.ub = c(ve.ub.1, ve.ub.2, ve.ub.3, ve.ub.4, ve.ub.5,
            ve.ub.6, ve.ub.7, ve.ub.8, ve.ub.9)
  )

  

# look at all the results with 1-month interval
ve.biwkinterval.infection %>%
  rbind(ve.biwkinterval.RSVoutpatient, 
        ve.biwkinterval.RSVhosp,
        ve.biwkinterval.RSVLRTI, 
        ve.biwkinterval.RSVLRTIhosp,
        ve.biwkinterval.RSVsevere) %>% 
  dplyr::rename(weeks_since_vax = vax_time) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T, groupBy = "against") 

# save the data table 
tab.ve.wane.biwk <- 
  ve.biwkinterval.infection %>%
  rbind(ve.biwkinterval.RSVoutpatient, 
        ve.biwkinterval.RSVhosp,
        ve.biwkinterval.RSVLRTI, 
        ve.biwkinterval.RSVLRTIhosp,
        ve.biwkinterval.RSVsevere) %>%
  dplyr::select(against, vax_time, n_cases, n_controls, VE.adjusted) %>%
  flextable() %>%
  set_header_labels(against = "Outcome prevented",
                    vax_time = "Time since vaccination (weeks)",
                    n_cases = "RSV positive",
                    n_controls = "RSV negative",
                    VE.adjusted = "Adjusted VE (95% CI)"
                    ) %>%
  merge_at(i = 1:10, j = 1) %>%
  merge_at(i = 11:20, j = 1) %>%
  merge_at(i = 21:30, j = 1) %>%
  merge_at(i = 31:40, j = 1) %>%
  merge_at(i = 41:50, j = 1) %>%
  merge_at(i = 51:60, j = 1) %>%
  width(j = c(1,2,5), width = 2) %>%
  vline() %>%
  hline()

if(savenewplot){
  save_as_docx(tab.ve.wane.biwk, path = "../figs_tabs/tables/jags.wane.biwk.docx")
}
  
```

#### one outcome per panel

```{r fig.width = 12, fig.height = 8}
df.plt.wane.biwk <- 
  df.ve.biwkinterval.infection %>%
  rbind(df.ve.biwkinterval.RSVoutpatient, 
        df.ve.biwkinterval.RSVhosp,
        df.ve.biwkinterval.RSVLRTI, 
        df.ve.biwkinterval.RSVLRTIhosp,
        df.ve.biwkinterval.RSVsevere) %>%
  mutate(time_since_vax = case_when(
    vax_time == "(0, 2)" ~ "2",
    vax_time == "[2, 4)" ~ "4",
    vax_time == "[4, 6)" ~ "6",
    vax_time == "[6, 8)" ~ "8",
    vax_time == "[8, 10)" ~ "10",
    vax_time == "[10, 12)" ~ "12",
    vax_time == "[12, 14)" ~ "14",
    vax_time == "[14, 16)" ~ "16",
    vax_time == "[16, )" ~ "16+"
  )) %>%
  mutate(VE = paste0(round(VE.median), " (", round(VE.lb), ", ", round(VE.ub), ")")) %>% 
  # mutate(time_since_vax = factor(time_since_vax, levels = c("(0, 2)", "[2, 4)", "[4, 6)", "[6, 8)",
  #                                                           "[8, 10)", "[10, 12)", "[12, 14)", "[14, 16)", "[16, )"))) %>% 
  mutate(time_since_vax = factor(time_since_vax, levels = c("2", "4", "6", "8",
                                                            "10", "12", "14", "16", "16+"))) %>% 
  mutate(against = paste0("Against ", against)) %>%
  mutate(against = factor(against, levels = c("Against RSV infection",
                                              "Against RSV outpatient visit",
                                              "Against RSV hospitalization",
                                              "Against RSV LRTI",
                                              "Against RSV LRTI hospitalization",
                                              "Against RSV severe outcomes")))

df.no.arrow <- 
  df.plt.wane.biwk %>%
  mutate(add_arrow = ifelse(VE.lb <= -25, 1, 0)) %>%
  mutate(VE.lb = ifelse(add_arrow == 1, -25, VE.lb)) %>% 
  mutate(across(starts_with("VE"), ~ ifelse(add_arrow == 1, NA, .)))

df.add.arrow <- 
  df.plt.wane.biwk %>%
  mutate(add_arrow = ifelse(VE.lb <= -25, 1, 0)) %>%
  mutate(VE.lb = ifelse(add_arrow == 1, -25, VE.lb)) %>% 
  mutate(across(starts_with("VE"), ~ ifelse(add_arrow != 1, NA, .)))



plt.jags.wane.biwk <- 
  ggplot() +
  # if lb > -25
  geom_point(aes(x = time_since_vax, y = VE.median), 
             position = position_dodge(0.5), data = df.no.arrow) +
  geom_errorbar(aes(x = time_since_vax, ymin = VE.lb, ymax = VE.ub), 
                width = 0, position = position_dodge(0.5), data = df.no.arrow) +
  geom_text(aes(x = time_since_vax, y = VE.median-10, label = VE), 
            angle = 90, position = position_dodge(0.5), vjust = - 0.7, show_guide = F,
            size = 4.3, data = df.no.arrow) +
  # if lb < -25
  geom_point(aes(x = time_since_vax, y = VE.median), 
             position = position_dodge(0.5), data = df.add.arrow) +
  geom_segment(aes(x = time_since_vax, xend = time_since_vax, 
                   y = VE.ub, yend = VE.lb),
               arrow = arrow(length = unit(2, "mm")),
               position = position_dodge(0.5),
               data = df.add.arrow, show_guide = F) +
  geom_text(aes(x = time_since_vax, y = VE.median-10, label = VE), 
            angle = 90, position = position_dodge(0.5), vjust = - 0.7, show_guide = F,
            size = 4.3, data = df.add.arrow) +
  theme_classic() +
  scale_color_brewer(palette = "Dark2") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  ylab("Effectiveness of Nirsevimab (%)") +
  xlab("Time since vaccination (weeks)") +
  labs(color = "Clinical endpoint") +
  ylim(c(-25,100)) +
  scale_y_continuous(breaks = c(-25, 0, 25, 50, 75, 100),
                     labels = c("-25", "0", "25", "50", "75", "100")) +
  facet_wrap( ~ against) +
   theme(
    #panel.grid.major = element_line(color = "grey", linewidth = 0.1), 
    #panel.grid.minor = element_blank(),
    axis.text.x = element_text(size = 12),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    strip.text.x = element_text(size = 12), 
        strip.text.y = element_text(size = 11)
     )
        

plt.jags.wane.biwk

if(savenewplot){
  ggsave(plot = plt.jags.wane.biwk, filename = "../figs_tabs/figures/jags.wane.biwk.pdf", height = 8, width = 12)
}

```









