---
title: "VE of Nirsevimab"
output: 
  html_document:
    toc: true
    toc_float: true
---

#### Date: `r Sys.Date()`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

library(dplyr)
library(tidyr)
library(tidyverse)
library(readxl)
library(writexl)
library(reactable)
library(ggplot2)
library(stringr)
library(flextable)
library(lubridate)


library(gtsummary) # for table 1
library(multcomp)
library(survival) # for matched case-control

fig.counter <- 1
tab.counter <- 1
```


```{r}
# read in dataset
df <- read.csv("../data/clean_data/df.mab.csv") %>% mutate(collection_date = as.Date(collection_date))
colnames <- as.data.frame(colnames(df))

source("utils_mAb_VE.R")
```


```{r}
# add some variables 

# month when tested
df <- df %>% 
  mutate(month_when_tested = as.character(month(collection_date, label = T))) %>% 
  mutate(month_when_tested = ifelse(month_when_tested == "Sep", "Oct", month_when_tested)) %>%
  mutate(age_at_test_in_months_cat = case_when(
    age_at_test_in_months < 6 ~ "under 6m",
    age_at_test_in_months >= 6 & age_at_test_in_months < 12 ~ "6-12m",
    age_at_test_in_months >= 12 ~ "above 1 yo" 
  )) %>%
  mutate(risk_factor_atleastone = case_when(risk_factor_atleastone == 1 ~ "yes",
                                            risk_factor_atleastone == 0 ~ "no"))

```


### There are totally `r nrow(df)` testing records in the analysis dataset. 

<br>

### Table `r tab.counter`. Study population (testing level)
  * (TBC) where should we include the "unrelated" hospital admissions and ICU admissions? count them as "outpatient"/"no ICU admission"? (currently doing this, but doesn't really make sense..)
  * this is assuming that: if mAb was taken before collection date, we count it as immunized. For SSA, need to change it to: if the person took mAb more than 5 days before sample collection, we count it as immunized.
  * Here, cases are RSV+, and controls are RSV-.

```{r}
tab.counter <- tab.counter + 1

df_table1 <- df %>%
  # add dose of mab 
  mutate(rsv_mab = case_when(rsv_mab_detailed == "100mg before collection" ~ "Yes, 100mg dose",
                             rsv_mab_detailed == "50mg before collection" ~ "Yes, 50mg dose",
                             TRUE ~ "No")) %>%
  dplyr::select(positive_rsv,Sex, age_at_test_in_months, race_ethnicity, encounter_type, risk_factor_gestage, insurance_type, rsv_mab, risk_factor_atleastone, icu_admitted, month_when_tested) %>% 
  mutate(positive_rsv = case_when(positive_rsv == 1 ~ "Cases (RSV+)",
                                  positive_rsv == 0 ~ "Controls (RSV-)")) %>%
  # count "unrelated" hosp and ICU admissions as "no"
  mutate(encounter_type = ifelse(encounter_type == "inpatient_unrelated", "outpatient", encounter_type)) %>%
  mutate(icu_admitted = ifelse(icu_admitted == "yes_unrelated", "no", icu_admitted))

table1_testing <- df_table1 %>% 
  tbl_summary(by = positive_rsv,
              
              type = all_continuous() ~ "continuous2",       # indicate that you want to print multiple statistics 
              statistic = list(all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})"),                 
                          all_categorical() ~ "{n} ({p}%)"),
              
              digits = list(all_categorical() ~ c(0, 1),
                            all_continuous() ~ 1),
              
              label  = list(  
                Sex ~ "Sex", 
                age_at_test_in_months ~ "Age at testing (months)",
                race_ethnicity ~ "Race and ethnicity",
                encounter_type ~ "Encounter type",
                risk_factor_gestage ~ "Gestational age",
                insurance_type ~ "Insurance type",
                rsv_mab ~ "mAb status",
                risk_factor_atleastone ~ "Having at least one risk factor",
                icu_admitted ~ "ICU admission",
                month_when_tested ~ "Month tested"
                ),
        missing_text = "Missing"
        #,
         #     percent = "row"
        #      missing= "no"
                      ) %>% 
  add_p(pvalue_fun = ~ style_pvalue(., digits = 3)) %>% 
  add_overall(last = F) %>%
  bold_labels()


table1_testing %>% as_flex_table() %>% 
  flextable::set_table_properties( width = 1, layout = "autofit") 
  
```

<br>


```{r echo = T}
confounders <- c("Sex", 
                 "risk_factor_gestage",
                 "age_at_test_in_months",
                 "race_ethnicity",
                  "insurance_type",
                  "risk_factor_atleastone",
                 "month_when_tested"
                  )

```

<br>

### Effectiveness of Nirsevimab (unmatched) {.tabset}

#### Table `r tab.counter`. Case: RSV+; control: RSV-
```{r warning=F}
tab.counter <- tab.counter + 1

# define case and control
df.unmatched <- df %>% mutate(case_control = positive_rsv)

###################
# VE (unstratified)
###################
ve.unmatched.unadj <- regress_unmatch(df.ve = df.unmatched,
                                      adjusted = "no") %>%
  mutate(stratify_by = "unstratified", strata = NA)

ve.unmatched.adj <- regress_unmatch(df.ve = df.unmatched, 
                                    adjusted = "yes") %>%
  mutate(stratify_by = "unstratified", strata = NA)


###################
# VE (stratified)
###################

# by gestational age
ve.unmatched.gestage <- regress_unmatch_stratified(df.ve = df.unmatched, 
                                                   stratify_by = "risk_factor_gestage")


# by sex
ve.unmatched.sex <- regress_unmatch_stratified(df.ve = df.unmatched, 
                                               stratify_by = "Sex")

# by age at test
ve.unmatched.agetested <- regress_unmatch_stratified(df.ve = df.unmatched, 
                                                     stratify_by = "age_at_test_in_months_cat")


# by race 
ve.unmatched.race <- regress_unmatch_stratified(df.ve = df.unmatched %>% filter(race_ethnicity != "unknown"), 
                                                     stratify_by = "race_ethnicity")

# by insurance type 
ve.unmatched.insurance <- regress_unmatch_stratified(df.ve = df.unmatched %>% filter(insurance_type != "uninsured"), 
                                                     stratify_by = "insurance_type")

# by risk factor 
ve.unmatched.riskfactor <- regress_unmatch_stratified(df.ve = df.unmatched, 
                                                     stratify_by = "risk_factor_atleastone")

# combine into one table 
ve.unmatched.unadj %>% 
  mutate(across(starts_with("ve"), ~ round(.*100, 1))) %>%
  mutate(VE.unadjusted = paste0(ve_median, " (", ve_lb, "-", ve_ub, ")")) %>%
  dplyr::select(VE.unadjusted) %>%
  cbind(
    ve.unmatched.adj %>% 
      mutate(across(starts_with("ve"), ~ round(.*100, 1))) %>%
      mutate(VE.adjusted = paste0(ve_median, " (", ve_lb, "-", ve_ub, ")")) %>%
      mutate(n_overall = paste0(n_overall, " (", n_overall_eff, ")"),
         n_cases = paste0(n_cases, " (", n_cases_eff, ")"),
         n_controls = paste0(n_controls, " (", n_controls_eff, ")")) %>%
      dplyr::select(stratify_by, strata, n_overall, n_cases, n_controls, VE.adjusted)
  ) %>% 
  dplyr::select(stratify_by, strata, n_overall, n_cases, n_controls, VE.unadjusted, VE.adjusted) %>% 
  rbind(
    rbind(
  
  ve.unmatched.gestage,
  ve.unmatched.sex,
  ve.unmatched.agetested,
  ve.unmatched.race,
  ve.unmatched.insurance,
  ve.unmatched.riskfactor
) %>% 
  # filter out NA 
  filter(!is.na(ve_ub_unadj)) %>%
  mutate(across(starts_with("ve"), ~ round(. * 100, 1))) %>%
  mutate(VE.unadjusted = paste0(ve_median_unadj, " (", ve_lb_unadj, "-", ve_ub_unadj, ")")) %>%
  mutate(VE.adjusted = paste0(ve_median_adj, " (", ve_lb_adj, "-", ve_ub_adj, ")")) %>%
  mutate(n_overall = paste0(n_overall, " (", n_overall_eff, ")"),
         n_cases = paste0(n_cases, " (", n_cases_eff, ")"),
         n_controls = paste0(n_controls, " (", n_controls_eff, ")")) %>%
  dplyr::select(stratify_by, strata, n_overall, n_cases, n_controls, VE.unadjusted, VE.adjusted) 
  ) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            groupBy = "stratify_by", defaultExpanded = T) 
  
```


#### Table `r tab.counter`. Case: RSV+ & hospitalized; control: RSV-
  * TBC: control should be only RSV- or also include RSV+ but not hospitalized?
```{r warning=F}
tab.counter <- tab.counter + 1

# define case and control
df.unmatched <- df %>% 
  mutate(case_control = case_when(positive_rsv == 1 & encounter_type == "inpatient" ~ 1,
                                  positive_rsv == 0 ~ 0)) %>% 
  filter(!is.na(case_control)) %>%
  filter(insurance_type != "uninsured")


###################
# VE (unstratified)
###################
ve.unmatched.unadj <- regress_unmatch(df.ve = df.unmatched,
                                      adjusted = "no") %>%
  mutate(stratify_by = "unstratified", strata = NA)

ve.unmatched.adj <- regress_unmatch(df.ve = df.unmatched, 
                                    adjusted = "yes") %>%
  mutate(stratify_by = "unstratified", strata = NA)


###################
# VE (stratified)
###################

# by gestational age
ve.unmatched.gestage <- regress_unmatch_stratified(df.ve = df.unmatched, 
                                                   stratify_by = "risk_factor_gestage")


# by sex
ve.unmatched.sex <- regress_unmatch_stratified(df.ve = df.unmatched, 
                                               stratify_by = "Sex")

# by age at test
ve.unmatched.agetested <- regress_unmatch_stratified(df.ve = df.unmatched, 
                                                     stratify_by = "age_at_test_in_months_cat")


# by race 
ve.unmatched.race <- regress_unmatch_stratified(df.ve = df.unmatched %>% filter(race_ethnicity!= "unknown"), 
                                                     stratify_by = "race_ethnicity")

# by insurance type 
ve.unmatched.insurance <- regress_unmatch_stratified(df.ve = df.unmatched %>% filter(insurance_type != "uninsured"), 
                                                     stratify_by = "insurance_type")

# by risk factor 
ve.unmatched.riskfactor <- regress_unmatch_stratified(df.ve = df.unmatched, 
                                                     stratify_by = "risk_factor_atleastone")

# combine into one table 
ve.unmatched.unadj %>% 
  mutate(across(starts_with("ve"), ~ round(.*100, 1))) %>%
  mutate(VE.unadjusted = paste0(ve_median, " (", ve_lb, "-", ve_ub, ")")) %>%
  dplyr::select(VE.unadjusted) %>%
  cbind(
    ve.unmatched.adj %>% 
      mutate(across(starts_with("ve"), ~ round(.*100, 1))) %>%
      mutate(VE.adjusted = paste0(ve_median, " (", ve_lb, "-", ve_ub, ")")) %>%
      mutate(n_overall = paste0(n_overall, " (", n_overall_eff, ")"),
         n_cases = paste0(n_cases, " (", n_cases_eff, ")"),
         n_controls = paste0(n_controls, " (", n_controls_eff, ")")) %>%
      dplyr::select(stratify_by, strata, n_overall, n_cases, n_controls, VE.adjusted)
  ) %>% 
  dplyr::select(stratify_by, strata, n_overall, n_cases, n_controls, VE.unadjusted, VE.adjusted) %>% 
  rbind(
    rbind(
  
  ve.unmatched.gestage,
  ve.unmatched.sex,
  ve.unmatched.agetested,
  ve.unmatched.race,
  ve.unmatched.insurance,
  ve.unmatched.riskfactor
) %>% 
  # filter out NA 
  filter(!is.na(ve_ub_unadj)) %>%
  mutate(across(starts_with("ve"), ~ round(. * 100, 1))) %>%
  mutate(VE.unadjusted = paste0(ve_median_unadj, " (", ve_lb_unadj, "-", ve_ub_unadj, ")")) %>%
  mutate(VE.adjusted = paste0(ve_median_adj, " (", ve_lb_adj, "-", ve_ub_adj, ")")) %>%
  mutate(n_overall = paste0(n_overall, " (", n_overall_eff, ")"),
         n_cases = paste0(n_cases, " (", n_cases_eff, ")"),
         n_controls = paste0(n_controls, " (", n_controls_eff, ")")) %>%
  dplyr::select(stratify_by, strata, n_overall, n_cases, n_controls, VE.unadjusted, VE.adjusted) 
  ) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            groupBy = "stratify_by", defaultExpanded = T) 
  

```

#### Table `r tab.counter`. Case: RSV+ & severe; control: RSV- 
  * TBC: control should be only RSV- or also include RSV+ but not hospitalized? 
  * here severe cases includes: those admitted to ICU or ordered highflow oxygen
```{r warning=F}
tab.counter <- tab.counter + 1

# define case and control
df.unmatched <- df %>% 
  mutate(case_control = case_when(positive_rsv == 1 & (icu_admitted == "yes" | highflow_oxygen == 1) ~ 1,
                                  positive_rsv == 0 ~ 0)) %>% 
  filter(!is.na(case_control)) %>%
  filter(insurance_type != "uninsured")

###################
# VE (unstratified)
###################
ve.unmatched.unadj <- regress_unmatch(df.ve = df.unmatched,
                                      adjusted = "no") %>%
  mutate(stratify_by = "unstratified", strata = NA)

ve.unmatched.adj <- regress_unmatch(df.ve = df.unmatched,
                                    adjusted = "yes") %>%
  mutate(stratify_by = "unstratified", strata = NA)


###################
# VE (stratified)
###################

# by gestational age
ve.unmatched.gestage <- regress_unmatch_stratified(df.ve = df.unmatched, 
                                                   stratify_by = "risk_factor_gestage")


# by sex
ve.unmatched.sex <- regress_unmatch_stratified(df.ve = df.unmatched, 
                                               stratify_by = "Sex")

# by age at test
ve.unmatched.agetested <- regress_unmatch_stratified(df.ve = df.unmatched, 
                                                     stratify_by = "age_at_test_in_months_cat")


# by race 
ve.unmatched.race <- regress_unmatch_stratified(df.ve = df.unmatched %>% filter(race_ethnicity != "unknown"), 
                                                     stratify_by = "race_ethnicity")

# by insurance type 
ve.unmatched.insurance <- regress_unmatch_stratified(df.ve = df.unmatched %>% filter(insurance_type != "uninsured"), 
                                                     stratify_by = "insurance_type")

# by risk factor 
ve.unmatched.riskfactor <- regress_unmatch_stratified(df.ve = df.unmatched, 
                                                     stratify_by = "risk_factor_atleastone")

# combine into one table 
ve.unmatched.unadj %>% 
  mutate(across(starts_with("ve"), ~ round(.*100, 1))) %>%
  mutate(VE.unadjusted = paste0(ve_median, " (", ve_lb, "-", ve_ub, ")")) %>%
  dplyr::select(VE.unadjusted) %>%
  cbind(
    ve.unmatched.adj %>% 
      mutate(across(starts_with("ve"), ~ round(.*100, 1))) %>%
      mutate(VE.adjusted = paste0(ve_median, " (", ve_lb, "-", ve_ub, ")")) %>%
      mutate(n_overall = paste0(n_overall, " (", n_overall_eff, ")"),
         n_cases = paste0(n_cases, " (", n_cases_eff, ")"),
         n_controls = paste0(n_controls, " (", n_controls_eff, ")")) %>%
      dplyr::select(stratify_by, strata, n_overall, n_cases, n_controls, VE.adjusted)
  ) %>% 
  dplyr::select(stratify_by, strata, n_overall, n_cases, n_controls, VE.unadjusted, VE.adjusted) %>% 
  rbind(
    rbind(
  
  ve.unmatched.gestage,
  ve.unmatched.sex,
  ve.unmatched.agetested,
  ve.unmatched.race,
  ve.unmatched.insurance,
  ve.unmatched.riskfactor
) %>% 
  # filter out NA 
  filter(!is.na(ve_ub_unadj)) %>%
  mutate(across(starts_with("ve"), ~ round(. * 100, 1))) %>%
  mutate(VE.unadjusted = paste0(ve_median_unadj, " (", ve_lb_unadj, "-", ve_ub_unadj, ")")) %>%
  mutate(VE.adjusted = paste0(ve_median_adj, " (", ve_lb_adj, "-", ve_ub_adj, ")")) %>%
  mutate(n_overall = paste0(n_overall, " (", n_overall_eff, ")"),
         n_cases = paste0(n_cases, " (", n_cases_eff, ")"),
         n_controls = paste0(n_controls, " (", n_controls_eff, ")")) %>%
  dplyr::select(stratify_by, strata, n_overall, n_cases, n_controls, VE.unadjusted, VE.adjusted) 
  ) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            groupBy = "stratify_by", defaultExpanded = T) 
  



```


#### Table `r tab.counter`. Case: RSV+ & ICU admitted; control: RSV- 
  * TBC: control should be only RSV- or also include RSV+ but not admitted to ICU? 
  * there are only 24 records with RSV+ and also admitted to ICU, might be too small sample size.
```{r warning=F}
tab.counter <- tab.counter + 1

# define case and control
df.unmatched <- df %>% 
  mutate(case_control = case_when(positive_rsv == 1 & icu_admitted == "yes" ~ 1,
                                  positive_rsv == 0 ~ 0)) %>%
  filter(!is.na(case_control))

regress_unmatch(df.ve = df.unmatched, adjusted = "no") %>% 
  mutate(across(ve_median: ve_ub, ~ round(.*100,1))) %>%
  mutate(VE.unadjusted = paste0(ve_median, " (", ve_lb, "-", ve_ub, ")")) %>%
  dplyr::select(VE.unadjusted) %>%
  cbind(
    regress_unmatch(df.ve = df.unmatched, adjusted = "yes") %>%
    mutate(across(ve_median: ve_ub, ~ round(.*100,1))) %>%
    mutate(VE.adjusted = paste0(ve_median, " (", ve_lb, "-", ve_ub, ")")) %>%
    mutate(n_overall = paste0(n_overall, " (", n_overall_eff, ")"),
           n_cases = paste0(n_cases, " (", n_cases_eff, ")"),
           n_controls = paste0(n_controls, " (", n_controls_eff, ")")) %>%
    dplyr::select(n_overall, n_cases, n_controls, VE.adjusted)
  ) %>% 
  dplyr::select(n_overall, n_cases, n_controls, VE.unadjusted, VE.adjusted) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T) 

```

<br>

#### Table `r tab.counter`. VE by severity (Case-only analyses) 
  * Only doing unstratified for now.
  * severe cases includes those admitted to ICU and those ordered highflow oxygen.
```{r warning=F}
tab.counter <- tab.counter + 1

## RSV+ & hospitalized vs. RSV+ unhospitalized
df.severity <- df %>% filter(positive_rsv == 1) %>% 
  filter(encounter_type != "inpatient_unrelated") %>%
  mutate(case_control = case_when(encounter_type == "inpatient" ~ 1,
                                  encounter_type == "outpatient" ~ 0))

ve.severity.hosp.unadj <- regress_unmatch(df.ve = df.severity, adjusted = "no") %>% 
  mutate(type = "RSV+ & hospitalized vs. RSV+ unhospitalized")
ve.severity.hosp.adj <- regress_unmatch(df.ve = df.severity, adjusted = "yes") %>%
  mutate(type = "RSV+ & hospitalized vs. RSV+ unhospitalized")


## RSV+ & severe vs. RSV+ mild
# (severe: admitted to ICU or highflow_oxygen == "yes)
df.severity <- df %>% filter(positive_rsv == 1) %>% 
  mutate(case_control = case_when(icu_admitted == "yes" | highflow_oxygen == 1 ~ 1,
                                  TRUE ~ 0))

ve.severity.severe.unadj <- regress_unmatch(df.ve = df.severity, adjusted = "no") %>%
  mutate(type = "RSV+ & severe vs. RSV+ & not severe")
ve.severity.severe.adj <- regress_unmatch(df.ve = df.severity, adjusted = "yes") %>%
  mutate(type = "RSV+ & severe vs. RSV+ & not severe")


# combine into one table
ve.unmatched.severity <- 
  # unadjusted ve
  rbind(
    ve.severity.hosp.unadj,
    ve.severity.severe.unadj
  ) %>%
  dplyr::select(ve_median, ve_lb, ve_ub, type) %>%
  mutate(across(ve_median:ve_ub, ~ round(. * 100, 1))) %>%
  mutate(VE.unadjusted = paste0(ve_median, " (", ve_lb, "-", ve_ub, ")")) %>%
  dplyr::select(-c(ve_median, ve_lb, ve_ub)) %>%
  left_join(
    rbind(
      ve.severity.hosp.adj,
      ve.severity.severe.adj
  ) %>%
  mutate(n_overall = paste0(n_overall, " (", n_overall_eff, ")"),
         n_cases = paste0(n_cases, " (", n_cases_eff, ")"),
         n_controls = paste0(n_controls, " (", n_controls_eff, ")")) %>%
  mutate(across(ve_median:ve_ub, ~ round(. * 100, 1))) %>%
  mutate(VE.adjusted = paste0(ve_median, " (", ve_lb, "-", ve_ub, ")")) %>%
  dplyr::select(-c(ve_median, ve_lb, ve_ub, n_overall_eff, n_cases_eff, n_controls_eff)),
  by = c("type")
  ) %>%
  dplyr::select(type, n_overall, n_cases, n_controls, VE.unadjusted, VE.adjusted)

ve.unmatched.severity %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T) 
```

#### Table `r tab.counter`. VE over time (2 months break)
```{r}
tab.counter <- tab.counter + 1

# classify time since mab to testing 
df <- df %>% 
  mutate(days_btw_mab_collection_cat = 
           case_when(days_btw_mab_collection < 0 & days_btw_mab_collection > -60 ~ "0-2 months", 
                     days_btw_mab_collection <= -60 & days_btw_mab_collection > -120 ~ "2-4 months",
                     days_btw_mab_collection <= -120 ~ "4 months +",
                     is.na(days_btw_mab_collection) | days_btw_mab_collection >= 0 ~ "no mAb"))

# define case control
df.wane <- df %>% mutate(case_control = positive_rsv) %>%
  mutate(days_btw_mab_collection_cat = factor(days_btw_mab_collection_cat,
                                              levels = c("no mAb",
                                                         "0-2 months",
                                                         "2-4 months",
                                                         "4 months +")))

# unadjusted 
model.unadj <- glm(case_control ~ days_btw_mab_collection_cat, data = df.wane, family = "binomial")

ve.median.unadj <- 1 - exp(model.unadj$coefficients[2:4])
ve.ub.unadj <- 1 - exp(confint(model.unadj)[,1][2:4])
ve.lb.unadj <- 1 - exp(confint(model.unadj)[,2][2:4])

# adjusted 
formula <- as.formula(paste0("case_control ~ days_btw_mab_collection_cat + ", 
                             paste(confounders, collapse = " + ")))
model.adj <- glm(formula, data = df.wane, family = "binomial")
ve.median.adj <- 1 - exp(model.adj$coefficients[2:4])
ve.ub.adj <- 1 - exp(confint(model.adj)[,1][2:4])
ve.lb.adj <- 1 - exp(confint(model.adj)[,2][2:4])

n.cases.eff <- df.wane[, c("case_control", "days_btw_mab_collection_cat", confounders)] %>%
  filter(across(everything(), ~ !is.na(.))) %>% filter(case_control == 1) %>% count(days_btw_mab_collection_cat)

n.controls.eff <- df.wane[, c("case_control", "days_btw_mab_collection_cat", confounders)] %>%
  filter(across(everything(), ~ !is.na(.))) %>% filter(case_control == 0) %>% count(days_btw_mab_collection_cat)

n.overall.eff <- n.cases.eff + n.controls.eff

n.cases <-  df.wane[, c("case_control", "days_btw_mab_collection_cat")] %>%
  filter(across(everything(), ~ !is.na(.))) %>% filter(case_control == 1) %>% count(days_btw_mab_collection_cat)

n.controls <-  df.wane[, c("case_control", "days_btw_mab_collection_cat")] %>%
  filter(across(everything(), ~ !is.na(.))) %>% filter(case_control == 0) %>% count(days_btw_mab_collection_cat)

n.overall <- n.cases + n.controls 

data.frame(
  strata = c("immunized 0-2 months ago", "immuniaed 2-4 months ago", "immunized 4 months + ago"),
  n.overall = paste0(n.overall[,2], " (", n.overall.eff[,2], ")")[2:4],
  n.cases = paste0(n.cases[,2], " (", n.cases.eff[,2], ")")[2:4],
  n.controls = paste0(n.controls[,2], " (", n.controls.eff[,2], ")")[2:4],
  VE.unadjusted = paste0(round(ve.median.unadj*100,1), " (", round(ve.lb.unadj*100,1), "-", round(ve.ub.unadj*100,1), ")"),
  VE.adjusted = paste0(round(ve.median.adj*100,1), " (", round(ve.lb.adj*100,1), "-", round(ve.ub.adj*100,1), ")")
) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T) 
  
```
<br>

#### Table `r tab.counter`. VE over time (1 month break)
```{r}
tab.counter <- tab.counter + 1

# classify time since mab to testing 
df <- df %>% 
  mutate(days_btw_mab_collection_cat_2 = 
           case_when(days_btw_mab_collection < 0 & days_btw_mab_collection > -30 ~ "0-1 months", 
                     days_btw_mab_collection <= -30 & days_btw_mab_collection > -60 ~ "1-2 months",
                     days_btw_mab_collection <= -60 & days_btw_mab_collection > -90 ~ "2-3 months",
                     days_btw_mab_collection <= -90 & days_btw_mab_collection > -120 ~ "3-4 months",
                     days_btw_mab_collection <= -120 ~ "4 months +",
                     is.na(days_btw_mab_collection) | days_btw_mab_collection >= 0 ~ "no mAb"))

# define case control
df.wane <- df %>% mutate(case_control = positive_rsv) %>%
  mutate(days_btw_mab_collection_cat_2 = factor(days_btw_mab_collection_cat_2,
                                              levels = c("no mAb",
                                                         "0-1 months",
                                                         "1-2 months",
                                                         "2-3 months",
                                                         "3-4 months",
                                                         "4 months +")))

# unadjusted 
model.unadj <- glm(case_control ~ days_btw_mab_collection_cat_2, data = df.wane, family = "binomial")

ve.median.unadj <- 1 - exp(model.unadj$coefficients[2:6])
ve.ub.unadj <- 1 - exp(confint(model.unadj)[,1][2:6])
ve.lb.unadj <- 1 - exp(confint(model.unadj)[,2][2:6])

# adjusted 
formula <- as.formula(paste0("case_control ~ days_btw_mab_collection_cat_2 + ", 
                             paste(confounders, collapse = " + ")))
model.adj <- glm(formula, data = df.wane, family = "binomial")
ve.median.adj <- 1 - exp(model.adj$coefficients[2:6])
ve.ub.adj <- 1 - exp(confint(model.adj)[,1][2:6])
ve.lb.adj <- 1 - exp(confint(model.adj)[,2][2:6])

n.cases.eff <- df.wane[, c("case_control", "days_btw_mab_collection_cat_2", confounders)] %>%
  filter(across(everything(), ~ !is.na(.))) %>% filter(case_control == 1) %>% count(days_btw_mab_collection_cat_2)

n.controls.eff <- df.wane[, c("case_control", "days_btw_mab_collection_cat_2", confounders)] %>%
  filter(across(everything(), ~ !is.na(.))) %>% filter(case_control == 0) %>% count(days_btw_mab_collection_cat_2)

n.overall.eff <- n.cases.eff + n.controls.eff

n.cases <-  df.wane[, c("case_control", "days_btw_mab_collection_cat_2")] %>%
  filter(across(everything(), ~ !is.na(.))) %>% filter(case_control == 1) %>% count(days_btw_mab_collection_cat_2)

n.controls <-  df.wane[, c("case_control", "days_btw_mab_collection_cat_2")] %>%
  filter(across(everything(), ~ !is.na(.))) %>% filter(case_control == 0) %>% count(days_btw_mab_collection_cat_2)

n.overall <- n.cases + n.controls 

data.frame(
  strata = c("immunized 0-1 months ago", "immuniaed 1-2 months ago", "immuniaed 2-3 months ago",
             "immuniaed 3-4 months ago", "immunized 4 months + ago"),
  n.overall = paste0(n.overall[,2], " (", n.overall.eff[,2], ")")[2:6],
  n.cases = paste0(n.cases[,2], " (", n.cases.eff[,2], ")")[2:6],
  n.controls = paste0(n.controls[,2], " (", n.controls.eff[,2], ")")[2:6],
  VE.unadjusted = paste0(round(ve.median.unadj*100,1), " (", round(ve.lb.unadj*100,1), "-", round(ve.ub.unadj*100,1), ")"),
  VE.adjusted = paste0(round(ve.median.adj*100,1), " (", round(ve.lb.adj*100,1), "-", round(ve.ub.adj*100,1), ")")
) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T) 
  
```

<br>

### Effectiveness of Nirsevimab **(matched)**

#### Match each case (RSV positive) with controls (RSV negative). Match by:
  * tested date: within 14 days before of after (TBC: whether need to add this as confounder to unmatched analysis, maybe add as month tested?)
  * age when tested (months): exact the same month of age.
  * sex
  * race and ethnicity
  
#### Here match case with all eligible controls. 
```{r}
df.matched <- df %>% mutate(case_control = positive_rsv) %>% 
  mutate(collection_date = as.Date(collection_date))


df.cases <- df.matched %>% filter(case_control == 1)
df.cases$id_case <- 1:nrow(df.cases)
df.controls <- df.matched %>% filter(case_control == 0)

n.cases <- nrow(df.cases)


for(i in 1:n.cases){
  
  df.temp <- df.cases[i,]
  
  # this case's traits
  case.test.date <- df.temp$collection_date
  case.age <- floor(df.temp$age_at_test_in_months)
  case.sex <- df.temp$Sex
  case.race <- df.temp$race_ethnicity
  case.insurance <- df.temp$insurance_type
  case.gestage <- df.temp$risk_factor_gestage
  
  df.matched.controls <- df.controls %>%
    filter(collection_date >= case.test.date - 14 & collection_date <= case.test.date + 14) %>%
    filter(floor(age_at_test_in_months) ==  case.age) %>%
    filter(Sex == case.sex) %>%
    filter(race_ethnicity == case.race)
    # filter(insurance_type == case.insurance) %>% 
    # filter(risk_factor_gestage == case.gestage) 
  
  if(nrow(df.matched.controls != 0)){
    df.matched.controls <- df.matched.controls %>% mutate(id_case = i)
    df.case.control.temp <- rbind(df.temp, 
                                  df.matched.controls) 
    if(i == 1){df.case.control <- df.case.control.temp}
    if(i != 1){df.case.control <- rbind(df.case.control, df.case.control.temp)}
  }
  
}


# there are some cases without matched controls (n=72)
n.unmatched <- nrow(df.cases) - length(unique(df.case.control$id_case)) 
id.unmatched <- c(1:nrow(df.cases))[c(1:nrow(df.cases)) %in% unique(df.case.control$id_case) == F]

# average number of control matched (n ~ 5)
n.mean.controls <- mean((df.case.control %>% filter(case_control == 0) %>% group_by(id_case) %>% count() )$n)

```


### Table `r tab.counter`. Take a look at matched cases and controls 
```{r}
tab.counter <- tab.counter + 1

df.case.control %>% 
  count(case_control) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T) 

```

<br>

### Table `r tab.counter`. Compare matched cases and unmatched cases 
```{r}
tab.counter <- tab.counter + 1

df.cases <- df.cases %>%
  mutate(matched = ifelse(id_case %in% id.unmatched, "unmatched", "matched"))

df_compare <- df.cases %>%
  mutate(rsv_mab = ifelse(rsv_mab == 1, "yes", "no")) %>%
  dplyr::select(positive_rsv,Sex, age_at_test_in_months, race_ethnicity, encounter_type, risk_factor_gestage, insurance_type, rsv_mab, risk_factor_atleastone, icu_admitted, matched) %>% 
  mutate(positive_rsv = case_when(positive_rsv == 1 ~ "Cases (RSV+)",
                                  positive_rsv == 0 ~ "Controls (RSV-)")) %>%
  # count "unrelated" hosp and ICU admissions as "no"
  mutate(encounter_type = ifelse(encounter_type == "inpatient_unrelated", "outpatient", encounter_type)) %>%
  mutate(icu_admitted = ifelse(icu_admitted == "yes_unrelated", "no", icu_admitted))

tab_compare <- df_compare %>% 
  tbl_summary(by = "matched",
              
              type = all_continuous() ~ "continuous2",       # indicate that you want to print multiple statistics 
              statistic = list(all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})"),                 
                          all_categorical() ~ "{n} ({p}%)"),
              
              digits = list(all_categorical() ~ c(0, 1),
                            all_continuous() ~ 1),
              
              label  = list(  
                Sex ~ "Sex", 
                age_at_test_in_months ~ "Age at testing (months)",
                race_ethnicity ~ "Race and ethnicity",
                encounter_type ~ "Encounter type",
                risk_factor_gestage ~ "Gestational age",
                insurance_type ~ "Insurance type",
                rsv_mab ~ "mAb status",
                risk_factor_atleastone ~ "Having at least one risk factor",
                icu_admitted ~ "ICU admission"
                ),
        missing_text = "Missing"
        #,
         #     percent = "row"
        #      missing= "no"
                      ) %>% 
  add_p(pvalue_fun = ~ style_pvalue(., digits = 3)) %>% 
  add_overall(last = F) %>%
  bold_labels()


tab_compare %>% as_flex_table() %>% 
  flextable::set_table_properties( width = 1, layout = "autofit") 

```


#### After matching, there are still `r n.unmatched` cases with no matched controls (excluded these from matched cc analysis), the mean number of controls matched to a case is 5.

```{r}
confounders_matched <- c("risk_factor_gestage",
                         "insurance_type",
                         "risk_factor_atleastone")

```

<br>


### Matched case-control to get VE {.tabset}

#### Table `r tab.counter` RSV+ vs. RSV-
```{r}
tab.counter <- tab.counter + 1

df.matched <- df.case.control 

##############
# unstratified
##############

# unadjusted
formula <- as.formula("case_control ~ rsv_mab + strata(id_case)")

model <- clogit(formula, data = df.matched)

ve.median.unadj <- 1- exp(model$coefficients)
ve.ub.unadj <- 1- exp(confint(model)[1])
ve.lb.unadj <- 1- exp(confint(model)[2])


# adjusted 
formula <- as.formula(paste0("case_control ~ rsv_mab + ",
                             paste(confounders_matched, collapse = " + "),
                             " + strata(id_case)"))

model <- clogit(formula, data = df.matched)

ve.median.adj <- 1- exp(model$coefficients[1])
ve.ub.adj <- 1- exp(confint(model)[,1][1])
ve.lb.adj <- 1- exp(confint(model)[,2][1])

# get the number of cases and controls 
n.cases <- df.matched %>% filter(case_control == 1) %>% nrow()
n.controls <- df.matched %>% filter(case_control == 0) %>% nrow()
n.overall <- n.cases + n.controls 

n.cases.eff <- df.matched[, c("case_control", confounders)] %>% filter(case_control == 1) %>%
  filter(across(confounders, ~ !is.na(.))) %>% nrow()
n.controls.eff <- df.matched[, c("case_control", confounders)] %>% filter(case_control == 0) %>%
  filter(across(confounders, ~ !is.na(.))) %>% nrow()
n.overall.eff <- n.cases.eff + n.controls.eff

# combine into one table 
data.frame(
  n.overall = paste0(n.overall, " (", n.overall.eff, ")"),
  n.cases = paste0(n.cases, " (", n.cases.eff, ")"),
  n.controls = paste0(n.controls, " (", n.controls.eff, ")"),
  VE.unadj = paste0(round(ve.median.unadj*100,1), " (", 
                    round(ve.lb.unadj*100,1), "-", 
                    round(ve.ub.unadj*100,1), ")"),
  VE.adj = paste0(round(ve.median.adj*100,1), " (", 
                    round(ve.lb.adj*100,1), "-", 
                    round(ve.ub.adj*100,1), ")")
) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            defaultExpanded = T) 

```











