---
title: "Check and recode variables"
output: 
  html_document:
    toc: true
    toc_float: true
---

#### Date: `r Sys.Date()`

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

library(dplyr)
library(tidyr)
library(tidyverse)
library(readxl)
library(writexl)
library(reactable)
library(ggplot2)
library(stringr)


fig.counter <- 1
tab.counter <- 1

save_recoded_dataset <- FALSE
```

### Table `r tab.counter`. StudyID
```{r}
tab.counter <- tab.counter + 1
# read in data from onedrive shared folder 
df <- read_excel("/Users/hmx/OneDrive - Yale University/Hanmeng RSV VE/data/RSV_deid_2024_may.xlsx", sheet = "Dataset")

n_unique <- length(unique(df$StudyID))
n_single_test <- df %>% group_by(StudyID) %>% count() %>% filter(n==1) %>% nrow()
n_multi_test <- df %>% group_by(StudyID) %>% count() %>% filter(n>1) %>% nrow()

df %>% group_by(StudyID) %>% count() %>% group_by(n) %>% count() %>% rename(`Times tested` = n, n_patients = nn) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

```

There are `r n_unique` patients in the original main dataset. There are `r n_single_test` patients tested only once, and `r n_multi_test` patients were tested more than once. 

<br>

### Figure `r fig.counter`. Display age at testing
  * Age eligibility:   
    + it is possible that they are > 1yo when being tested
    + the mAb is available in October 2023, and is recommended for those under 8 month (CDC), so in theory, only those born after February 2023 are eligible for mAb, these should be included.
    + however, as mAb is also recommended for older high risk infants, also check those born before February and see if they have high risk.
  * Generated age_at_testing_in_days, age_at_testing_in_months.
```{r}
fig.counter <- fig.counter + 1

df <- df %>% mutate(DOB = as.Date(DOB))

df <- df %>% mutate(age_at_test_in_days = as.numeric(as.Date(`Collection Date`) - as.Date(DOB))) %>% 
  mutate(age_at_test_in_months = round(age_at_test_in_days / (365/12), 1))

n_above1yo <- df %>% filter(age_at_test_in_months > 12) %>% nrow()

df %>% 
  ggplot() + theme_classic() +
  geom_histogram(aes(x = age_at_test_in_months), binwidth = 1, color = "black", fill = "white") +
  geom_vline(xintercept = 12, color = "red", linetype = "dashed") +
  annotate("text", x= 13, y = 280, label = "12 months", color = "red")

# remove > 12 months 
# df <- df %>% filter(age_at_test_in_months <= 12)
```

#### There are `r n_above1yo` testing records having age > 12 months at the time of testing. Currently haven't removed any records. (TBC)


<br>

### Table `r tab.counter`. Times tested
```{r}
tab.counter <- tab.counter + 1
# after removing > 12 months records 
n_unique <- length(unique(df$StudyID)) 
n_single_test <- df %>% group_by(StudyID) %>% count() %>% filter(n==1) %>% nrow()
n_multi_test <- df %>% group_by(StudyID) %>% count() %>% filter(n>1) %>% nrow()

# tested many times 
id_multi_tests <- (df %>% group_by(StudyID) %>% count() %>% filter(n > 1))$StudyID # those who had multiple tests
id_5tests <- as.character((df %>% group_by(StudyID) %>% count() %>% filter(n == 5))$StudyID)
id_6tests <- as.character((df %>% group_by(StudyID) %>% count() %>% filter(n == 6))$StudyID)

# unique ids 
id_unique <- (df %>% group_by(StudyID) %>% count())$StudyID 

df %>% group_by(StudyID) %>% count() %>% group_by(n) %>% count() %>% rename(`Times tested` = n, n_patients = nn) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```


After removing records > 12 months at testing, there are `r n_unique` patients in the dataset. There are `r n_single_test` patients tested only once, and `r n_multi_test` patients were tested more than once. 

StudyID for those who were tested 5 timese: `r id_5tests`.
StudyID for those who were tested 6 timese: `r id_6tests`.



<br> 

### Table `r tab.counter` Sex 
recode unknown to NA.
```{r}
tab.counter <- tab.counter + 1

df %>%  count(Sex) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

df <- df %>% 
  mutate(Sex = ifelse(Sex == "Unknown" | Sex == "Choose not to disclose", NA, Sex))

```

<br>

### Figure `r fig.counter`. Sex & Age at testing 
```{r}
fig.counter <- fig.counter + 1

df %>% select(age_at_test_in_months, Sex) %>%
  mutate(age = round(age_at_test_in_months)) %>%
  group_by(Sex, age) %>% count() %>% 
  mutate(n = ifelse(Sex == "Female", -n, n)) %>%
  ggplot() +
  geom_col(aes(x = age, y = n, fill = Sex)) + coord_flip() +
  xlab("Age at testing (months)") + theme_classic()

```

<br>

### Figure `r fig.counter` Collection Date (sample collection date)
Generate collection_date (Date class varaible).
```{r}
fig.counter <- fig.counter + 1

df <- df %>% mutate(collection_date = as.Date(`Collection Date`))
#sum(is.na(df$collection_date)) # no missing for sample collection date
max_cd <- max(df$collection_date)
min_cd <- min(df$collection_date)

df %>% ggplot() +
  geom_histogram(aes(x = collection_date), color="black", fill="white") +
  scale_x_date(date_breaks = "1 month") + theme_classic()


# check if collection date is before DOB
# df %>% filter(`Collection Date` < DOB) # n = 0
```

Sample collection date: `r min_cd` ~ `r max_cd`.

<br>

### Viral test, Resp Result, Viral detected: 
#### From these variables, generate variables:
  * tested_xxx: indicating whether this record was tested for certain virus
  * positive_xxx: the testing results for certain virus (flu,rhino,hmpv,adeno,parainfluenza,rsv).
  * positive_otherviruses: binary variable indicating that this record was tested positive for other viruses other than RSV (if == 1, this record was tested positive for other viruses, but this record can be either negative and positive for RSV.)
  
#### From tested_xxx and positive_xxx, generate new variable:
  * tested_viruses: string class, listing viruses tested for a record (some viruses are not listed here, like covid)
  * positive_viruses: string class, listing viruses tested positive for a record (some viruses are not listed here, like covid)

#### what tests are included in "RESPIRATORY VIRUS PCR PANEL     (BH GH LMW Q YH) [LAB3444]"? (TBC, we discussed this, this might not be that important. )
```{r}
# generate "whether tested" variables 
df <- df %>% 
  mutate(tested_flu = ifelse(`Viral test` %in% c("INFLUENZA A+B/RSV BY RT-PCR [LAB11021]",
                                                  "SARS-COV-2 (COVID-19)/INFLUENZA A+B/RSV BY RT-PCR (BH GH LMW YH) [LAB11020]",
                                                  "RESPIRATORY VIRUS PCR PANEL  (YH VERIGENE)(LAB ORDER ONLY) [LAB10852]",
                                                  "ZZZINFLUENZA/RSV PCR      (BH) [LAB9626]",
                                                  "RESPIRATORY VIRUS PCR PANEL     (BH GH LMW Q YH) [LAB3444]"), 1, 0)) %>% 
  mutate(tested_rhino = ifelse(`Viral test` %in% c("RESPIRATORY VIRUS PCR PANEL  (YH VERIGENE)(LAB ORDER ONLY) [LAB10852]",
                                                   "RESPIRATORY VIRUS PCR PANEL     (BH GH LMW Q YH) [LAB3444]"), 1, 0)) %>%
  mutate(tested_hmpv = ifelse(`Viral test` %in% c("RESPIRATORY VIRUS PCR PANEL  (YH VERIGENE)(LAB ORDER ONLY) [LAB10852]",
                                                  "RESPIRATORY VIRUS PCR PANEL     (BH GH LMW Q YH) [LAB3444]"), 1, 0)) %>%
  mutate(tested_adeno = ifelse(`Viral test` %in% c("RESPIRATORY VIRUS PCR PANEL  (YH VERIGENE)(LAB ORDER ONLY) [LAB10852]",
                                                   "RESPIRATORY VIRUS PCR PANEL     (BH GH LMW Q YH) [LAB3444]"), 1, 0)) %>%
  mutate(tested_parainfluenza = ifelse(`Viral test` %in% c("RESPIRATORY VIRUS PCR PANEL  (YH VERIGENE)(LAB ORDER ONLY) [LAB10852]",
                                                           "RESPIRATORY VIRUS PCR PANEL     (BH GH LMW Q YH) [LAB3444]"), 1, 0)) %>%
  mutate(tested_rsv = ifelse(`Viral test` %in% c("INFLUENZA A+B/RSV BY RT-PCR [LAB11021]",
                                                "SARS-COV-2 (COVID-19)/INFLUENZA A+B/RSV BY RT-PCR (BH GH LMW YH) [LAB11020]",
                                                "RESPIRATORY VIRUS PCR PANEL  (YH VERIGENE)(LAB ORDER ONLY) [LAB10852]",
                                                "ZZZINFLUENZA/RSV PCR      (BH) [LAB9626]",
                                                "ZZZRESPIRATORY SYNCYTIAL VIRUS, RAPID ANTIGEN     (GH) [LAB3465]",
                                                "RESPIRATORY VIRUS PCR PANEL     (BH GH LMW Q YH) [LAB3444]",
                                                "ZZZRESPIRATORY SYNCYTIAL VIRUS BY RT-PCR (GH) [LAB3438]"), 1, 0))
  

# generate binary variables for testing results 
df <- df %>% 
  mutate(positive_fluA = case_when(tested_flu == 1 & str_detect(`Virus detected`, "Influenza A") == TRUE ~ 1,
                                   tested_flu == 1 & (str_detect(`Virus detected`, "Influenza A") == FALSE | 
                                                        is.na(`Virus detected`))  ~ 0)) %>%
  mutate(positive_fluB = case_when(tested_flu == 1 & str_detect(`Virus detected`, "Influenza B") == TRUE ~ 1,
                                   tested_flu == 1 & (str_detect(`Virus detected`, "Influenza B") == FALSE | 
                                                        is.na(`Virus detected`))  ~ 0)) %>%
  mutate(positive_flu = ifelse(positive_fluA == 1 | positive_fluB == 1, 1, 0)) %>% 
  mutate(positive_rhino = case_when(tested_rhino == 1 & str_detect(`Virus detected`, "Rhinovirus") == TRUE ~ 1,
                                    tested_rhino == 1 & (str_detect(`Virus detected`, "Rhinovirus") == FALSE | 
                                                        is.na(`Virus detected`))  ~ 0)) %>%
  mutate(positive_hmpv = case_when(tested_hmpv == 1 & str_detect(`Virus detected`, "HMPV") == TRUE ~ 1,
                                   tested_hmpv == 1 & (str_detect(`Virus detected`, "HMPV") == FALSE | 
                                                        is.na(`Virus detected`))  ~ 0)) %>%
  mutate(positive_adeno = case_when(tested_adeno == 1 & str_detect(`Virus detected`, "Adenovirus") == TRUE ~ 1,
                                    tested_adeno == 1 & (str_detect(`Virus detected`, "Adenovirus") == FALSE | 
                                                        is.na(`Virus detected`))  ~ 0)) %>%
  mutate(positive_parainfluenza = case_when(tested_parainfluenza == 1 & str_detect(`Virus detected`, "Parainfluenza") == TRUE ~ 1,
                                            tested_parainfluenza == 1 & (str_detect(`Virus detected`, "Parainfluenza") == FALSE | 
                                                                is.na(`Virus detected`))  ~ 0)) %>%
  mutate(positive_rsv = case_when(tested_rsv == 1 & str_detect(`Virus detected`, "Syncytial") == TRUE ~ 1,
                                  tested_rsv == 1 & (str_detect(`Virus detected`, "Syncytial") == FALSE | 
                                                                is.na(`Virus detected`))  ~ 0))

# variable listing all viruses tested
df <- cbind.data.frame(df,
    tested_viruses = apply(df, 1, function(x)
        paste(colnames(df[ , grepl( "tested_", names(df))])[ x[grepl( "tested_", names(x))] == 1 ], collapse = " "))) %>% 
  mutate(tested_viruses = str_replace_all(tested_viruses, "tested_", ""))


# variable listing all viruses detected 
df <- cbind.data.frame(df,
    positive_viruses = apply(df %>% 
                               mutate(across(positive_fluA:positive_rsv, ~ as.character(.x))) %>% 
                               mutate(across(positive_fluA:positive_rsv,  ~ replace_na(.x, "NA"))), 1, function(x)
        paste(colnames(df[ , grepl( "positive_", names(df))])[ x[grepl( "positive_", names(x))] == 1 ], collapse = " "))) %>% 
  mutate(positive_viruses = str_replace_all(positive_viruses, "positive_", "")) %>% 
  mutate(positive_viruses = str_replace_all(positive_viruses, "NA", "")) %>% 
  mutate(positive_viruses = str_replace(positive_viruses, " flu", "")) %>% 
  mutate(positive_viruses = ifelse(positive_viruses == "", NA, positive_viruses))


# create a variable positive_otherviruses indicating this record tested positive for other viruses 
df <- df %>% 
  mutate(positive_otherviruses = ifelse(positive_fluA == 1 | 
                                          positive_fluB == 1 |
                                          positive_flu == 1 |
                                          positive_rhino == 1 |
                                          positive_hmpv == 1 |
                                          positive_adeno == 1 |
                                          positive_parainfluenza == 1, 1, 0))

```

### Table `r tab.counter`. Viral test (taken by a record)
```{r}
tab.counter <- tab.counter + 1
# briefly summarize testing
df %>% 
  group_by(tested_viruses) %>% count() %>% arrange(desc(n)) %>% rename(n_records = n) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

```

This table shows the number of testing records (w/ duplicates) that took certain tests, some viruses are not included here (like SARS-CoV-2).

<br>

### Table `r tab.counter`. Viral test results (by virus combo)
Listing all the combinations of viral test results. Each record contributes one virus combo.
```{r}
tab.counter <- tab.counter + 1

df %>% 
  group_by(positive_viruses) %>% count() %>% arrange(desc(n)) %>% rename(n_records = n) %>% 
  mutate(positive_viruses = ifelse(is.na(positive_viruses), "NO detection of any viruses", positive_viruses)) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```

<br>

### Table `r tab.counter`. Viral test results (by single virus)
Listing viruses tested positive, each record can contribute one or more as one record can be tested positive for multiple viruses.
```{r}
tab.counter <- tab.counter + 1

data.frame(
  fluA = nrow(df %>% filter(positive_fluA == 1)),
  fluB = nrow(df %>% filter(positive_fluB == 1)),
  rhino = nrow(df %>% filter(positive_rhino == 1)),
  hmpv = nrow(df %>% filter(positive_hmpv == 1)),
  adeno = nrow(df %>% filter(positive_adeno == 1)),
  parainfluenza = nrow(df %>% filter(positive_parainfluenza == 1)),
  rsv = nrow(df %>% filter(positive_rsv == 1)),
  `No detection` = nrow(df %>% filter(is.na(positive_viruses)))
) %>% pivot_longer(cols = 1:8, names_to = "Virus", values_to = "n_records") %>% 
  arrange(desc(n_records)) %>%
  mutate(perc = round(n_records / nrow(df)*100, 1)) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
  
```

<br>

### Table `r tab.counter`. Admit Date
#### Generate variable days_btw_admit_collect = collection_date - Admit date. If <0, collection before admission.
  * if the admission date and collection date are 7 days away, we consider this admission is "related" to the testing result (TBC).
```{r}
tab.counter <- tab.counter + 1
 
df %>% 
  mutate(days_btw_admit_collect = as.Date(`Collection Date`) - as.Date(`Admit Date`)) %>%
  group_by(days_btw_admit_collect ) %>% count() %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

# those admitted after sample collection
df <- df %>% mutate(days_btw_admit_collect = as.numeric(as.Date(`Collection Date`) - as.Date(`Admit Date`))) 

df <- df %>% mutate(admit_date = as.Date(`Admit Date`))

n_temp <- df %>% filter(days_btw_admit_collect > 7) %>% nrow()
n_temp_case <- df %>% filter(days_btw_admit_collect > 7) %>% filter(positive_rsv == 1) %>% nrow()
#n_temp_mab <- df %>% filter(days_btw_admit_collect > 7) %>% filter(rsv_mab == 1) %>% nrow()



# a <- df %>% filter(days_btw_admit_collect > 7) %>% 
#   mutate(type = ifelse(DOB == admit_date & DOB == date_icu_admit, "ICU admission on DOB", NA)) %>%
#   select(248, 1:247)
# 
# write.csv(a, "../../data/days_btw_admit_collect_morethan7days.csv", row.names = F)
```

There are `r n_temp` records whose collection date was more than 7 days after admission date. Among, these, there are/is `r n_temp_case` RSV+ case, 25 were admitted to ICU on DOB: (how to do with these? TBC)

<br>

### Table `r tab.counter`. Hosp LoS
Length of Stay (in days) of hospitalization originally recorded in the main dataset.
```{r}
tab.counter <- tab.counter + 1

df %>%  count(`Hosp LoS`) %>% reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

n_missing_hosp_los <- df %>% filter(is.na(`Hosp LoS`)) %>% nrow()
```
  * Hosp LOS for "Emergency", "Specimen", "Outpatient", "Hospital Outpatient Surgery" encounter type: all are 1 day;
  * Hosp LOS for "Observation" encounter type: all but 2 records are 2 days, others all 1 day;
  * Hosp LOS for "Newborn" encounter type: range from 3-287 days
  
#### There are `r n_missing_hosp_los` records missing Hosp LoS: (these are all records from BH EMERGENCY DEPARTMENT)
After discussing, these are all outpaitent, thus no hosp stay.
```{r}
df %>% filter(is.na(`Hosp LoS`)) %>% arrange(StudyID) %>% 
  select(StudyID, collection_date, `Collection Department`, tested_viruses, positive_viruses) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```
#### Generate new variable hosp_los:
  * if the encounter type is outpatient ---> NA, as there should be hosp stay for outpatient.
```{r}
df <- df %>% 
  mutate(hosp_los = ifelse(`Encounter Type` %in% c("Emergency", "Outpatient", "Hospital Outpatient Surgery", "Specimen"), NA, `Hosp LoS`) )

df %>% count(hosp_los) %>% arrange(hosp_los) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```
  

<br>

### Table `r tab.counter`. Collection Department & Admission location
#### Recode these two to sample_source variable (might not use this variable?):
  * if Admission Location is available, use Admission Location;
  * if Admission Location is not available, use Collection Department.
```{r}
tab.counter <- tab.counter + 1

df <- df %>% 
  mutate(sample_source = `Admission Location`) %>%
  mutate(sample_source = case_when(is.na(sample_source) ~ `Collection Department`,
                                   TRUE ~ sample_source))

df %>% group_by(sample_source) %>% count() %>% arrange(desc(n)) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

```

<br>

### Table `r tab.counter`. Original Encounter type
This is the Encounter Type recorded in the original main dataset.
```{r}
tab.counter <- tab.counter + 1
df %>% group_by(`Encounter Type`) %>% count() %>% arrange(desc(n)) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```
<br>

### Table `r tab.counter`. Records missing Encounter type 
There are records missings for original "encounter type" variable. Most from LABs or DRAW STATION except one record from "NE PEDS OLD SAYBROOK" (after discussing, this one is an outpatient record). Fill in these missings with "Specimen" or "Outpatient".
```{r}
tab.counter <- tab.counter + 1

df %>% select(StudyID, `Collection Department`, `Admission Location`, `Encounter Type`) %>%
  filter(is.na(`Encounter Type`)) %>% 
  arrange(`Admission Location`) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

df <- df %>%
  mutate(`Encounter Type` = case_when(
    is.na(`Encounter Type`) & str_detect(`Collection Department`, "MAIN LAB|DRAW STATION|SPECIMENS") ~ "Specimen",
    is.na(`Encounter Type`) & `Collection Department` == "NE PEDS OLD SAYBROOK" ~ "Outpatient",
    TRUE ~ `Encounter Type`
  ))
```

<br>

### Table `r tab.counter`. Aggregate "Encounter Type" to fewer categories 
#### Generated new variable: encounter_type, coded as:
  * Emergency ---> outpatient
  * Outpatient ---> outpatient
  * Hospital Outpatient Surgery ---> outpatient 
  * Specimen ---> outpatient
  * Inpatient ---> inpatient 
  * Observation ---> inpatient
  * Newborn ---> inpatient
```{r}
tab.counter <- tab.counter + 1

df <- df %>% 
  mutate(encounter_type = case_when(`Encounter Type` == "Emergency" ~ "outpatient",
                                    `Encounter Type` == "Inpatient" ~ "inpatient",
                                    `Encounter Type` == "Specimen" ~ "outpatient",
                                    `Encounter Type` == "Observation" ~ "inpatient",
                                    `Encounter Type` == "Newborn" ~ "inpatient",
                                    `Encounter Type` == "Outpatient" ~ "outpatient",
                                    `Encounter Type` == "Hospital Outpatient Surgery" ~ "outpatient"))

df %>% count(encounter_type) %>% rename(n_records = n) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
  
```

<br>

### Table `r tab.counter`. ICU admission date
#### Generated new variables:
  + date_icu_admit: the same as ICU Admission Date but in Date class, N/A as NA;
  + days_btw_collection_icu: days between sample collection and ICU admission (collection_date - ICU admission)
  + date_icu_admit_related: ICU admission that can be linked with the testing result (**within a week of sample collection date? yes, discussed. TBC**)
  + icu_admitted_related: binary variable indicating whether the icu can be related to the testing result (within a week of testing)
  
```{r}
tab.counter <- tab.counter + 1

df <- df %>% 
  mutate(date_icu_admit = as.Date(`ICU Admission Date`, "%m/%d/%Y")) %>%
  mutate(days_btw_collection_icu = as.numeric(as.Date(`Collection Date`) - date_icu_admit)) %>% 
  mutate(date_icu_admit_related = case_when(days_btw_collection_icu <= 7 ~ date_icu_admit)) %>%
  mutate(icu_admitted_related = case_when(!is.na(date_icu_admit_related) ~ 1,
                                          !is.na(date_icu_admit) & is.na(date_icu_admit_related) ~ 0))

df %>% count(days_btw_collection_icu) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

n_icu <- nrow(df %>% filter(!is.na(date_icu_admit))) # total ICU admissions 
n_icu_unrelated <- nrow(df %>% filter(days_btw_collection_icu > 7))
```

#### Out of `r n_icu` ICU admissions, `r n_icu_unrelated` have ICU admission more than 7 days before or after sample collection date. Check these: (1 RSV+, 9 took mAb)
```{r}
df %>% filter(days_btw_collection_icu > 7) %>% 
  select(StudyID, DOB, admit_date, date_icu_admit, collection_date,days_btw_collection_icu, positive_rsv) %>% 
  mutate(type = ifelse(DOB == admit_date & DOB == date_icu_admit, 
                       "ICU admission on DOB", NA)) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

# a <- df %>% filter(days_btw_collection_icu > 7) %>% 
#   mutate(type = ifelse(DOB == admit_date & DOB == date_icu_admit, "ICU admission on DOB", NA)) %>%
#   select(248, 1:247)
# write.csv(a, "../../data/days_btw_ICUadmit_collect_morethan7days.csv", row.names = F)
```

<br>

### Figure `r fig.counter`. ICU admission date 
These are ICU admissions within 7 days of sample collection date.
```{r}
fig.counter <- fig.counter + 1

df %>% 
  ggplot() + 
  geom_histogram(aes(x = date_icu_admit_related), color = "black", fill = "white") + theme_classic()
```

<br>

### Figure `r fig.counter`. ICU LOS
#### The original data was in XXd XXh format. Generate new variables:
  * icu_los_hours (unit: hour)
  * icu_los_days (unit: day)
```{r}
fig.counter <- fig.counter + 1

df <- df %>% 
  mutate(icu_los_hours = case_when( 
                                    str_detect(`ICU LOS`, "h") == FALSE & str_detect(`ICU LOS`, "d") == TRUE ~
                                      as.numeric(str_remove(`ICU LOS`, "d")) * 24,
                                    str_detect(`ICU LOS`, "h") == TRUE & str_detect(`ICU LOS`, "d") == FALSE ~ 
                                      as.numeric(str_remove(`ICU LOS`, "h")),
                                    str_detect(`ICU LOS`, "h") == TRUE & str_detect(`ICU LOS`, "d") == TRUE ~ 
                                      parse_number(`ICU LOS`) * 24 + as.numeric(str_remove(gsub(".* ", "", `ICU LOS`), "h")),
                                    str_detect(`ICU LOS`, "m") == TRUE ~ 
                                      as.numeric(str_remove(`ICU LOS`, "m")) * 30
                                  )) %>%
  mutate(icu_los_days = icu_los_hours / 24)


df %>%
  filter(icu_admitted_related == 1) %>%
  ggplot() + ggtitle("Only plotting ICU admissions related to the testing \n (within a week of sample collection)") +
  geom_histogram(aes(x = icu_los_days), color = "black", fill = "white")  + theme_classic()
```

Several infants with ICU LOS longer than 1 month: 

### Table `r tab.counter`.
```{r}
tab.counter <- tab.counter + 1

df %>% filter(icu_admitted_related == 1) %>% filter(icu_los_days > 30)%>% 
  select(StudyID, `Collection Date`, date_icu_admit_related, icu_los_days) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```

<br>

### Figure `r fig.counter`. Gest age (as recorded in "Gest Age" variable)
There are ~700 records missing for original Gest Age variable.

```{r}
fig.counter <- fig.counter + 1

df %>% 
  ggplot() + geom_histogram(aes(x = `Gest Age`), binwidth = 1, color = "black", fill = "white") + theme_classic()
  
```

#### Generate categorical variable of gest age: gest_age_cat **(is the following classification okay? combine groups?)**
#### Reference: https://www.cdc.gov/nchs/data/nvsr/nvsr73/nvsr73-01.pdf
  *	42 and +: post term
  *	41: late term
  * 39-40: full term
  * 37-38: early term
  *	< 37: preterm
 
### Table `r tab.counter`. Gest Age (classified only using "Gest Age" variable)
#### In addition to "Gest Age" variable, I will also use Medical History, Problems.. variables to classify gestational age to fill in NA here, see below.
```{r}
tab.counter <- tab.counter + 1

df <- df %>%
  mutate(gest_age_cat = case_when( `Gest Age` >= 42 ~ "post term",
                                    `Gest Age` == 41 ~ "late term",
                                    `Gest Age` == 39 | `Gest Age` == 40 ~ "full term",
                                    `Gest Age`== 37 | `Gest Age` == 38 ~ "early term",
                                    `Gest Age` < 37 ~ "preterm")) 
  
df %>% count(gest_age_cat) %>% arrange(desc(n)) %>% rename(n_records = n) %>%
  mutate(perc = round(n_records / nrow(df) * 100,1)) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

```

<br>

### Figure `r fig.counter`. Birth weight
  * PENDING: Generate birth_weight_kg (numeric), low_birth_weight (binary). Low birth weight is defined as a birth weight of less than 2500 g (up to and including 2499 g), as per the World Health Organization (WHO).
  * what is the unit of original variable Birth Wgt (ounce??)? Haven't generated new variables (TBC?).
  * After confirming, generate risk factor indicating low birth weight.
```{r}
fig.counter <- fig.counter + 1

df %>% 
  mutate(birth_weight = as.numeric(`Birth Wgt`)) %>%
  ggplot() +
  geom_histogram(aes(x = birth_weight), color = "black", fill = "white") + theme_classic()
```

<br>

### Table `r tab.counter`. Race and Ethnicity
There are many conflicting answers. Here are the unique answers for Race variable:
```{r}
tab.counter <- tab.counter + 1

df %>% count(Race) %>% arrange(desc(n)) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```

<br>

#### To classify race, generate new variable "race". I use dominant answers to classify, e.g. if a records answered both black and white, use black.
```{r echo = T}
df <- df %>% 
  mutate(race = case_when(str_detect(Race, "Black") ~ "Black",
                          Race %in% c("White",
                                      "I Do Not See My Race Listed Here\r\nWhite",
                                      "White\r\nI Do Not Know",
                                      "White\r\nI Do Not See My Race Listed Here",
                                      "I Do Not Know\r\nWhite",
                                      "I Prefer Not To Share\r\nWhite",
                                      "White\r\nI Do Not Know\r\nI Do Not See My Race Listed Here") ~ "White",
                          Race %in% c("Asian",
                                      "Asian\r\nWhite",
                                      "White\r\nAsian",
                                      "Asian\r\nI Do Not Know",
                                      "Asian Indian",
                                      "Asian\r\nPacific Islander\r\nWhite",
                                      "Asian\r\nI Do Not Know\r\nWhite") ~ "Asian",
                          Race %in% c("Pacific Islander\r\nWhite",
                                      "White\r\nPacific Islander",
                                      "Pacific Islander\r\nI Do Not See My Race Listed Here",
                                      "American Indian or Native American",
                                      "Middle Eastern or Northern African",
                                      "Pacific Islander",
                                      "American Indian or Native American\r\nI Do Not Know",
                                      "Other\r\nI Do Not See My Race Listed Here",
                                      "I Do Not See My Race Listed Here",
                                      "I Do Not See My Race Listed Here\r\nI Do Not Know",
                                      "I Do Not Know\r\nI Do Not See My Race Listed Here",
                                      "I Do Not See My Race Listed Here\r\nI Prefer Not To Share",
                                      "White\r\nAmerican Indian or Native American",
                                      "Other") ~ "Other",
                          Race %in% c("I Do Not Know",
                                      "I Prefer Not To Share") ~ "unknown")) %>%
  # combine Asian to "Other" category
  mutate(race = ifelse(race == "Asian", "Other", race)) %>%
  mutate(race = ifelse(is.na(race), "unknown", race))

df %>% count(race) %>% 
  mutate(perc = round(n/nrow(df) * 100,1)) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```

```{r}
df %>% count(Ethnicity) %>% arrange(desc(n)) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```

#### Combine race and ethnicity into one variable: generate this new variable called "race_ethnicity" 
  * Hispanic & not black & not white ---> hispanic 
  * Hispanic & other/unknown race ---> hispanic
  * Black (any ethnicity) ---> Black 
  * white (any ethnicity) ---> white 
  * other race & not Hispanic/unknown ethnicity ---> other 
  * other race & not Hispanic/unknown ethnicity ---> unknown
```{r echo = T}
df <- df %>% 
  mutate(ethnicity = case_when(Ethnicity %in% c("Not Hispanic or Latino/a/e") ~ "Not Hispanic or Latino",
                               Ethnicity %in% c("Hispanic or Latino/a/e", 
                                                 "Puerto Rican",
                                                 "Mexican, Mexican American, Chicano/a") ~ "Hispanic or Latino",
                               Ethnicity %in% c("I Prefer Not To Share",
                                                "I Do Not Know") ~ "unknown"))

# tab the two variable 
table(df$race, df$ethnicity) 

# combine race and ethnicity
df <- df %>% 
  mutate(race_ethnicity = case_when(race == "Black" ~ "Black",
                                    race == "White" ~ "White",
                                    race %in% c("Other", "unknown") & ethnicity %in% c("Hispanic or Latino") ~ "Hispanic or Latino",
                                    race == "Other" & ethnicity %in% c("Not Hispanic or Latino", "unknown") ~ "Other",
                                    race == "unknown" & ethnicity %in% c("Not Hispanic or Latino", "unknown") ~ "unknown",
                                    TRUE ~ "unknown"))

df %>% count(race_ethnicity) %>% arrange(desc(n)) %>% mutate(perc = round(n/nrow(df)*100,1)) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```



<br>

### Table `r tab.counter`. Primary Insurance & Payor
#### Generate new variable insurance_type (TBC)
  *	Medicare / Medicaid ---> public insurance 
  *	Most others ---> private insurance 
  *	Who are considered as “uninsured”? (patients having NA for Primary Insurance and Payor variable? n = 17)
  * After discussing, made some changes to classification. I googled the Insurance and reclassified some.
Aim to use this variable to see the SES background of patients.
```{r}
tab.counter <- tab.counter + 1
df <- df %>% 
  mutate(insurance_concat = paste(`Primary Insurance`, Payor)) %>% 
  mutate(insurance_type = case_when(str_detect(insurance_concat, "MEDICAID") | str_detect(insurance_concat, "MEDICARE") ~ "public",
                                    insurance_concat == "NA NA" ~ "uninsured",
                                    TRUE ~ "private")) %>%
  select(-insurance_concat)


# update: after discussing, reclassify insurance_type for some records:
# LOCAL 1199SEIU BENEFIT FUNDS --> uninsured
# MCD MGD” (Medicare Coverage Database managed ?) are Medicare (public insurance)
df <- df %>%
  mutate(insurance_type = case_when(`Primary Insurance` == "LOCAL 1199SEIU BENEFIT FUNDS" ~ "uninsured",
                                    str_detect(`Primary Insurance`, "MCD MGD") | str_detect(Payor, "MCD MGD") ~ "public",
                                    TRUE ~ insurance_type))


df %>% count(insurance_type) %>% arrange(desc(n)) %>% rename(n_records = n) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```

<br>

### Table `r tab.counter`. Fever?
This variable displays whether the patient had a fever according to the NHSN definition (>38 C) within three days of the collection date. The information appears as a Yes or a No.
```{r}
tab.counter <- tab.counter + 1

df %>% count(`Fever?`) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```

<br>

### Table `r tab.counter`. Temp
The most recent flowsheet data for temperature. Convert to new numeric variable recent_temp. (Might not be useful as this is the "most recent" temperature, but I used this below in generating symptom variables, if recent_temp>38, I considered this record had fever symptom.)
```{r}
tab.counter <- tab.counter + 1

df <- df %>% 
  mutate(recent_temp = substring(gsub(".*°F (.+) °C.*", "\\1", Temp), 2)  ) %>% 
  mutate(recent_temp = as.numeric(recent_temp))

df %>% count(recent_temp) %>% arrange(desc(recent_temp)) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

df %>% ggplot() +
  geom_histogram(aes(x = recent_temp), color = "black", fill = "white") + theme_classic() +
  geom_vline(xintercept = 38, color = "red", linetype = "dashed")
```

<br>

### Last PCP visit (haven't processed)
### Last Well Child visit (haven't processed)
### Recent contact (haven't processed)

<br>

### Below are text patterns to detect risk factors (i.e. underlying conditions) and respiratory symptoms from the following variables:
  * Medical History (past) ---> risk factors
  * Problem List (past + current, more from past based on descriptions) ---> risk factors
  * Primary Problem (current) ---> risk factors & respiratory symptoms
  * ED Dx (current) ---> risk factors & respiratory symptoms
  * Admit Dx (current) ---> risk factors & respiratory symptoms
  * Hospital Problem List (current + past, more from current) ---> risk factors & respiratory symptoms
  
#### I detected the presence of these patterns to see if a record has certain risk factor (based on past and current encounters) or show a certain respiratory symptom in current encounter (based on diagnosis records of current encounter). The new variables generated are binary variables. For example, med_hist_congen_heart means that based on description in the "Medical History" variable, this records had congenital heart disease, which can be a risk factor for more severe outcomes.
```{r, echo = T}
######################################
# patterns for underlying risk factors
######################################

pattern_anemia <- paste(c("anemia",
                          "S-C",
                          "thalassemia",
                          "Hemoglobin S-S disease",
                          "Sickle cell",
                          "sickle-cell",
                          "Hemoglobin S trait"), 
                        collapse = "|")

pattern_blood <- paste(pattern_anemia, 
                       c("hemangioma",
                         "Thrombus of aorta",
                         "hypoglycemia"),
                       collapse = "|")

pattern_asthma <- paste(c("asthma",
                          "Reactive airway disease"),
                        collapse = "|")


pattern_liver <- paste(c("liver cell damage",
                         "Liver cell injury",
                         "liver disease",
                         "Decompensated hepatic cirrhosis",
                         "Liver transplanted"), 
                       collapse = "|")

pattern_immunodeficiency <- paste(c("liver transplanted",
                                    "transplant",
                                    "leukemia"),
                                  collapse = "|")

pattern_cvd <- paste(c("Atrial septa",
                       "ventricular septa",
                 "Patent ductus arteriosus",
                 "Cardiac abnormality",
                 "Cardiac hypertrophy", # added 
                 "cardiac septal defect", # added 
                 "fetal cardiac arrhythmia", # added
                 "Cardiac dysfunction", # added
                 "cardiac arrest", # added 
                 "Stenosis of right pulmonary artery", # added
                 "Stenosis of left pulmonary artery", # added
                 "Stenosis of pulmonary artery", # added
                 "Cardiac abnormality", # added
                 "cardiac surgery", # added
                 "cardiac valve disease", # added 
                 "Cardiac anomaly", # added 
                 "Congenital heart disease",
                 "Partial AV canal",
                 "Ventricular septa",
                 "Coarctation of aorta",
                 "double outlet right ventricle",
                 "Dextrocardia",
                 "DORV",
                 # "Heart murmur",
                 # "Heart murmur of newborn",
                 # "murmur",
                 "heart problem",
                 "Mitral regurgitation",
                 "Kawasaki disease",
                 "Coarctation of aorta",
                 # "hemangioma", # moved to blood group
                 "atrial septal defect",
                 # "Thrombus of aorta", # moved to blood group
                 "premature atrial contraction",
                 "Cardiomegaly",
                 "Myocarditis",
                 "supraventricular tachycardia",
                 "Tetralogy of Fallot",
                 "Atrioventricular canal (AVC), complete",
                 "Heart failure",
                 "Aortic arch anomaly",
                 "supraventricular tachycardia",
                 "aortic coarctation",
                 "Enlarged heart"),
                 collapse = "|")


# pattern_leukemia <- "leukemia" # combined with immunodeficiency group


pattern_gi <- paste(c(
                      # "Abdominal distension",
                      # "Acid reflux",
                      # "gastroesophageal reflux",
                      "GI disease",
                      # "Constipation",
                      "Esophageal atresia",
                      "Gastric perforation",
                      # "Gastric reflux",
                      "Hirschsprung",
                      # "GERD",
                      "Colostomy",
                      "necrotizing enterocolitis",
                      "Intestinal perforation",
                      "Intussusception",
                      "Biliary atresia",
                      "Ileostomy",
                      # "esophageal reflux",
                      "Pyloric stenosis",
                      # "Reflux gastritis",
                      "Gastric bleed",
                      "GI bleed",
                      "gastritis"),
                    collapse = "|")


pattern_congen_heart <- paste(c("Congenital heart disease",
                                "Coarctation of aorta",
                                "Congenital heart",
                                "D-TGA",
                                "double outlet right ventricle",
                                "Dextrocardia",
                                "DORV",
                                "Cardiac abnormality",
                                "ventricular septa",
                                "Mitral regurgitation",
                                "Coarctation of aorta",
                                "Hypoplastic aortic arch",
                                "atrial septal defect",
                                # "Thrombus of aorta", # moved to blood group
                                "Heart abnormality",
                                "Cardiomegaly",
                                "patent ductus arteriosus",
                                "Tetralogy of Fallot",
                                "Atrioventricular canal (AVC), complete",
                                "persistent left superior vena cava",
                                "Aortic arch anomaly",
                                "Wolff-Parkinson-White (WPW) syndrome",
                                "supraventricular tachycardia",
                                "Partial AV canal",
                                "Atrial septa",
                                # "Heart murmur of newborn",
                                "supraventricular tachycardia",
                                "Partial anomalous pulmonary venous return",
                                "aortic coarctation",
                                "Congenital coronary artery fistula to pulmonary artery",
                                "Peripheral pulmonic stenosis",
                                "Tricuspid atresia with normal great arteries"),
                              collapse = "|")

pattern_cardiac <- paste(pattern_cvd, 
                         pattern_congen_heart,
                         c("Pulmonary valve atresia",
                           "Partial anomalous pulmonary venous return",
                           "pulmonary artery stenosis",
                           "pulmonary artery",
                           "Peripheral pulmonic stenosis",
                           "Pulmonary valve stenosis",
                           "Pulmonary hypertension"),
                         collapse = "|")


pattern_pulmonary <- paste(c(
                             # "Pulmonary valve atresia", # moved to cardiac
                             # "Chronic cough",
                             "CPAM",
                             "Cystic fibrosis",
                             "Bronchopulmonary dysplasia",
                             "Protracted bacterial bronchitis",
                             "reactive airway disease",
                             "Pneumothorax",
                             #"Pulmonary hypertension",
                             #"Pulmonary valve stenosis",
                             "Bronchomalacia",
                             "Tracheomalacia"
                             # "Partial anomalous pulmonary venous return", 
                             # "pulmonary artery stenosis",
                             # "pulmonary artery",
                             # "Peripheral pulmonic stenosis"
                             ),
                           collapse = "|")

pattern_down <- paste(c("Down syndrome",
                        "Trisomy 21"),
                      collapse = "|")

# 37-38 weeks 
pattern_earlyterm <- paste(c("37 completed weeks",
                             "38 completed weeks",
                             "37 weeks gestation",
                             "38 weeks gestation"),
                           collapse = "|")

# 39-40 weeks
pattern_fullterm <- paste(c("39 completed weeks",
                            "39 weeks gestation",
                            "Term newborn",
                            "Term birth",
                            "40 completed weeks",
                            "40 weeks gestation"),
                          collapse = "|")

# < 37 weeks
pattern_preterm <- paste(c("Premature",
                           "prematurity",
                           "Extremely low birth weight",
                           "Preterm",
                           "36 weeks gestation",
                           "36 completed weeks",
                           "preterm newborn",
                           "preterm birth",
                           "33-34 completed weeks",
                           "29-30 completed weeks",
                           "35-36 completed weeks",
                           "34 completed weeks",
                           "35 completed weeks",
                           "22 weeks gestation"),
                         collapse = "|")

# >= 42 weeks
pattern_postterm <- paste(c("post-term",
                            "post term"),
                          collapse = "|")



######################################
# patterns for respiratory symptoms
######################################

# for upper respiratory tract diseases 
pattern_URTI <- paste(c("Abnormal breathing",
                        "Breathing difficulty",
                        "difficulty breathing",
                        "breathing problem",
                        "Shortness of breath",
                        "cough",
                        "Acute obstructive laryngitis",
                        "pharyngitis",
                        "otitis media",
                        "upper respiratory infection",
                        "upper respiratory tract infection",
                        "upper resp. tract infection",
                        "upper resp. infection",
                        "croup",
                        "Nasopharyngitis",
                        "Pain in throat",
                        "reactive airway disease",
                        "Nasal congestion",
                        # "wheezing", # moved to LRT
                        "sore throat",
                        "URI",
                        "Laryngeal stridor"), 
                      collapse = "|")

# for lower respiratory tract diseases:
pattern_LRTI <- paste(c("bronchiolitis",
                        "Laryngotracheobronchitis",
                        "Bronchospasm",
                        "Acute chest syndrome",
                        "Acute hypoxic respiratory failure",
                        "Pneumonia",
                        "Hypoxia",
                        "Hypoxemia",
                        "Lower resp. tract infection",
                        "Lower resp. infection",
                        "Lower respiratory tract infection",
                        "Lower respiratory infection",
                        "Hypoxemic respiratory failure",
                        "Acute respiratory failure with hypoxia",
                        "wheezing"), 
                      collapse = "|")


pattern_fever <- "fever|febrile"

pattern_cough <- "cough"

pattern_wheezing <- "wheezing"

pattern_breathing <- paste(c("Abnormal breathing",
                             "Breathing difficulty",
                             "difficulty breathing",
                             "Shortness of breath",
                             "breathing problem",
                             "apnea"), 
                           collapse = "|")

pattern_bronchiolitis <- "bronchiolitis|Bronchospasm"

pattern_sepsis <- "sepsis"

# pattern_apnea <- "apnea"

# some general terms used to detect if the record's encounter is suspcted resp infection
pattern_suspect_resp_general <- paste(c("respiratory",
                                        "RSV",
                                        "syncytial",
                                        "viral infection",
                                        "covid",
                                        "influenza", 
                                        "flu",
                                        "viral illness",
                                        "Viral syndrome",
                                        "nasal"
                                        #"asthma",
                                        #"decreased activity"
                                        ), 
                                      collapse = "|")
```


```{r}
##########################
### Medical History (past)
##########################

# extract risk factors and underlying conditions from `Medical History`
df <- df %>%
  mutate(med_hist_anemia = case_when(grepl(pattern_anemia, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_blood = case_when(grepl(pattern_blood, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_preterm = case_when(grepl(pattern_preterm, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_postterm = case_when(grepl(pattern_postterm, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_asthma = case_when(grepl(pattern_asthma, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_liver = case_when(grepl(pattern_liver, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_cvd = case_when(grepl(pattern_cvd, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_immunodeficiency = case_when(grepl(pattern_immunodeficiency, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_gi = case_when(grepl(pattern_gi, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_congen_heart = case_when(grepl(pattern_congen_heart, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_cardiac = case_when(grepl(pattern_cardiac, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_pulmonary = case_when(grepl(pattern_pulmonary, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_down = case_when(grepl(pattern_down, `Medical History`, ignore.case = T) ~ 1))  %>%
  mutate(med_hist_cvd = ifelse(med_hist_congen_heart == 1 & is.na(med_hist_cvd), 1, med_hist_cvd)) %>%
  mutate(med_hist_earlyterm = case_when(grepl(pattern_earlyterm, `Medical History`, ignore.case = T) ~ 1)) %>%
  mutate(med_hist_fullterm = case_when(grepl(pattern_fullterm, `Medical History`, ignore.case = T)  & 
                                           !grepl(pattern_preterm, `Medical History`, ignore.case = T) ~ 1))
  

```

```{r}
##########################
### Problem List (past+current, more from past)
##########################

# extract risk factors and underlying conditions from `Problem List`

df <- df %>%
  mutate(prob_list_anemia = case_when(grepl(pattern_anemia, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_blood = case_when(grepl(pattern_blood, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_preterm = case_when(grepl(pattern_preterm, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_postterm = case_when(grepl(pattern_postterm, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_asthma = case_when(grepl(pattern_asthma, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_liver = case_when(grepl(pattern_liver, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_cvd = case_when(grepl(pattern_cvd, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_immunodeficiency = case_when(grepl(pattern_immunodeficiency, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_gi = case_when(grepl(pattern_gi, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_congen_heart = case_when(grepl(pattern_congen_heart, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_cardiac = case_when(grepl(pattern_cardiac, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_pulmonary = case_when(grepl(pattern_pulmonary, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_down = case_when(grepl(pattern_down, `Problem List`, ignore.case = T) ~ 1))  %>%
  mutate(prob_list_cvd = ifelse(prob_list_congen_heart == 1 & is.na(prob_list_cvd), 1, prob_list_cvd)) %>%
  mutate(prob_list_earlyterm = case_when(grepl(pattern_earlyterm, `Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(prob_list_fullterm = case_when(grepl(pattern_fullterm, `Problem List`, ignore.case = T)  & 
                                           !grepl(pattern_preterm, `Problem List`, ignore.case = T) ~ 1))
```

```{r}
##################################
### Primary Problem (current)
##################################

# extract risk factors and underlying conditions from `Primary Problem`
df <- df %>%
  mutate(prim_prob_anemia = case_when(grepl(pattern_anemia, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_blood = case_when(grepl(pattern_blood, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_preterm = case_when(grepl(pattern_preterm, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_postterm = case_when(grepl(pattern_postterm, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_asthma = case_when(grepl(pattern_asthma, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_liver = case_when(grepl(pattern_liver, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_cvd = case_when(grepl(pattern_cvd, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_immunodeficiency = case_when(grepl(pattern_immunodeficiency, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_gi = case_when(grepl(pattern_gi, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_congen_heart = case_when(grepl(pattern_congen_heart, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_cardiac = case_when(grepl(pattern_cardiac, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_pulmonary = case_when(grepl(pattern_pulmonary, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_down = case_when(grepl(pattern_down, `Primary Problem`, ignore.case = T) ~ 1))  %>%
  mutate(prim_prob_cvd = ifelse(prim_prob_congen_heart == 1 & is.na(prim_prob_cvd), 1, prim_prob_cvd)) %>%
  mutate(prim_prob_earlyterm = case_when(grepl(pattern_earlyterm, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_fullterm = case_when(grepl(pattern_fullterm, `Primary Problem`, ignore.case = T)  & 
                                           !grepl(pattern_preterm, `Primary Problem`, ignore.case = T) ~ 1))
  

# extract conditions related to respiratory infection
df <- df %>% 
  mutate(prim_prob_URTI = case_when(grepl(pattern_URTI, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_LRTI = case_when(grepl(pattern_LRTI, `Primary Problem`, ignore.case = T) ~ 1)) %>% 
  mutate(prim_prob_fever = case_when(grepl(pattern_fever, `Primary Problem`, ignore.case = T) | `Fever?` == "Yes" | recent_temp >= 38 ~ 1)) %>%
  mutate(prim_prob_cough = case_when(grepl(pattern_cough, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_wheezing = case_when(grepl(pattern_wheezing, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_breathing = case_when(grepl(pattern_breathing, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_bronchiolitis = case_when(grepl(pattern_bronchiolitis, `Primary Problem`, ignore.case = T) ~ 1)) %>%
  mutate(prim_prob_sepsis = case_when(grepl(pattern_sepsis, `Primary Problem`, ignore.case = T) ~ 1))
  # if a record has LRTI and URTI at the same time, record this as LRTI
  # mutate(prim_prob_URTI = case_when(prim_prob_URTI == 1 & is.na(prim_prob_LRTI) ~ 1))
```

```{r}
############################
### ED Dx (current)
############################

# extract risk factors and underlying conditions from ED Dx 
df <- df %>%
  mutate(ED_dx_anemia = case_when(grepl(pattern_anemia, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_blood = case_when(grepl(pattern_blood, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_preterm = case_when(grepl(pattern_preterm, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_postterm = case_when(grepl(pattern_postterm, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_asthma = case_when(grepl(pattern_asthma, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_liver = case_when(grepl(pattern_liver, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_cvd = case_when(grepl(pattern_cvd, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_immunodeficiency = case_when(grepl(pattern_immunodeficiency, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_gi = case_when(grepl(pattern_gi, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_congen_heart = case_when(grepl(pattern_congen_heart, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_cardiac = case_when(grepl(pattern_cardiac, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_pulmonary = case_when(grepl(pattern_pulmonary, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_down = case_when(grepl(pattern_down, `ED Dx`, ignore.case = T) ~ 1))  %>%
  mutate(ED_dx_cvd = ifelse(ED_dx_congen_heart == 1 & is.na(ED_dx_cvd), 1, ED_dx_cvd)) %>%
  mutate(ED_dx_earlyterm = case_when(grepl(pattern_earlyterm, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_fullterm = case_when(grepl(pattern_fullterm, `ED Dx`, ignore.case = T)  & 
                                           !grepl(pattern_preterm, `ED Dx`, ignore.case = T) ~ 1))


# extract conditions related to respiratory infection
df <- df %>% 
  mutate(ED_dx_URTI = case_when(grepl(pattern_URTI, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_LRTI = case_when(grepl(pattern_LRTI, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_fever = case_when(grepl(pattern_fever, `ED Dx`, ignore.case = T) | 
                                   `Fever?` == "Yes" | recent_temp >= 38 ~ 1)) %>%
  mutate(ED_dx_cough = case_when(grepl(pattern_cough, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_wheezing = case_when(grepl(pattern_wheezing, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_breathing = case_when(grepl(pattern_breathing, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_bronchiolitis = case_when(grepl(pattern_bronchiolitis, `ED Dx`, ignore.case = T) ~ 1)) %>%
  mutate(ED_dx_sepsis = case_when(grepl(pattern_sepsis, `ED Dx`, ignore.case = T) ~ 1))
  # if a record has LRTI and URTI at the same time, record this as LRTI
  # mutate(ED_dx_URTI = case_when(ED_dx_URTI == 1 & is.na(ED_dx_LRTI) ~ 1))
  
```

```{r}
############################
### Admit Dx (current)
############################

# extract risk factors and underlying conditions from Admit Dx
df <- df %>% 
  mutate(admit_dx_anemia = case_when(grepl(pattern_anemia, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_blood = case_when(grepl(pattern_blood, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_preterm = case_when(grepl(pattern_preterm, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_postterm = case_when(grepl(pattern_postterm, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_asthma = case_when(grepl(pattern_asthma, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_liver = case_when(grepl(pattern_liver, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_cvd = case_when(grepl(pattern_cvd, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_immunodeficiency = case_when(grepl(pattern_immunodeficiency, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_gi = case_when(grepl(pattern_gi, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_congen_heart = case_when(grepl(pattern_congen_heart, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_cardiac = case_when(grepl(pattern_cardiac, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_pulmonary = case_when(grepl(pattern_pulmonary, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_down = case_when(grepl(pattern_down, `Admit Dx`, ignore.case = T) ~ 1))  %>%
  mutate(admit_dx_cvd = ifelse(admit_dx_congen_heart == 1 & is.na(admit_dx_cvd), 1, admit_dx_cvd)) %>%
  mutate(admit_dx_earlyterm = case_when(grepl(pattern_earlyterm, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_fullterm = case_when(grepl(pattern_fullterm, `Admit Dx`, ignore.case = T)  & 
                                           !grepl(pattern_preterm, `Admit Dx`, ignore.case = T) ~ 1))

# extract conditions related to respiratory infection 
df <- df %>% 
  mutate(admit_dx_URTI = case_when(grepl(pattern_URTI, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_LRTI = case_when(grepl(pattern_LRTI, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_fever = case_when(grepl(pattern_fever, `Admit Dx`, ignore.case = T) | 
                                      `Fever?` == "Yes" | recent_temp >= 38 ~ 1)) %>%
  mutate(admit_dx_cough = case_when(grepl(pattern_cough, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_wheezing = case_when(grepl(pattern_wheezing, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_breathing = case_when(grepl(pattern_breathing, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_bronchiolitis = case_when(grepl(pattern_bronchiolitis, `Admit Dx`, ignore.case = T) ~ 1)) %>%
  mutate(admit_dx_sepsis = case_when(grepl(pattern_sepsis, `Admit Dx`, ignore.case = T) ~ 1))
  # if a record has LRTI and URTI at the same time, record this as LRTI
  # mutate(admit_dx_URTI = case_when(admit_dx_URTI == 1 & is.na(admit_dx_LRTI) ~ 1))
```

```{r}
#########################################
### Hospital Problem List (current+past,more from current)
########################################

# extract risk factors and underlying conditions from Admit Dx
df <- df %>% 
  mutate(hosp_prob_anemia = case_when(grepl(pattern_anemia, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_blood = case_when(grepl(pattern_blood, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_preterm = case_when(grepl(pattern_preterm, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_postterm = case_when(grepl(pattern_postterm, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_asthma = case_when(grepl(pattern_asthma, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_liver = case_when(grepl(pattern_liver, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_cvd = case_when(grepl(pattern_cvd, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_immunodeficiency = case_when(grepl(pattern_immunodeficiency, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_gi = case_when(grepl(pattern_gi, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_congen_heart = case_when(grepl(pattern_congen_heart, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_cardiac = case_when(grepl(pattern_cardiac, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_pulmonary = case_when(grepl(pattern_pulmonary, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_down = case_when(grepl(pattern_down, `Hospital Problem List`, ignore.case = T) ~ 1))  %>%
  mutate(hosp_prob_cvd = ifelse(hosp_prob_congen_heart == 1 & is.na(hosp_prob_cvd), 1, hosp_prob_cvd)) %>%
  mutate(hosp_prob_earlyterm = case_when(grepl(pattern_earlyterm, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_fullterm = case_when(grepl(pattern_fullterm, `Hospital Problem List`, ignore.case = T)  & 
                                           !grepl(pattern_preterm, `Hospital Problem List`, ignore.case = T) ~ 1))


# extract conditions related to respiratory infection
df <- df %>% 
  mutate(hosp_prob_URTI = case_when(grepl(pattern_URTI, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_LRTI = case_when(grepl(pattern_LRTI, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_fever = case_when(grepl(pattern_fever, `Hospital Problem List`, ignore.case = T) | 
                                       `Fever?` == "Yes" | recent_temp >= 38 ~ 1)) %>%
  mutate(hosp_prob_cough = case_when(grepl(pattern_cough, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_wheezing = case_when(grepl(pattern_wheezing, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_breathing = case_when(grepl(pattern_breathing, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_bronchiolitis = case_when(grepl(pattern_bronchiolitis, `Hospital Problem List`, ignore.case = T) ~ 1)) %>%
  mutate(hosp_prob_sepsis = case_when(grepl(pattern_sepsis, `Hospital Problem List`, ignore.case = T) ~ 1))
  # if a record has LRTI and URTI at the same time, record this as LRTI
  # mutate(hosp_prob_URTI = case_when(hosp_prob_URTI == 1 & is.na(hosp_prob_LRTI) ~ 1))

```

#### From the generated binary variables 
  * med_hist_xx
  * prob_list_xx
  * prim_prob_xx
  * ED_dx_xx
  * Admit_dx_xx
  * hosp_prob_xx
  
#### generate new binary variables: **risk_factor_xx** indicating whether this record has certain risk factor.
```{r}
df <- df %>% 
  mutate(risk_factor_anemia = case_when(med_hist_anemia == 1 | prob_list_anemia == 1 | prim_prob_anemia == 1 | 
                                          ED_dx_anemia == 1 | admit_dx_anemia == 1 | hosp_prob_anemia == 1 ~ 1)) %>%
  mutate(risk_factor_blood = case_when(med_hist_blood == 1 | prob_list_blood == 1 | prim_prob_blood == 1 | 
                                          ED_dx_blood == 1 | admit_dx_blood == 1 | hosp_prob_blood == 1 ~ 1)) %>%
  mutate(risk_factor_asthma = case_when(med_hist_asthma == 1 | prob_list_asthma == 1 | prim_prob_asthma == 1 | 
                                          ED_dx_asthma == 1 | admit_dx_asthma == 1 | hosp_prob_asthma == 1 ~ 1)) %>%
  mutate(risk_factor_liver = case_when(med_hist_liver == 1 | prob_list_liver == 1 | prim_prob_liver == 1 | 
                                          ED_dx_liver == 1 | admit_dx_liver == 1 | hosp_prob_liver == 1 ~ 1)) %>%
  mutate(risk_factor_cvd = case_when(med_hist_cvd == 1 | prob_list_cvd == 1 | prim_prob_cvd == 1 | 
                                          ED_dx_cvd == 1 | admit_dx_cvd == 1 | hosp_prob_cvd == 1 ~ 1)) %>%
  mutate(risk_factor_immunodeficiency = case_when(med_hist_immunodeficiency == 1 | prob_list_immunodeficiency == 1 | prim_prob_immunodeficiency == 1 | 
                                          ED_dx_immunodeficiency == 1 | admit_dx_immunodeficiency == 1 | hosp_prob_immunodeficiency == 1 ~ 1)) %>%
  mutate(risk_factor_gi = case_when(med_hist_gi == 1 | prob_list_gi == 1 | prim_prob_gi == 1 | 
                                          ED_dx_gi == 1 | admit_dx_gi == 1 | hosp_prob_gi == 1 ~ 1)) %>%
  mutate(risk_factor_congen_heart = case_when(med_hist_congen_heart == 1 | prob_list_congen_heart == 1 | prim_prob_congen_heart == 1 | 
                                          ED_dx_congen_heart == 1 | admit_dx_congen_heart == 1 | hosp_prob_congen_heart == 1 ~ 1)) %>%
  mutate(risk_factor_cardiac = case_when(med_hist_cardiac == 1 | prob_list_cardiac == 1 | prim_prob_cardiac == 1 | 
                                          ED_dx_cardiac == 1 | admit_dx_cardiac == 1 | hosp_prob_cardiac == 1 ~ 1)) %>%
  mutate(risk_factor_pulmonary = case_when(med_hist_pulmonary == 1 | prob_list_pulmonary == 1 | prim_prob_pulmonary == 1 | 
                                          ED_dx_pulmonary == 1 | admit_dx_pulmonary == 1 | hosp_prob_pulmonary == 1 ~ 1)) %>%
  mutate(risk_factor_down = case_when(med_hist_down == 1 | prob_list_down == 1 | prim_prob_down == 1 | 
                                          ED_dx_down == 1 | admit_dx_down == 1 | hosp_prob_down == 1 ~ 1)) %>%
  mutate(risk_factor_earlyterm = case_when(med_hist_earlyterm == 1 | prob_list_earlyterm == 1 | prim_prob_earlyterm == 1 | 
                                          ED_dx_earlyterm == 1 | admit_dx_earlyterm == 1 | hosp_prob_earlyterm == 1 | 
                                            gest_age_cat == "early term" ~ 1)) %>%
  mutate(risk_factor_fullterm = case_when(med_hist_fullterm == 1 | prob_list_fullterm == 1 | prim_prob_fullterm == 1 | 
                                          ED_dx_fullterm == 1 | admit_dx_fullterm == 1 | hosp_prob_fullterm == 1 | 
                                            gest_age_cat == "full term"  ~ 1)) %>%
  mutate(risk_factor_preterm = case_when(med_hist_preterm == 1 | prob_list_preterm == 1 | prim_prob_preterm == 1 | 
                                          ED_dx_preterm == 1 | admit_dx_preterm == 1 | hosp_prob_preterm == 1 | 
                                           gest_age_cat == "preterm" ~ 1)) %>%
  mutate(risk_factor_postterm = case_when(med_hist_postterm == 1 | prob_list_postterm == 1 | prim_prob_postterm == 1 | 
                                          ED_dx_postterm == 1 | admit_dx_postterm == 1 | hosp_prob_postterm == 1 | 
                                            gest_age_cat == "post term" ~ 1)) 

```

<br>

#### From generated binary varibles 
  * prim_prob_xx
  * ED_dx_xx
  * Admit_dx_xx
  * hosp_prob_xx
  
#### generate new binary variables **(symp_xxx)** indicating whether this record has certain respiratory symptoms at this encounter.
```{r}
df <- df %>% 
  mutate(symp_URT_distress = case_when(prim_prob_URTI == 1 | ED_dx_URTI == 1 | admit_dx_URTI == 1 | hosp_prob_URTI == 1 ~ 1)) %>% 
  mutate(symp_LRT_distress = case_when(prim_prob_LRTI == 1 | ED_dx_LRTI == 1 | admit_dx_LRTI == 1 | hosp_prob_LRTI == 1 ~ 1)) %>%
  mutate(symp_fever = case_when(prim_prob_fever == 1 | ED_dx_fever == 1 | admit_dx_fever == 1 | hosp_prob_fever == 1 ~ 1)) %>%
  mutate(symp_cough = case_when(prim_prob_cough == 1 | ED_dx_cough == 1 | admit_dx_cough == 1 | hosp_prob_cough == 1 ~ 1)) %>%
  mutate(symp_wheezing = case_when(prim_prob_wheezing == 1 | ED_dx_wheezing == 1 | admit_dx_wheezing == 1 | hosp_prob_wheezing == 1 ~ 1)) %>%
  mutate(symp_breathing = case_when(prim_prob_breathing == 1 | ED_dx_breathing == 1 | admit_dx_breathing == 1 | hosp_prob_breathing == 1 ~ 1)) %>%
  mutate(symp_bronchiolitis = case_when(prim_prob_bronchiolitis == 1 | ED_dx_bronchiolitis == 1 | admit_dx_bronchiolitis == 1 | hosp_prob_bronchiolitis == 1 ~ 1)) %>%
  mutate(symp_sepsis = case_when(prim_prob_sepsis == 1 | ED_dx_sepsis == 1 | admit_dx_sepsis == 1 | hosp_prob_sepsis == 1 ~ 1)) 
```

<br>

### Table `r tab.counter`. There are some records that no patterns of respiratory symptoms (above patterns) can be detected 
#### (Should they be considered suspected respiratory/RSV infections and included in the study population? TBC)
```{r}
tab.counter <- tab.counter + 1

df.uncertain <- df %>% filter(is.na(symp_URT_distress) & is.na(symp_LRT_distress) & is.na(symp_fever) & is.na(symp_cough) & is.na(symp_wheezing) & is.na(symp_breathing) & is.na(symp_bronchiolitis) & is.na(symp_sepsis) &
                     grepl(pattern_suspect_resp_general, `Primary Problem`,ignore.case = T) %in% c(NA, FALSE)  & 
                     grepl(pattern_suspect_resp_general, `ED Dx`, ignore.case = T) %in% c(NA, FALSE) & 
                     grepl(pattern_suspect_resp_general, `Admit Dx`,ignore.case = T) %in% c(NA, FALSE) & 
                     grepl(pattern_suspect_resp_general, `Hospital Problem List`,ignore.case = T) %in% c(NA, FALSE)                   )

df.uncertain %>%
  select(StudyID, `Primary Problem`, `ED Dx`, `Admit Dx`, `Hospital Problem List`) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"),
            columns = list(
            `ED Dx` = colDef(width = 300),
            `Admit Dx` = colDef(width = 300),
            `Hospital Problem List` = colDef(width = 300)
            ))

```

<br>


### Table `r tab.counter`. Summarize extracted risk factors 
Each record can have multiple risk factors. For gestational age (preterm...), I also used the information in gest_age_cat to classify if this record is preterm/early term, etc.
```{r}
tab.counter <- tab.counter + 1

data.frame(
  anemia = nrow(df %>% filter(risk_factor_anemia == 1)),
  blood = nrow(df %>% filter(risk_factor_blood == 1)),
  asthma = nrow(df %>% filter(risk_factor_asthma == 1)),
  liver_disease = nrow(df %>% filter(risk_factor_liver == 1)),
  cvd = nrow(df %>% filter(risk_factor_cvd == 1)),
  immunodeficiency = nrow(df %>% filter(risk_factor_immunodeficiency == 1)),
  GI_disease = nrow(df %>% filter(risk_factor_gi == 1)),
  congenital_heart_disease = nrow(df %>% filter(risk_factor_congen_heart == 1)),
  cardiac = nrow(df %>% filter(risk_factor_cardiac == 1)),
  pulmonary_disease = nrow(df %>% filter(risk_factor_pulmonary == 1)),
  down_syndrome = nrow(df %>% filter(risk_factor_down == 1)),
  early_term = nrow(df %>% filter(risk_factor_earlyterm == 1)),
  full_term = nrow(df %>% filter(risk_factor_fullterm == 1)),
  preterm = nrow(df %>% filter(risk_factor_preterm == 1)),
  post_term = nrow(df %>% filter(risk_factor_postterm == 1))
) %>%
  pivot_longer(cols = 1:15, names_to = "risk_factor", values_to = "n_records") %>%
  arrange(desc(n_records)) %>%
  mutate(perc = round(n_records / nrow(df)*100,1)) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

```

<br>

### Table `r tab.counter`. Some more processing of gestational age 
#### From
  * gest_age_cat (original variable in the dataset);
  * risk_factor_fullterm, risk_factor_earlyterm, risk_factor_preterm, risk_factor_postterm (extracted from medical history..)
```{r}
tab.counter <- tab.counter + 1
# As some information about gestational age was extracted from medical history, there might be some inaccuracy, here first detect if there is individuals who was marked 1 in both cats. 
df <- df %>% 
  mutate(risk_factor_gestage = case_when(
    !is.na(gest_age_cat) ~ gest_age_cat,
    is.na(gest_age_cat) & risk_factor_earlyterm == 1 ~ "early term",
    is.na(gest_age_cat) & risk_factor_fullterm == 1 ~ "full term",
    is.na(gest_age_cat) & risk_factor_postterm == 1 ~ "post term",
    is.na(gest_age_cat) & risk_factor_preterm == 1 ~ "preterm"
  )) 

df %>% count(risk_factor_gestage) %>% arrange(desc(n)) %>% 
  mutate(perc = round(n / nrow(df)*100,1)) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

# a <- df %>% filter(is.na(risk_factor_gestage)) 
# write.csv(a, "../../data/missing_gestage.csv", row.names = F)
```

<br>

### Table `r tab.counter`. Summarize extracted respiratory symptoms
Each record can have multiple symptoms.
```{r}
tab.counter <- tab.counter + 1

data.frame(
  symp_URT_distress = nrow(df %>% filter(symp_URT_distress == 1)),
  symp_LRT_distress = nrow(df %>% filter(symp_LRT_distress == 1)), 
  symp_fever = nrow(df %>% filter(symp_fever == 1)),
  symp_cough = nrow(df %>% filter(symp_cough == 1)),
  symp_wheezing = nrow(df %>% filter(symp_wheezing == 1)),
  symp_breathing = nrow(df %>% filter(symp_breathing == 1)),
  symp_bronchiolitis = nrow(df %>% filter(symp_bronchiolitis == 1)),
  symp_sepsis = nrow(df %>% filter(symp_sepsis == 1))
) %>%
  pivot_longer(cols = 1:8, names_to = "symp", values_to = "n_records") %>%
  arrange(desc(n_records)) %>%
  mutate(perc = round(n_records / nrow(df)*100,1)) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))

```

<br>

### Table `r tab.counter`. There are records missing diagnosis details:
#### aka. records that are missing for all following variables:
  * Primary Problem
  * ED Dx
  * Admit Dx
  * Hospital Problem List

This table is a subset of table 20 above. (all records here are from outpatient) For these records we can't be sure these are hospitalizations related to respiratory infection.
```{r}
tab.counter <- tab.counter + 1

df %>% filter(is.na(`ED Dx`) & is.na(`Admit Dx`) & is.na(`Primary Problem`) & is.na(`Hospital Problem List`)) %>%
  filter(`Fever?` == "No" & recent_temp <= 38) %>%
  select(StudyID, `Fever?`, recent_temp, `Medical History`, `Problem List`
         , icu_admitted_related, encounter_type
         # `Primary Problem`, `ED Dx`, `Admit Dx`, `Hospital Problem List`
         ) %>% 
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"),
            columns = list(
    `Medical History` = colDef(width = 500),
    `Problem List` = colDef(width = 600))
    )
```
<br>

### Mom RSV vax
Generate binary variable mom_rsv_vaxed to indicate the infant's mother was vaccinated
```{r}
df <- df %>% 
  mutate(mom_rsv_vaxed = ifelse(!is.na(`Mom RSV vax`), 1, NA)) %>% 
  mutate(mom_rsv_vaxed_date = as.Date(`Mom RSV vax date`))

n_temp <- df %>% filter(mom_rsv_vaxed == 1) %>% nrow()
```

There are `r n_temp` records whose mom received RSV maternal vaccine. (self report)

<br>


### Read in Nirsevimab tab from excel
This tab contains nirsevimab information, if there is discordance between the main tab and this tab about the nirsevimab, use this tab's information. (There is no duplicate in the nirsevimab tab).
```{r}
df.nir <- read_excel("/Users/hmx/OneDrive - Yale University/Hanmeng RSV VE/data/RSV_deid_2024_may.xlsx", sheet = "nirsevimab")

# merge nirsevimab tab with main tab 
df <- df %>% select(-`mAb Date`, - Nirsevimab) %>% 
  left_join(df.nir %>% select(-`IMM Entry Date`), by = "StudyID")
```

### Figure `r fig.counter`. See how many mAb were administered after sample collection
#### Generate new variable days_btw_mab_collection (mAb date - collection date), >0 means immunization after sample collection.
(days_btw_mab_collection can be used to see how protection from mAb wanes over time.)
```{r}
fig.counter <- fig.counter + 1

df <- df %>% 
  mutate(mab_date = as.Date(`mAb date`)) %>%
  mutate(days_btw_mab_collection = as.numeric(as.Date(`mAb date`) - collection_date)) 

df %>% 
  filter(!is.na(days_btw_mab_collection)) %>%
  select(StudyID, collection_date, mab_date, days_btw_mab_collection) %>%
  ggplot() + 
  geom_histogram(aes(x = days_btw_mab_collection), color = "black", fill ="white") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed") +
  xlab("days_btw_mab_collection\n (Date of mAb - date of collection)") + theme_classic() +
  annotate("text", x = 50, y = 45 , label = "---> mAb immunization \nAFTER sample collection", color = "red")
```

### Those who received mAb within 7 days before sample collection OR received on/after date of collection:
#### (TBC) how do we define exposure? those who are immunized with mAb before sample collection date or those who are immunized >7 days before sample collection date?
```{r}
df %>% 
  filter(!is.na(days_btw_mab_collection)) %>%
  filter(days_btw_mab_collection >= -7) %>%
  arrange(days_btw_mab_collection) %>%
  select(StudyID,  days_btw_mab_collection,mab_date, collection_date) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px")) 
  
```


<br>

### Table `r tab.counter`. Nirsevimab status
#### Generated new categorical variables rsv_mab_detailed, to have values of 
  * 50mg before collection (days_btw_mab_collection < 0)
  * 100mg before collection (days_btw_mab_collection < 0)
  * 50mg after collection (days_btw_mab_collection >= 0)
  * 100mg after collection (days_btw_mab_collection >= 0)
  * no mAb recorded but with last hepB vax recorded
  * no mAb recorded and no last hepB vax recorded
  
```{r}
df <- df %>% 
  mutate(rsv_mab_detailed = case_when(`Nirsevimab info` == "RSV, MAB, NIRSEVIMAB-ALIP, 50 MG/0.5 ML, FOR PATIENTS < 5 KG [306]" & 
                              days_btw_mab_collection < 0 ~  "50mg before collection",
                             `Nirsevimab info` == "RSV, MAB, NIRSEVIMAB-ALIP, 100 MG/ML, FOR PATIENTS >= 5 KG [307]" &
                              days_btw_mab_collection < 0 ~ "100mg before collection",
                             `Nirsevimab info` == "RSV, MAB, NIRSEVIMAB-ALIP, 50 MG/0.5 ML, FOR PATIENTS < 5 KG [306]" & 
                              days_btw_mab_collection >= 0 ~  "50mg after collection",
                             `Nirsevimab info` == "RSV, MAB, NIRSEVIMAB-ALIP, 100 MG/ML, FOR PATIENTS >= 5 KG [307]" &
                              days_btw_mab_collection >= 0 ~ "100mg after collection",
                             is.na(`Nirsevimab info`) & !is.na(`Hep B Imm Last Given`) ~ "no mAb recorded but with last hepB vax recorded",
                             is.na(`Nirsevimab info`) & is.na(`Hep B Imm Last Given`) ~ "no mAb recorded and no last hepB vax recorded"))

df %>% count(rsv_mab_detailed) %>% rename(n_records = n) %>%
  mutate(perc = round(n_records/nrow(df)*100,1)) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```

#### Generated new binary variable rsv_mab from rsv_mab_detailed, to indicate if the record took mAb before collection (TBC), which is to be used as exposure in the analysis:
  * 50mg before collection ---> 1
  * 100mg before collection ---> 1
  * 50mg after collection ---> 0
  * 100mg after collection ---> 0
  * no mAb recorded but with last hepB vax recorded ---> 0
  * no mAb recorded and no last hepB vax recorded ---> 0
  
```{r}
df <- df %>% 
  mutate(rsv_mab = case_when(rsv_mab_detailed %in% c("50mg before collection",
                                                     "100mg before collection") ~ 1,
                             rsv_mab_detailed %in% c("50mg after collection",
                                                     "100mg after collection",
                                                     "no mAb recorded but with last hepB vax recorded",
                                                     "no mAb recorded and no last hepB vax recorded") ~ 0))

df %>% count(rsv_mab) %>% rename(n_records = n) %>%
  mutate(perc = round(n_records/nrow(df)*100,1)) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```
<br>

### Figure `r fig.counter`. Age at mAb 
Generate new variable age_at_mab_in_days (calculated as mAb date in nir tab - DOB )
The figure below only includes records with rsv_mab == 1:
```{r}
fig.counter <- fig.counter + 1

df <- df %>% 
  mutate(age_at_mab_in_days = as.numeric(as.Date(`mAb date`) - as.Date(DOB) ))

df %>% 
  filter(rsv_mab == 1) %>%
  ggplot() +
  geom_histogram(aes(x = age_at_mab_in_days), color = "black", fill = "white") + theme_classic()
```

<br>

### Read in oxygen volume tab and merge with main tab
```{r}
df.oxygen <- read_excel("/Users/hmx/OneDrive - Yale University/Hanmeng RSV VE/data/RSV_deid_2024_may.xlsx", sheet = "oxygen")

# merge oxygen data with main tab
df <- df %>% 
  left_join(df.oxygen, by = "StudyID")
```

### Figure `r fig.counter`. Maximum oxygen flow rate
#### Generate new variable max_oxygen_flowrate (unit: L/min), which threshold to use to indicate severe outcome? (after discussing, 1.5L/min can be used as a threshold to indicate severe disease.)
  * Also need to note that, there is no date in the oxygen tab, so for those patients with multiple visits, we cannot sure which record should be linked with the oxygen order.
```{r}
fig.counter <- fig.counter + 1

df <- df %>% mutate(max_oxygen_flowrate = as.numeric(gsub("Max. of flowsheet CPM S22 R INV FLOW (L/MIN) (OXYGEN THERAPY): ", "",
                                                      `Extreme Flowsheet Value`, fixed = TRUE)))

df %>% ggplot() +
  geom_histogram(aes(x = max_oxygen_flowrate), color = "black", fill = "white") + theme_classic() +
  geom_vline(xintercept = median(df$max_oxygen_flowrate, na.rm = T), color = "red", linetype = "dashed") +
  annotate("text", x = 16, y = 120, label = paste0("median=", median(df$max_oxygen_flowrate, na.rm = T)), color = "red")

```
#### Also, from "Order Questions" variable in the oxygen tab, extract whether there was CPAP (continuous positive airway pressure), BiPAP (Bilevel positive airway pressure), HFNC (high-flow nasal cannula)... ordered for each records, if there was, this is also an indication of severe disease.

#### Then, patients with max_oxygen_flowrate > 1.5L/min and patients who ordered high flow oxygen (based on order questions) were deemed "used high flow oxygen", generate a new variable called highflow_oxygen.
```{r}
pattern_oxygen <- paste(c("cpap",
                          "Bi-level",
                          "HFNC"),
                        collapse = "|")
df <- df %>% 
  mutate(ordered_highflow = ifelse(grepl(pattern_oxygen, `Order Questions`, ignore.case = T), 1, 0))

df <-  df %>% 
  mutate(highflow_oxygen = ifelse(max_oxygen_flowrate > 1.5 | ordered_highflow == 1, 1, 0))

df %>% count(highflow_oxygen) %>% 
   reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"))
```


<br>
<br>
<br>


```{r}
### Records that have more than one testing records 
df.multi.tests <- df %>% filter(StudyID %in% id_multi_tests) %>% arrange(StudyID, `Collection Date`)

a <- df.multi.tests %>% select(StudyID, `mAb date`,
             collection_date, `Admit Date`, `Hosp LoS`,  `Collection Department`, sample_source,
             tested_viruses, positive_viruses, `Encounter Type`, encounter_type,
             date_icu_admit_related, icu_admitted_related, icu_los_hours, 
             `Fever?`, `Problem List`, `Primary Problem`, `ED Dx`, `Admit Dx`,`Hospital Problem List`
             ) 


# write_xlsx(a, "../../data/multi_tests_records.xlsx")
```

### For each testing record, generate unique testID
#### If a patient was tested multiple times, the testID will has values of StudyID_nthTest (e.g. 99999999_1, 9999999_2..), the suffix indicates the nth test of the patient, ordered by date of sample collection.
Also generated n_tests for each StudyID, to indicate the number of tests this individual took,
and generated new variable nth_test to indicate this is the nth test of the same individual patient.
```{r}
df <- df %>% 
  group_by(StudyID) %>%
  arrange(collection_date) %>%
  mutate(n_tests = n()) %>% 
  mutate(testID = paste0(StudyID, "_", 1:n_tests)) %>%
  arrange(StudyID) 

# also generate variable nth_test to indicate this is the nth test of the same patient
df <- df %>% as.data.frame() %>% mutate(nth_test = str_sub(testID, -1))
```

### Table `r tab.counter`. Time since earliest collection for each patient
#### if an individual has multiple tests, for each test, generate new variables:
  * days_since_earliest_collection: the time elapse since the earliest test (in days, if this is the first test of a patient, take 0)
  * days_since_last_collection: time elapse since the most recent test (in days, if this is the first test of a patient, take 0)
  * days_to_next_collection: time to next collection (in days, if this is the last test of a patient, take 0).
```{r}
tab.counter <- tab.counter + 1

df <- df %>% 
  group_by(StudyID) %>%
  mutate(days_since_earliest_collection = as.numeric(collection_date - min(collection_date))) %>%
  as.data.frame()

df <- df %>% 
  group_by(StudyID) %>%
  mutate(days_since_last_collection = case_when(days_since_earliest_collection == 0 ~ 0,
                                                days_since_earliest_collection > 0 ~ 
                                                  as.numeric(collection_date - lag(collection_date)))) %>%
  as.data.frame()

df <- df %>% 
  group_by(StudyID) %>%
  mutate(days_to_next_collection = case_when(nth_test == n_tests ~ 0,
                                             nth_test < n_tests ~ 
                                               as.numeric( lead(collection_date) - collection_date )
                                               )) %>% 
  as.data.frame()
  


df %>% filter( days_since_earliest_collection > 0) %>%
  ggplot() + geom_histogram(aes(x = days_since_earliest_collection), color = "black", fill = "white") + theme_classic()
```

<br>

### Table `r tab.counter`. There are several individuals with more than one testing results on the same day. (TBC)
```{r}
tab.counter <- tab.counter + 1
temp_id <- (df %>% group_by(StudyID, collection_date) %>% count() %>% filter(n>1))$StudyID 

df %>% filter(StudyID %in% temp_id) %>%
  select(StudyID, collection_date, `Collection Department`, positive_viruses, rsv_mab, encounter_type, `Admit Date`) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"),
            groupBy = "StudyID", defaultExpanded = T)

a <- df %>% filter(StudyID %in% temp_id) 
```

<br>

### Mark testing records as cases and controls
(reference: https://pubmed.ncbi.nlm.nih.gov/36454733/)

#### Test-positive cases: 
  * A case of test-positive is defined as a positive RSV test. 

#### Test-negative controls:
  * Define test-negative control as a negative RSV test 
    + collected at any time if this patient was tested only once, **OR**
    + collected > 7 days prior this patient's next test **AND** collected > 7 days after this patient's last test (if the patient was tested multiple times)

#### Other notes:
  * An individual patient is allowed to contribute as both case and control, as the analysis is to be conducted at test-level, instead of patient-level. 
  * Each patient can contribute to up to three negative tests (controls) (TBC).
  *	If a person had more than one negative test within 7-day period, one random test was selected during the period as a control.

```{r echo = T}
##########################
# mark test-positive cases
##########################

df <- df %>% mutate(case_control = ifelse(positive_rsv == 1, "case", NA)) 

#############################
# mark test-negative controls
#############################

# generate a binary indicator to mark if this patient's next test is RSV positive (didn't use this) 
df <- df %>% 
  group_by(StudyID) %>%
  mutate(next_test_rsv_positive = lead(positive_rsv)) %>% 
  # NA if a person was tested once or this is a last test of an individual
  as.data.frame()
  

df <- df %>%
  group_by(StudyID) %>% 
  mutate(case_control = case_when(
  # 1. the patient was only tested once and was rsv negative
    (positive_rsv == 0 & n_tests == 1) | 
  # 2. the patient was tested multiple times: 
    # 2.1 if this is not the first or last test of the patient 
    # this negative test should be >7 days prior next test AND >7 days after previous test
    (positive_rsv == 0 & n_tests > 1 & days_to_next_collection > 7 & days_since_last_collection > 7) |
    # 2.2 if this is the first test of the patient
    # this negative test should be > 7 days prior next test
    (positive_rsv == 0 & n_tests > 1 & nth_test == 1 & days_to_next_collection > 7) |
    # 2.3 if this is the last test of the patient
    # this negative test should be > 7 days after previous test
    (positive_rsv == 0 & n_tests > 1 & nth_test == n_tests & days_since_last_collection > 7) ~ "control",
    TRUE ~ case_control
  )) %>% as.data.frame()


# If a person had more than one negative test within 7-day period, one random test was selected during the period as a control
set.seed(123)
temp <- df %>% 
  group_by(StudyID) %>%
  filter( 
    (  ((days_to_next_collection <= 7 | days_since_last_collection <= 7) & nth_test != 1 & n_tests != nth_test) | # tests in the middle 
       (nth_test == 1 & days_to_next_collection <= 7) | # first test
       (nth_test == n_tests & days_since_last_collection <= 7) # last test
    ) &  positive_rsv == 0)  %>%
  mutate(n_controls_to_sample_from = n()) %>%
  select(StudyID, n_controls_to_sample_from) %>% unique()
  

df <- df %>% left_join(temp, by = "StudyID")
  
# random select one control 
randomly.selected.controls.ids <- (df %>%
  filter(n_controls_to_sample_from > 1 & is.na(case_control)) %>%
  group_by(StudyID) %>% 
  sample_n(1) %>% 
  mutate(control_randomly_selected = 1))$testID
  
# mark these controls
df <- df %>% 
  mutate(randomly_selected_control = ifelse(testID %in% randomly.selected.controls.ids, 1, 0)) %>% 
  mutate(case_control = ifelse(randomly_selected_control == 1, "control", case_control))

# # individual patients contribute more than three controls (n = 17)
# df %>% 
#   group_by(StudyID) %>%
#   count(case_control) %>% 
#   filter(n>1) %>%
#   arrange(desc(n), StudyID) %>% 
#   filter(case_control == "control") %>%
#   filter(n > 3)

```

### Table `r tab.counter` Take a look at number of cases and controls.
```{r}
tab.counter <- tab.counter + 1
df %>% count(case_control) %>% 
  mutate(perc = round(n/nrow(df)*100, 1)) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px")) 
```

<br>

### Table `r tab.counter`. There are patients who contributed 2 cases.
#### (TBC) Should we include all test-positive records as cases? Or if the two test-positive results for the same individual happened within 7(?) days, we only keep one case for this individual?
```{r}
tab.counter <- tab.counter + 1

# there are several patients who contributed two cases:
id_multi_cases <- (df %>% group_by(StudyID) %>% count(case_control) %>% filter(case_control == "case") %>% filter(n>1))$StudyID

df %>% filter(StudyID %in% id_multi_cases) %>% 
  select(StudyID, collection_date, tested_viruses, positive_viruses, case_control) %>%
  reactable(style = list(color = "black", `font-family` = "Georgia", `font-size` = "15px"), 
            groupBy = "StudyID", defaultExpanded = T) 
```

<br>

```{r}
if(save_recoded_dataset){
  write.csv(df, "/Users/hmx/OneDrive - Yale University/Hanmeng RSV VE/data/RSV_mAb.csv", row.names = F)
}
```

<br>

### Table `r tab.counter`. briefly look at risk factors by mAb status
```{r}
tab.counter <- tab.counter + 1
library(table1)
# table1(): https://cran.r-project.org/web/packages/table1/vignettes/table1-examples.html


pvalue <- function(x, ...) {
    # Construct vectors of data y, and groups (strata) g
    y <- unlist(x)
    g <- factor(rep(1:length(x), times=sapply(x, length)))
    if (is.numeric(y)) {
        # For numeric variables, perform a standard 2-sample t-test
        p <- t.test(y ~ g)$p.value
    } else {
        # For categorical variables, perform a chi-squared test of independence
        p <- chisq.test(table(y, g))$p.value
    }
    # Format the p-value, using an HTML entity for the less-than sign.
    # The initial empty string places the output on the line below the variable label.
    c("", sub("<", "&lt;", format.pval(p, digits=3, eps=0.001)))
}


table1( ~ factor(Sex) + 
          age_at_test_in_months + 
          factor(encounter_type) +
          factor(insurance_type) +
          factor(risk_factor_gestage) +
          factor(risk_factor_cvd) +
          factor(risk_factor_gi) +
          factor(risk_factor_pulmonary) +
          factor(risk_factor_asthma) +
          factor(risk_factor_anemia) 
        | rsv_mab, data = df, overall= F,
          extra.col=list(`P-value`=pvalue))

```






<br>






